\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Backend Engineer} with 5+ years of experience designing and implementing scalable, high-performance backend services and \textbf{RESTful APIs} for enterprise and financial domains. Proficient in \textbf{Java}, \textbf{Python}, and \textbf{C++} with solid expertise in microservices architecture, cloud-native development on \textbf{AWS} and \textbf{Azure}, containerization with \textbf{Docker} and \textbf{Kubernetes}, and CI/CD pipelines. Experienced in collaborating with cross-functional teams to deliver secure, fault-tolerant distributed systems integrated with relational and NoSQL databases. Committed to clean, testable, and efficient code, with strong focus on observability, security best practices, and continuous learning in cloud infrastructure and backend technologies.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Spring MVC, Node.js, RESTful APIs, Microservices Architecture, gRPC (familiar) \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, Data Factory, AKS), GCP \\
     \textbf{Containerization/Orchestration}: Docker, Kubernetes \\
     \textbf{CI/CD Tools}: Jenkins, GitHub Actions, Azure DevOps, Terraform \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Data Streaming}: Apache Kafka, Real-time Data Processing, Event-driven Architecture \\
     \textbf{Security}: OAuth2, JWT, Backend Security Best Practices \\
     \textbf{Monitoring/Observability}: Prometheus, Grafana, ELK Stack \\
     \textbf{Testing}: JUnit, Cucumber, Postman, TDD/BDD, Automated and Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Designed, developed, and optimized \textbf{backend services} and \textbf{APIs} in \textbf{Python} and \textbf{SQL} to validate and process incoming fraud detection data workflows, improving system reliability and performance.}
        \resumeItem{Implemented automated regression and functional testing frameworks in \textbf{Java} using \textbf{Cucumber} and \textbf{BDD}, increasing test coverage and reducing manual testing effort by 40\%.}
        \resumeItem{Collaborated with cross-functional teams to build fraud monitoring pipelines handling large-scale transactional data using distributed processing tools and third-party software, enabling timely detection and case management.}
        \resumeItem{Contributed to Agile development cycles with continuous integration and deployment pipelines, leveraging best practices in \textbf{CI/CD}, code reviews, and system design for scalable backend microservices.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Engineered and tested scalable backend components for \textbf{Azure Cognitive Services}, utilizing \textbf{SDKs}, \textbf{RESTful APIs}, and cloud tools to improve service stability and scalability.}
        \resumeItem{Automated testing, monitoring, and containerized workflows using \textbf{Jupyter Notebooks}, \textbf{Postman}, and cloud orchestration tools, enhancing product observability by 30\%.}
        \resumeItem{Optimized large language model training pipelines on \textbf{Azure OpenAI}, improving performance by 25\% through tuning and benchmarking, supporting global-scale AI workloads.}
        \resumeItem{Partnered with engineering and product teams to shape backend architecture decisions for next-generation AI services, focusing on scalability, security, and maintainability in distributed cloud environments.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Quickly mastered \textbf{Azure} cloud services, \textbf{C++}, \textbf{C\#}, and data transformation tools like \textbf{XSLT} and \textbf{XML} to maintain and enhance backend modules within a complex enterprise system.}
        \resumeItem{Introduced code quality improvements and refactoring techniques under mentorship, contributing to more robust, maintainable codebases and a 10-15\% increase in development velocity.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led backend and frontend development supporting automotive haptics and infotainment systems, integrating \textbf{C++}, \textbf{Qt}, and \textbf{React} with backend \textbf{APIs} for seamless service-to-service communication.}
        \resumeItem{Designed and tested interactive features on prototype hardware, ensuring \textbf{low-latency} feedback crucial for safety and user experience compliance.}
        \resumeItem{Implemented CI/CD pipelines using \textbf{Jenkins} and version control tools, automating build and deployment processes for distributed microservices architecture.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed high-performance analytical backend components using \textbf{Java}, \textbf{C++}, \textbf{Python}, and \textbf{SQL}, achieving significant reductions in processing time through optimized algorithms and data structures.}
        \resumeItem{Built a \textbf{Python}-based utility to convert and compress large model datasets into efficient binary formats, accelerating data access and processing workflows.}
        \resumeItem{Diagnosed complex production issues including memory leaks and scalability bottlenecks, applying system design principles and observability practices for robust backend health monitoring.}
        \resumeItem{Applied \textbf{Lean Six Sigma} methodologies to streamline backend engineering processes, improving code quality and reducing cycle time.}
        \resumeItem{Mentored junior engineers on backend best practices, distributed systems design, and cloud-native development techniques.}
        \resumeItem{Led a team and served as \textbf{Scrum Master}, managing Agile ceremonies and collaborating with cross-functional teams to deliver scalable, enterprise-grade backend solutions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led development of a full-stack web application enabling peer-to-peer delivery of daily essentials with highly scalable backend services.}
            \resumeItem{Designed and implemented secure, scalable \textbf{RESTful APIs} using Node.js and Express, ensuring performant and reliable service interactions.}
            \resumeItem{Achieved full test coverage with Jest and implemented \textbf{JWT}-based authentication following clean code and SOLID principles, boosting maintainability by 40\%.}
            \resumeItem{Applied backend best practices focused on security, scalability, and performance to support growing user base and concurrent transactions.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed a cloud-native expense tracking solution leveraging \textbf{AWS Lambda}, \textbf{API Gateway}, and \textbf{DynamoDB} for serverless backend architecture.}
            \resumeItem{Integrated intelligent data extraction using Amazon Textract and automated notifications with SNS, improving user efficiency and backend automation.}
            \resumeItem{Managed infrastructure through \textbf{CloudFormation} templates, ensuring reproducibility and scalable environment provisioning.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Contributed backend logic using Java for simulating power restoration routes, optimizing algorithms to reduce restoration times by 35\%.}
            \resumeItem{Developed and maintained \textbf{JUnit} test suites to ensure high reliability and correctness of distributed system components.}
            \resumeItem{Utilized efficient data structures and parallel processing techniques for scalable backend simulation of real-world disaster scenarios.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}