\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-oriented \textbf{Full-Stack Software Engineer} with 5+ years of experience designing and building scalable, cloud-native web applications and backend microservices. Proficient in \textbf{Java/Spring Boot}, \textbf{Node.js/React}, and \textbf{Python}, with solid expertise in developing RESTful APIs, implementing \textbf{microservices architecture}, and deploying solutions on \textbf{AWS} and \textbf{Azure}. Experienced in creating performant and accessible frontend components and integrating complex data visualization. Demonstrated ability to deliver high-impact software at \textbf{TD Bank}, \textbf{Microsoft}, and other global enterprises while fostering reliability, continuous delivery, and DevOps best practices.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, JavaScript (React, Node.js), Python, C\#, SQL, Bash \\
     \textbf{Backend}: Spring Boot, RESTful APIs, Microservices, Cloud-native Architectures \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS, Accessibility (WCAG, ARIA) \\
     \textbf{Databases}: PostgreSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation), Azure (DevOps, AKS) \\
     \textbf{DevOps}: Docker, Kubernetes, Jenkins, GitHub Actions, CI/CD Pipelines, Terraform \\
     \textbf{Testing}: JUnit, Cucumber, Selenium, TDD/BDD, Unit and Integration Testing \\
     \textbf{Data Visualization}: Complex data manipulation and display using modern frontend technologies \\
     \textbf{Practices}: Agile/Scrum, Code Reviews, Scalability Optimization, Continuous Delivery (CD)
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Designed and maintained data validation scripts using Python and SQL for Azure Data Notebooks to ensure high data integrity from fraud detection pipelines, contributing to system stability and accuracy.}
        \resumeItem{Automated regression and functional tests via Java, Cucumber, and Selenium BDD suites, improving release quality and reducing manual effort by 40\%.}
        \resumeItem{Developed and sustained complex fraud monitoring workflows handling large-scale transactional data, enabling rapid alerts and case tracking with integration of third-party analytics tools.}
        \resumeItem{Collaborated within Agile teams to optimize SQL queries and backend services, delivering scalable and reliable features aligned with business goals.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led testing and quality assurance for Azure Cognitive Services features consuming REST APIs and SDKs, enhancing cloud service resilience and performance.}
        \resumeItem{Improved code quality and observability using Jupyter, Postman, and Visual Studio across languages including Java, Python, and C\#, supporting scalable, cloud-native pipelines.}
        \resumeItem{Trained and optimized OpenAI GPT models on Azure OpenAI, implementing benchmarking pipelines to reduce latency and improve throughput for AI workloads.}
        \resumeItem{Supported development of microservices components and contributed to validation of AI-driven cloud products in distributed team settings.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained proficiency on C\#, C++, XSLT, and Azure cloud services for microservice backend and frontend components, independently resolving production bugs and sprint features.}
        \resumeItem{Introduced code-quality and refactoring best practices, increasing sprint delivery velocity and software maintainability.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of React-based interactive frontend components for Cadillac design platform with emphasis on accessibility and performance in a multi-component architecture.}
        \resumeItem{Integrated frontend with backend RESTful APIs, delivering responsive UI experience aligned with automotive HMI requirements.}
        \resumeItem{Designed haptic feedback features following safety and UX guidelines, validated through hardware testing in real-world conditions.}
        \resumeItem{Contributed to infotainment UI workflows using Qt and C++ within complex, multi-tenant embedded systems.}
        \resumeItem{Implemented CI/CD automation pipelines via Jenkins, improving build reliability and accelerating continuous deployment cycles.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented performant analytical microservices and core components in Java, C\#, and Python, improving throughput for business-critical applications by 40\%.}
        \resumeItem{Developed Python utilities to convert large datasets into efficient binary formats, reducing load times and memory usage significantly for damage computation models.}
        \resumeItem{Performed thorough root-cause analysis on production issues such as memory leaks and latency bottlenecks, enhancing service stability.}
        \resumeItem{Certified Lean Six Sigma practitioner improving development processes and engineering workflows to increase team efficiency.}
        \resumeItem{Mentored new engineers via code reviews, pair programming, and training, contributing to a culture of quality and collaboration.}
        \resumeItem{Led a team of three engineers and served as Scrum Master, coordinating agile delivery of scalable, high-performance software solutions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS services, leveraging serverless architecture for scalability and reliability.}
            \resumeItem{Integrated Amazon Textract to automate data extraction from receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated user notifications with Python Lambda functions and SNS, improving user engagement and operational efficiency.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Contributed to a simulation project modeling power restoration routes post-Hurricane Fiona using Java and advanced algorithms.}
            \resumeItem{Developed reliable core functionality tested with JUnit, improving restoration planning accuracy and efficiency by 35\%.}
            \resumeItem{Handled large postal code datasets and optimized route computations to accelerate disaster response strategies.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}