\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Backend Software Engineer} with 5+ years of experience designing and developing high-performance API and cloud-native backend services. Proficient in \textbf{Python}, \textbf{Java}, and \textbf{Spring Boot}, with expertise in building scalable RESTful APIs, optimizing backend system performance, and integrating machine learning models into production workloads. Experienced in leveraging \textbf{containerization} (Docker, Kubernetes), relational databases (\textbf{PostgreSQL}, \textbf{MySQL}), and infrastructure-as-code tools such as \textbf{Terraform}. Proven ability to collaborate across engineering, product, and data science teams to deliver maintainable, robust systems for real-time decisioning on complex datasets.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: RESTful APIs, FastAPI, Spring Boot, Microservices Architecture, ORM (SQLAlchemy) \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, Data Factory, AKS), GCP \\
     \textbf{Containerization and Orchestration}: Docker, Kubernetes \\
     \textbf{Infrastructure as Code}: Terraform \\
     \textbf{Testing and QA}: Unit Testing, Integration Testing, JUnit, Cucumber, Postman, TDD/BDD \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and SQL validation scripts in Azure Data Notebooks to verify incoming data from financial fraud detection pipelines, improving data quality and system reliability for real-time processing of complex datasets.}
        \resumeItem{Automated regression and functional testing using \textbf{Java}, \textbf{Cucumber}, and \textbf{Selenium} with BDD practices, reducing manual testing effort by 40\% and increasing backend service reliability.}
        \resumeItem{Built and supported backend workflows managing large-scale transactional datasets, enhancing fraud detection pipelines with real-time evaluation and monitoring features.}
        \resumeItem{Collaborated with cross-functional teams following Agile methodology to design and optimize complex SQL queries and backend microservices, improving scalability and maintainability of banking solutions.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led quality and performance improvements for \textbf{Azure Cognitive Services} by testing SDKs, \textbf{REST APIs}, and backend AI service workflows, ensuring scalability of machine learning features.}
        \resumeItem{Streamlined code testing and containerized workflows using \textbf{Jupyter}, \textbf{Postman}, \textbf{Python}, \textbf{Java}, and \textbf{Kusto} queries, improving cloud-native service reliability and monitoring by 30\%.}
        \resumeItem{Optimized \textbf{OpenAI GPT} model training and deployment on \textbf{Azure OpenAI}, integrating LLM-driven capabilities into backend services for enhanced real-time decisioning.}
        \resumeItem{Collaborated closely with product and data science teams to translate machine learning requirements into backend features supporting scalable and maintainable APIs.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained proficiency in \textbf{Azure} cloud services and C\# backend development, owning sprint user stories and production bug fixes in complex backend systems.}
        \resumeItem{Introduced code-quality and refactoring improvements to backend components, enhancing maintainability and performance within the team’s CI/CD pipelines.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {People Tech Group Private Ltd.}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed end-to-end features in a complex automotive HMI system including backend API integrations and frontend UI components using React and C++, ensuring performance and reliability.}
        \resumeItem{Implemented CI/CD pipelines automated via Jenkins and Bitbucket, containerizing builds and tests to improve integration cycles and deployment efficiency.}
        \resumeItem{Collaborated with cross-functional teams to validate hardware and software integration, ensuring consistent and responsive system behavior aligned with business requirements.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Implemented and optimized core backend components and analytical models using \textbf{Python}, \textbf{Java}, \textbf{C\#}, C++, and \textbf{SQL}, achieving 40\% performance improvements on critical data processing workflows.}
        \resumeItem{Built a \textbf{Python}-based application that translated large model data into optimized binary formats, reducing file sizes by 90\% and improving load times for backend damage assessments.}
        \resumeItem{Diagnosed and resolved backend memory leaks and system performance issues through detailed profiling and debugging techniques.}
        \resumeItem{Led engineering process improvements following \textbf{Lean Six Sigma} principles and mentored new hires in backend development best practices and scalable system design.}
        \resumeItem{Collaborated with product and research teams to translate complex data science models into reliable, maintainable backend services supporting real-time decisioning.}
        \resumeItem{Served as \textbf{Scrum Master}, leading an engineering team of three through multiple iterative release cycles with Agile methodologies.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at low delivery costs, emphasizing scalable backend architecture with Node.js and Express.}
            \resumeItem{Designed an intuitive frontend interface using React and Bootstrap, improving user experience and engagement.}
            \resumeItem{Achieved comprehensive test coverage through Jest and Test-Driven Development (TDD), supporting maintainable and reliable backend API endpoints.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean coding practices, increasing backend maintainability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed a cloud-native expense tracking solution leveraging \textbf{AWS Lambda} and \textbf{Python} serverless functions integrated with DynamoDB and API Gateway.}
            \resumeItem{Enhanced data processing by integrating Amazon Textract for automated data extraction, reducing manual errors by 50\%.}
            \resumeItem{Automated notification workflows with Python scripts, using SNS to alert users promptly, boosting system responsiveness and user satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Contributed to a project modeling power restoration after Hurricane Fiona using Java, applying advanced data structures and algorithms to optimize restoration paths.}
            \resumeItem{Developed comprehensive unit tests with JUnit to ensure algorithm correctness and system reliability under realistic conditions.}
            \resumeItem{Achieved a 35\% reduction in estimated recovery times through efficient data analysis and optimized routing strategies.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}