\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience architecting and delivering scalable, distributed systems and cloud-native applications. Proficient in \textbf{Java/Spring Boot}, \textbf{Node.js/React}, and \textbf{Python}, with strong expertise in designing and maintaining RESTful APIs, integrating both relational and NoSQL databases, and leveraging \textbf{containerization} and \textbf{Kubernetes} on \textbf{AWS} and \textbf{Azure}. Adept at collaborating across product, data science, and operations teams to deliver well-tested, high-quality code following engineering best practices. Experienced in leading projects end to end and mentoring teams to drive consistent, scalable software delivery.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Spring MVC, Node.js, RESTful APIs, Microservices Architecture, Distributed Systems \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB (Relational and NoSQL) \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, Data Factory, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Data Streaming}: Apache Kafka, Real-time Data Processing, Event-driven Architecture \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, TDD/BDD, Automated Testing, Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, Clear Design Documentation, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in \textbf{Azure Data Notebooks} to verify incoming data from fraud detection pipelines, significantly improving data quality and system reliability in distributed environments.}
        \resumeItem{Automated regression and functional testing by developing \textbf{Java}-based test suites using \textbf{Cucumber}, Selenium, and BDD practices, reducing manual testing effort by 40\% and increasing feature reliability.}
        \resumeItem{Built and maintained fraud monitoring workflows leveraging large-scale transactional datasets and third-party tools such as OFSAA, enabling rapid detection, case creation, and tracking of suspicious financial transactions.}
        \resumeItem{Delivered multiple high-impact initiatives by designing and optimizing complex SQL queries and \textbf{collaborating cross-functionally} within Agile teams to ensure timely, high-quality releases.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove major quality improvements for \textbf{Azure Cognitive Services} by rigorously testing new features using \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Azure AI Studio}, identifying and resolving critical defects to enhance performance and stability in cloud-based distributed systems.}
        \resumeItem{Streamlined code testing, database analysis, and container-based workflows using \textbf{Jupyter}, \textbf{Postman}, \textbf{Visual Studio}, \textbf{Java}, \textbf{Python}, \textbf{C\#}, and \textbf{Kusto} queries, improving product reliability and observability by an estimated 30\%.}
        \resumeItem{Pioneered training, evaluation, and optimization of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, achieving a 25\% improvement in key performance metrics and significantly reducing latency for real-time workloads through systematic benchmarking and configuration tuning.}
        \resumeItem{Collaborated with cross-functional engineering and product teams to validate next-generation \textbf{Azure AI} capabilities, contributing to more scalable, production-ready cognitive and LLM-based services used in enterprise scenarios.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Ramped up on \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure} within the first month on a complex codebase, enabling independent ownership of sprint user stories and production bug fixes.}
        \resumeItem{Leveraged \textbf{Pluralsight} courses and mentorship programs to introduce code-quality improvements and \textbf{best engineering practices} including code reviews and refactoring, helping the team deliver key Medic1 milestones on time.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of new haptic feedback features for Cadillac vehicles from concept to integration, including requirements analysis, implementation, and client communication to align UX behavior with safety and brand guidelines.}
        \resumeItem{Developed interactive frontend application for Cadillac design platform using React with modern component architecture, integrating with backend APIs to deliver responsive user experience while collaborating with design and engineering teams to visualize automotive configurations.}
        \resumeItem{Designed and tested \textbf{haptics} functionality on prototype hardware, validating vibration patterns and timing in realistic driving scenarios before in-car integration.}
        \resumeItem{Contributed to infotainment UI and interaction workflows using \textbf{Qt}, \textbf{Rhapsody}, \textbf{WeCAN}, and \textbf{C++}, improving responsiveness and reliability of production systems in a complex automotive HMI distributed environment.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines for automotive software using \textbf{Jenkins}, \textbf{SourceTree}, and \textbf{Bitbucket}, automating builds and tests for infotainment components, reducing deployment time and integration issues.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Implemented next-generation analytical models and core components using \textbf{Java}, \textbf{C\#}, \textbf{Python}, \textbf{C++}, \textbf{SQL}, data structures and algorithms, delivering an average 40\% performance improvement across 5+ business-critical models in distributed systems.}
        \resumeItem{Built a \textbf{Python}-based application to convert large model data into optimized binary formats, reducing file sizes from approximately 2GB to 200MB and significantly cutting load and processing times for downstream computations.}
        \resumeItem{Diagnosed and resolved complex production issues, including critical memory leaks and performance bottlenecks, using systematic debugging, profiling, and root-cause analysis techniques.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process-improvement practices to streamline development workflows and reduce waste in engineering processes.}
        \resumeItem{Mentored new hires through induction sessions, pair programming, and peer reviews, helping onboard engineers faster and strengthening overall engineering culture.}
        \resumeItem{Collaborated with Product Management and Research to refine feature requirements and deliver scalable, high-performance solutions, while leading a team of three engineers and serving as \textbf{Scrum Master} for multiple releases.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to \textbf{SOLID principles} and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}