\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience designing and deploying scalable, cloud-native applications and \textbf{machine learning} solutions. Proficient in building \textbf{data-driven models}, \textbf{statistical algorithms}, and \textbf{real-time data processing} pipelines leveraging \textbf{Python}, \textbf{Java}, and \textbf{Azure/AWS} cloud platforms. Experienced in collaborating cross-functionally with Engineers, Data Scientists, and Product Managers to deliver impactful software products and \textbf{ML models} with robust performance and reliability. Proven ability to integrate large-scale data, optimize backend services, and implement production-quality code, aligned with business objectives in fast-paced environments.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Machine Learning}: Supervised Learning, Forecasting, Recommendation Systems, Reinforcement Learning, Model Evaluation, OpenAI GPT, Azure Machine Learning \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation), Azure (DevOps, Data Factory, AKS, Cognitive Services, Azure AI Studio), GCP \\
     \textbf{Data Processing}: Apache Kafka, Real-time Data Streaming, Event-driven Architecture \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, TDD/BDD, Automated and Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{\textbf{Developed and maintained Python and SQL data validation scripts} in \textbf{Azure Data Notebooks} to ensure accuracy and freshness of input data from fraud detection pipelines, enhancing data quality with \textbf{ML}-compatible datasets.}
        \resumeItem{Automated regression and functional testing using Java-based Cucumber frameworks following BDD practices, improving \textbf{ML system} reliability and decreasing manual testing efforts by 40\%.}
        \resumeItem{Built monitoring workflows on large transactional datasets to track and analyze suspicious events, supporting rapid identification and case creation for potential fraud leveraging data-driven techniques.}
        \resumeItem{Collaborated with cross-functional teams using Agile methodologies to design optimized SQL queries and backend services that serve \textbf{real-time} operational mappings and analytics.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Enhanced quality and stability of \textbf{Azure Cognitive Services} by testing new \textbf{ML models} and APIs, leveraging SDKs and Azure AI Studio for comprehensive evaluation and defect resolution.}
        \resumeItem{Utilized \textbf{Python}, \textbf{Java}, \textbf{C\#}, and \textbf{Kusto queries} within \textbf{Jupyter} and Postman environments to streamline data validation and containerized workflows for scalable \textbf{ML model} deployment.}
        \resumeItem{Led training, tuning, and benchmarking of \textbf{OpenAI GPT} models via \textbf{Azure OpenAI} platform, achieving a 25\% improvement in predictive performance and lower latency in real-time processing pipelines.}
        \resumeItem{Partnered with engineering and product teams to validate and optimize \textbf{AI/ML} capabilities, contributing to the design of scalable \textbf{mapping-related} models and cognitive services.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained proficiency in \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure} to maintain complex codebases for data processing and backend services supporting \textbf{real-time} data workflows.}
        \resumeItem{Implemented code-quality improvements and refactoring, improving maintainability and velocity by 10–15\%, aligning with best practices for robust software systems supporting data pipelines.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led design and integration of advanced \textbf{haptic feedback} features, exhibiting strong problem solving and system design aligned with real-time hardware and UX integration challenges.}
        \resumeItem{Developed highly interactive React frontend applications interfacing with backend APIs, demonstrating skills in delivering seamless user experiences for complex systems.}
        \resumeItem{Tested and validated \textbf{hardware-driven} vibration patterns, emphasizing rigorous data collection and assessment analogous to mapping sensor data validation tasks.}
        \resumeItem{Contributed to automotive infotainment UI and interaction workflows using \textbf{Qt}, \textbf{C++}, and embedded systems, focusing on reliable, low-latency responses essential for real-world applications.}
        \resumeItem{Established CI/CD pipelines using \textbf{Jenkins} and source control tools, accelerating deployment cycles and improving software release quality.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Engineered scalable analytical \textbf{models} and core processing components using Java, Python, C++, C\#, and SQL, improving model performance by 40\% across critical business applications.}
        \resumeItem{Developed a \textbf{Python} application to convert large model datasets into optimized binary representations, decreasing load times and enabling efficient data handling for downstream computations.}
        \resumeItem{Diagnosed and resolved complex production issues such as memory leaks and performance bottlenecks via advanced debugging and profiling, maintaining high availability and robustness.}
        \resumeItem{Certified in \textbf{Lean Six Sigma}, implementing process improvements to streamline development and foster quality-driven team culture.}
        \resumeItem{Mentored new engineers using code reviews and pair programming, fostering knowledge sharing and accelerating onboarding within an \textbf{Agile Scrum} team.}
        \resumeItem{Collaborated with Product and Research teams to refine feature specifications and guide delivery of scalable, high-performance systems, fulfilling \textbf{business goals} through technology.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}