\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building cloud-native and \textbf{microservices-based} backend services and web applications for financial services and enterprise clients. Expert in \textbf{Java} and \textbf{Spring Boot} for developing scalable, secure \textbf{RESTful APIs} and integrating containerization with \textbf{Docker} and \textbf{Kubernetes}. Skilled in collaborating with frontend teams using \textbf{React}, and deploying solutions on \textbf{AWS} and \textbf{Azure} cloud platforms. Proven ability to deliver high-performance platforms and contribute effectively in fast-paced, agile environments.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: \textbf{Spring Boot}, Spring MVC, Node.js, \textbf{RESTful APIs}, Microservices Architecture \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS, WebSocket integrations \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), \textbf{Azure (DevOps, Data Factory, AKS)}, GCP \\
     \textbf{DevOps and Tools}: \textbf{Docker}, \textbf{Kubernetes}, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines, GitLab, Artifactory \\
     \textbf{Data Streaming}: Apache Kafka, Real-time Data Processing, Event-driven Architecture \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, TDD/BDD, Automated Testing, Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, Software Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, improving data quality and system reliability.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber, Selenium, and BDD practices, reducing manual testing effort by 40\% and improving feature integrity.}
        \resumeItem{Built and maintained fraud monitoring workflows leveraging large-scale transactional datasets and third-party tools such as OFSAA, enabling rapid detection and case tracking of suspicious financial transactions.}
        \resumeItem{Collaborated in Agile teams to design and optimize complex SQL queries and RESTful backend services, ensuring timely and maintainable delivery of financial risk management features.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements for \textbf{Azure Cognitive Services} by rigorously testing new features utilizing SDKs, \textbf{REST APIs}, and Azure AI Studio, identifying and resolving critical defects for enhanced stability.}
        \resumeItem{Streamlined code testing, database analytics, and containerized workflows using Jupyter, Postman, Visual Studio, Java, Python, C\#, and Kusto queries, improving reliability and observability by up to 30\%.}
        \resumeItem{Optimized \textbf{OpenAI GPT} model training and evaluation on \textbf{Azure OpenAI}, achieving 25\% performance improvements and reducing latency for real-time workloads through benchmarking and tuning.}
        \resumeItem{Collaborated closely with engineering and product teams to validate cloud-native AI capabilities, contributing to scalable, production-ready enterprise cognitive services deployed on cloud platforms.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Ramped up on XSLT, XML, C\#, C++, and \textbf{Azure AKS} within first month to support sprint delivery and production fixes on complex cloud-native codebase.}
        \resumeItem{Introduced code-quality enhancements and refactoring guidance leveraging Pluralsight courses and mentorship, increasing development velocity and maintainability by 10-15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of haptic feedback features from requirements to integration for Cadillac vehicles, ensuring compliance with safety and UX standards.}
        \resumeItem{Designed interactive frontend applications using \textbf{React} and integrated with backend RESTful APIs, collaborating with design and engineering teams to deliver seamless user experiences.}
        \resumeItem{Tested haptic functionality on prototype hardware, validating vibration patterns and timing for accurate in-car integration.}
        \resumeItem{Contributed to infotainment UI workflows using Qt, Rhapsody, WeCAN, and C++ in an embedded automotive environment, improving system responsiveness and reliability.}
        \resumeItem{Implemented CI/CD pipelines using Jenkins, SourceTree, and Bitbucket to automate build and deployment workflows, enhancing integration efficiency across teams.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed core analytical models and services using \textbf{Java}, C\#, Python, C++, and SQL with focus on high-performance and scalable risk analytics solutions, improving processing speeds by 40\%.}
        \resumeItem{Built a Python app to convert large model data into optimized binary formats, reducing data load times and improving downstream damage calculations.}
        \resumeItem{Diagnosed and resolved critical production issues including memory leaks and bottlenecks through in-depth debugging and profiling, enhancing system stability.}
        \resumeItem{Earned Lean Six Sigma certification and applied continuous process improvements to software development workflows for efficiency gains.}
        \resumeItem{Mentored new engineers and led a team of three as Scrum Master, fostering agile best practices and delivering multiple product releases on schedule.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, increasing user accessibility.}
            \resumeItem{Designed intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built robust, scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, boosting maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Integrated Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated user notifications via Python scripts in Lambda, extracting critical info and triggering SNS alerts, increasing user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Contributed to a project simulating extensive power outages after Hurricane Fiona in Atlantic Canada for improved disaster response planning.}
            \resumeItem{Developed core functionality using Java and JUnit test cases, assuring accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to optimize power restoration routes, decreasing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}