\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Software Engineer} with 5+ years of experience developing scalable backend services and \textbf{machine learning} solutions leveraging \textbf{Python}, \textbf{Java}, and cloud platforms such as \textbf{AWS} and \textbf{Azure}. Hands-on experience applying ML methodologies including supervised learning, forecasting, and recommendation systems to solve complex engineering and business problems. Proven ability to partner cross-functionally with engineers, data scientists, and product managers to design, develop, and launch \textbf{production-quality} ML models and cloud services. Strong focus on data quality, model performance, and real-time data pipelines in fast-paced, collaborative environments.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture \\
     \textbf{Machine Learning}: Supervised Learning, Forecasting, Recommendation Systems, Model Evaluation, OpenAI GPT \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, DynamoDB), Azure (DevOps, Data Factory, AKS, Azure AI Studio) \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Data Streaming and Processing}: Apache Kafka, Real-time Data Processing, Event-driven Architecture \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, TDD/BDD, Automated Testing, Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Wipro Technologies (TD Bank)}}{\textbf{Oct 2024 -- Present}}
      {Toronto, Canada}{}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in Azure Data Notebooks to verify and improve data quality for fraud detection and \textbf{real-time data processing} pipelines, enhancing overall system reliability.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber and Selenium, enabling faster, reliable delivery of features with reduced manual effort.}
        \resumeItem{Built and maintained fraud monitoring workflows leveraging large transactional datasets and integrated third-party tools, enabling rapid detection and tracking of suspicious activities.}
        \resumeItem{Collaborated with cross-functional teams under Agile methodologies to design scalable backend solutions and optimize performance-critical SQL queries supporting real-time analytics.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{LTI Mindtree LTD (Microsoft)}}{\textbf{Dec 2023 -- Apr 2024}}
      {Calgary, Canada}{}
      \resumeItemListStart
        \resumeItem{Drove quality improvements for \textbf{Azure Cognitive Services} through rigorous testing of new ML and AI features using SDKs, REST APIs, and cloud AI tooling, identifying defects and enhancing stability.}
        \resumeItem{Streamlined code testing, data analysis, and container workflows with Jupyter, Postman, Java, Python, C\#, and Kusto queries to improve observability and performance of production AI services.}
        \resumeItem{\textbf{Developed, trained, and optimized machine learning models}, including \textbf{OpenAI GPT} models on Azure OpenAI service, increasing key performance metrics and reducing latency for real-time cloud applications.}
        \resumeItem{Partnered with engineers and product teams to validate and scale \textbf{production-ready ML services} and cognitive AI capabilities used by enterprise customers.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{ESO}}{\textbf{Jan 2024 -- Apr 2024}}
      {Halifax, Canada}{}
      \resumeItemListStart
        \resumeItem{Gained proficiency in XSLT, XML, C\#, C++, and Azure cloud environments, autonomously managing sprint deliverables and critical production fixes.}
        \resumeItem{Introduced engineering best practices focused on code quality and refactoring to accelerate development velocity through mentorship and training programs.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{People Tech Group Private Ltd.}}{\textbf{Jan 2022 -- Aug 2022}}
      {Hyderabad, India}{}
      \resumeItemListStart
        \resumeItem{Led development of haptic feedback features for Cadillac vehicles, incorporating requirements analysis, implementation, and validation with prototype hardware in real-world driving scenarios.}
        \resumeItem{Developed interactive frontend using React and backend API integration to deliver responsive UX for automotive design tools, collaborating closely with design and engineering teams.}
        \resumeItem{Contributed to infotainment UI workflows using Qt, Rhapsody, WeCAN, and C++, improving system responsiveness and reliability in complex automotive HMI environments.}
        \resumeItem{Implemented CI/CD pipelines with Jenkins, SourceTree, and Bitbucket, automating build and test processes to support continuous integration for automotive software components.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Verisk Analytics}}{\textbf{Sep 2018 -- Jan 2022}}
      {Hyderabad, India}{}
      \resumeItemListStart
        \resumeItem{Implemented advanced analytical models and core components using Java, C\#, Python, C++, and SQL, achieving 40\% performance improvements for multiple business-critical models.}
        \resumeItem{Built a Python tool to convert large model data into optimized binary formats, reducing file sizes by 90\% and accelerating processing times for downstream ML workflows.}
        \resumeItem{Diagnosed and resolved complex production issues including memory leaks and bottlenecks, applying systematic debugging and performance profiling techniques.}
        \resumeItem{Earned Lean Six Sigma certification, applying process improvements and best practices to enhance engineering efficiency and quality.}
        \resumeItem{Mentored new engineers and led a Scrum team, collaborating with product and research teams to deliver scalable, high-performance solutions aligned with business objectives.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}