\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Backend Engineer} and \textbf{Full-Stack Software Engineer} with 5+ years of experience architecting, building, and maintaining scalable, secure, and high-performance backend services and APIs. Proficient in designing distributed systems and microservices with expertise in \textbf{Java/Spring Boot}, \textbf{Python}, \textbf{Node.js}, and \textbf{C++}, with hands-on experience in cloud-native environments (\textbf{AWS}, \textbf{Azure}) and container orchestration (\textbf{Docker}, \textbf{Kubernetes}). Adept at collaborating with cross-functional teams to drive impactful projects in financial, enterprise, and AI domains, focusing on enhancing reliability, observability, and security practices.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, C++, Node.js, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture, gRPC basics \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, AKS, Data Factory), GCP \\
     \textbf{Containerization and Orchestration}: Docker, Kubernetes \\
     \textbf{CI/CD}: Jenkins, GitHub Actions, Azure DevOps, Terraform (Infrastructure as Code) \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Data Streaming}: Apache Kafka, Event-driven Architecture \\
     \textbf{Security and Observability}: OAuth2, JWT, Prometheus, Grafana, ELK Stack \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, TDD/BDD, Automated Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Designed and implemented scalable backend validation services and APIs using \textbf{Python} to improve data ingestion quality for fraud detection pipelines on \textbf{Azure} cloud infrastructure.}
        \resumeItem{Automated regression and functional testing via \textbf{Java}-based suites with \textbf{Cucumber} and \textbf{BDD}, enhancing test coverage and accelerating deployment cadence by 40\%.}
        \resumeItem{Developed and optimized \textbf{SQL} queries for large-scale transactional data, improving performance and enabling efficient fraud monitoring workflows integrated with third-party tools.}
        \resumeItem{Collaborated closely with cross-functional teams adopting Agile practices to design and review microservices, ensuring robust performance, security, and maintainability at scale.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Azure Cognitive Services} backend by rigorously validating \textbf{REST APIs} and SDK functionality, improving stability and scalability for AI-powered enterprise applications.}
        \resumeItem{Utilized \textbf{Jupyter}, \textbf{Postman}, and containerized workflows incorporating \textbf{Java}, \textbf{Python}, and \textbf{C\#} to strengthen backend reliability and observability mechanisms.}
        \resumeItem{Implemented performance benchmarking and optimization for \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, reducing latency and improving throughput for real-time data pipelines.}
        \resumeItem{Collaborated in system architecture reviews and microservices design discussions, contributing backend expertise to production-ready, cloud-native AI services.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Quickly onboarded and enhanced backend components using \textbf{C++}, \textbf{C\#}, \textbf{Azure} services, and \textbf{XSLT}/\textbf{XML} for complex distributed software systems.}
        \resumeItem{Introduced backend code quality improvements and refactoring processes that increased development velocity and maintainability by up to 15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led backend development for automotive haptic feedback systems integrating real-time signal processing with embedded \textbf{C++} services, ensuring reliable performance in production environments.}
        \resumeItem{Developed React frontend and backend API integrations improving system scalability and responsiveness in automotive infotainment platforms.}
        \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins}, \textbf{Bitbucket}, and container-based automation, reducing integration issues and deployment times.}
        \resumeItem{Conducted performance testing and validation of distributed backend services, aligning with automotive safety and security standards.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Engineered high-performance backend systems and analytical models using \textbf{Java}, \textbf{Python}, \textbf{C++}, and \textbf{SQL}, improving processing speed and resource utilization by 40\%.}
        \resumeItem{Developed data transformation pipelines and storage optimizations reducing large model data sizes by over 90\%, facilitating faster downstream operations.}
        \resumeItem{Led debugging and root cause analysis efforts on production systems to resolve critical memory and scalability issues.}
        \resumeItem{Applied \textbf{Lean Six Sigma} methodologies to optimize development workflows and enhance code quality and team productivity.}
        \resumeItem{Mentored junior engineers on backend architecture, clean coding standards, and Agile development practices as Scrum Master.}
        \resumeItem{Collaborated with product and research teams to design scalable microservices architectures supporting complex business logic and distributed data processing.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, improving accessibility and user experience.}
            \resumeItem{Designed scalable backend \textbf{RESTful APIs} with Node.js and Express, following best practices for security and maintainability.}
            \resumeItem{Implemented \textbf{JWT}-based authentication and authorization, enhancing user security and data privacy.}
            \resumeItem{Achieved 100\% test coverage through rigorous \textbf{Jest} testing and \textbf{TDD}, ensuring high reliability of backend services.}
            \resumeItem{Followed SOLID principles and clean code practices, improving codebase scalability and team collaboration.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed a serverless expense tracking backend leveraging \textbf{AWS Lambda}, \textbf{API Gateway}, and \textbf{DynamoDB} to enable efficient, scalable cloud-native services.}
            \resumeItem{Integrated \textbf{Amazon Textract} to automate extraction of data from receipts, reducing manual entry errors by 50\%.}
            \resumeItem{Implemented event-driven workflows with \textbf{SNS} for real-time notifications, improving user engagement and responsiveness.}
            \resumeItem{Used \textbf{CloudFormation} templates for infrastructure as code, enabling reproducible and automated deployments.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Contributed to a simulation project addressing disaster recovery for power grids, applying \textbf{Java}-based algorithms to optimize restoration processes.}
            \resumeItem{Developed and tested core backend algorithms with \textbf{JUnit}, ensuring reliability and performance under real-world constraints.}
            \resumeItem{Utilized advanced data structures and algorithmic solutions to improve restoration efficiency by 35\%, enhancing disaster response planning tools.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}