\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building responsive, \textbf{data-rich frontend web applications} and backend services for financial services and enterprise domains. Skilled in \textbf{JavaScript (ES6+), TypeScript, React}, and cloud-native technologies including \textbf{AWS} and \textbf{Azure}. Proven experience integrating complex data models and optimizing applications for \textbf{performance and scalability} in real-time, mission-critical environments. Track record delivering projects at \textbf{TD Bank}, \textbf{Microsoft}, and other global firms, with a focus on clean, maintainable code and cross-team collaboration. Passionate about applying frontend expertise to build intuitive, high-performance user interfaces for \textbf{quantitative finance} and trading platforms.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: JavaScript (ES6+), TypeScript, Java, Python, C++, C\# \\
     \textbf{Frontend}: React, HTML5, CSS3, SCSS, Tailwind, styled-components \\
     \textbf{Testing}: Jest, React Testing Library, Selenium, Cucumber, Cypress \\
     \textbf{Visualization}: Exposure to D3.js, Highcharts concepts through data-intensive apps \\
     \textbf{Backend and Frameworks}: Node.js, Spring Boot, RESTful APIs, Microservices \\
     \textbf{Databases}: PostgreSQL, MongoDB, DynamoDB, Redis \\
     \textbf{Cloud & CI/CD}: AWS (EC2, Lambda, S3), Azure (AKS, DevOps), Docker, Kubernetes, Jenkins, GitHub Actions, CI/CD Pipelines \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability, Performance Optimization
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed automated \textbf{Python} and \textbf{SQL} validation scripts to ensure accuracy of transactional data feeding fraud detection workflows, enhancing \textbf{data reliability} for real-time financial monitoring.}
        \resumeItem{Improved application stability and quality by developing \textbf{Java}-based automated regression and functional test suites using \textbf{Cucumber} and \textbf{Selenium} with strong BDD focus, reducing manual QA effort.}
        \resumeItem{Collaborated with cross-functional teams to design, implement, and maintain data-intensive workflows and backend integrations, supporting seamless \textbf{real-time fraud monitoring} and alerting in high-throughput financial systems.}
        \resumeItem{Applied \textbf{Agile/Scrum} principles for iterative releases, focusing on \textbf{code quality}, peer reviews, and performance optimizations for critical banking applications.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Tested and validated new features of \textbf{Azure Cognitive Services} using SDKs, REST APIs, and integrated tools, increasing service \textbf{performance and robustness} in large-scale cloud deployments.}
        \resumeItem{Streamlined integration workflows involving \textbf{Python}, \textbf{Java}, and \textbf{C\#} with \textbf{Postman} and \textbf{Kusto} queries, enhancing observability and testing efficiency by 30\%.}
        \resumeItem{Optimized training and inference for \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, reducing latency for real-time AI workloads via benchmarking and tuning, directly improving responsiveness.}
        \resumeItem{Collaborated with engineering and product teams to validate next-gen AI capabilities, contributing to scalable, enterprise-ready services for cognitive and language model integrations.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Quickly ramped up on \textbf{Azure}, \textbf{C\#}, \textbf{XSLT}, and \textbf{XML} within a complex codebase, independently managing user stories and production bug fixes.}
        \resumeItem{Influenced team development velocity by introducing \textbf{code quality} improvements and refactoring practices through mentorship and learning resources.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led frontend feature development for Cadillac’s haptic feedback system using \textbf{React}, enabling richer, safety-compliant user experience through responsive interfaces integrated with backend APIs.}
        \resumeItem{Contributed to infotainment UI workflows with \textbf{Qt}, \textbf{C++}, and hardware testing, achieving improved responsiveness and system reliability in automotive HMI environments.}
        \resumeItem{Implemented CI/CD pipelines using \textbf{Jenkins} and \textbf{Bitbucket}, automating build and test processes to streamline deployment and integration.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Delivered scalable analytical models and core components with \textbf{Java}, \textbf{C\#}, \textbf{Python}, \textbf{C++}, and \textbf{SQL}, improving performance by 40\% across critical insurance risk products.}
        \resumeItem{Engineered a \textbf{Python}-based tool to convert large-scale model data to compact binary formats, reducing processing times significantly, vital for data-driven decision systems.}
        \resumeItem{Resolved complex production issues including memory leaks and bottlenecks via debugging and profiling tools, ensuring high system availability.}
        \resumeItem{Led a team of engineers, acted as \textbf{Scrum Master}, and collaborated closely with Product and Research on scalable, high-performance solutions, promoting Agile best practices.}
        \resumeItem{Earned and applied \textbf{Lean Six Sigma} certification to improve engineering workflows and reduce waste.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led development of a full-stack web application enabling peer-to-peer delivery of daily essentials, featuring a \textbf{React}-based \textbf{responsive frontend} enhancing user engagement.}
            \resumeItem{Built robust, scalable backend APIs with \textbf{Node.js} and \textbf{Express} ensuring seamless integration and performance under load.}
            \resumeItem{Achieved \textbf{100\% test coverage} with Jest and Test-Driven Development, substantially reducing bugs and improving reliability.}
            \resumeItem{Implemented secure authentication using JWT and followed \textbf{SOLID principles}, increasing maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed a scalable expense tracking system deployed on \textbf{AWS}, utilizing \textbf{Lambda} functions and \textbf{DynamoDB} for efficient backend processing.}
            \resumeItem{Integrated \textbf{Amazon Textract} for automatic receipt data extraction, reducing manual input errors by 50\% and improving user experience.}
            \resumeItem{Implemented Python scripts for notifications via SNS, automating user alerts and boosting engagement and efficiency.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Contributed to simulation modeling for post-Hurricane Fiona power outage recovery, applying \textbf{Java}, \textbf{JUnit}, and advanced data structures to optimize restoration routes.}
            \resumeItem{Improved planning efficiency by 35\% through algorithmic optimization, supporting faster disaster response and resource allocation.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}