\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience delivering scalable, cloud-native web applications and backend microservices primarily on \textbf{AWS} and \textbf{Azure}. Skilled in \textbf{Java/Spring Boot}, \textbf{Node.js/React}, and \textbf{Python}, with a strong focus on \textbf{RESTful API} design, microservices architecture, and \textbf{CI/CD} automation. Proven ability to build complex, data-intensive web applications with attention to performance optimization, accessibility (WCAG standards), and maintainability. Experienced in collaborating across distributed teams to deliver high-impact cloud solutions in fast-paced Agile environments aligned with enterprise-grade security and reliability standards.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, JavaScript (ES6+), Python, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture, Serverless \\
     \textbf{Frontend}: React, Web Components, JavaScript, HTML5, CSS3, Accessibility (WCAG, ARIA) \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, API Gateway, CloudFormation, DynamoDB), Azure (DevOps, Data Factory, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines, CD Best Practices \\
     \textbf{Data Visualization and Manipulation}: Complex Data Processing, Real-time Data Handling, Performance Tuning \\
     \textbf{Testing and QA}: Jest, JUnit, Cucumber, Selenium, Postman, TDD/BDD, Automated Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and \textbf{SQL} scripts in Azure Data Notebooks to validate large-scale data pipelines, significantly enhancing \textbf{data quality} and system reliability.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using \textbf{Cucumber}, \textbf{Selenium}, and BDD practices, improving \textbf{feature stability} and reducing manual testing effort by 40\%.}
        \resumeItem{Built and maintained \textbf{fraud monitoring workflows} handling high-volume transactional data, applying \textbf{microservices} principles to enable scalable detection and case tracking.}
        \resumeItem{Collaborated in Agile teams to design and optimize \textbf{RESTful APIs}, complex SQL queries, and deliver reliable releases, supporting continuous integration and deployment pipelines.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Data Engineer}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Azure Cognitive Services} features through rigorous testing using \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Azure AI Studio}, significantly improving performance and stability of cloud-native microservices.}
        \resumeItem{Optimized code quality, container workflows, and observability via tools such as \textbf{Jupyter}, \textbf{Postman}, \textbf{Visual Studio}, \textbf{Java}, \textbf{Python}, and \textbf{Kusto} queries, increasing product reliability by 30\%.}
        \resumeItem{Led fine-tuning of \textbf{OpenAI GPT} models leveraging \textbf{Azure OpenAI}, improving model efficiency and decreasing latency for real-time workloads.}
        \resumeItem{Collaborated cross-functionally to validate and scale \textbf{Azure AI} microservices in production, ensuring performance and seamless integration in cloud environments.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Development Engineer Co-op}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Ramped up quickly on \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure} within a complex microservices codebase, taking ownership of sprint user stories and bug fixes supporting production stability.}
        \resumeItem{Introduced code quality and refactoring improvements by leveraging mentorship and \textbf{Pluralsight} courses, increasing team development velocity by 10-15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed interactive \textbf{React}-based frontend applications using modern component architecture, integrating backend \textbf{RESTful APIs} to deliver scalable, accessible user experiences for automotive design platforms.}
        \resumeItem{Led development and testing of embedded \textbf{haptics} features for vehicles, validating functional requirements and ensuring compliance with safety and UX standards.}
        \resumeItem{Contributed to infotainment UI and interaction workflows using \textbf{Qt}, \textbf{C++}, and \textbf{WeCAN}, improving responsiveness and reliability in a complex, multi-component automotive system.}
        \resumeItem{Implemented \textbf{CI/CD pipelines} for automotive software deployment using \textbf{Jenkins}, \textbf{SourceTree}, and \textbf{Bitbucket}, automating builds and tests to speed integration and reduce errors.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer II}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented core components and data-intensive solutions in \textbf{Java}, \textbf{C\#}, \textbf{Python}, and SQL, delivering up to 40\% performance improvements in business-critical analytical models.}
        \resumeItem{Built Python-based tools to efficiently transform large datasets into optimized binary formats for quick loading and processing in downstream systems.}
        \resumeItem{Resolved critical production issues including memory leaks and performance degradation through advanced debugging and profiling.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process improvements to enhance engineering workflows and team efficiency.}
        \resumeItem{Mentored new engineers, conducting code reviews, pair programming, and onboarding, while leading a Scrum team and collaborating closely with Product Management for scalable delivery.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led development of a full-stack web application enabling peer-to-peer delivery of daily essentials with focus on \textbf{scalability} and \textbf{performance}.}
            \resumeItem{Built intuitive frontend using \textbf{React} with component-based architecture and implemented \textbf{accessibility} best practices to enhance user experience.}
            \resumeItem{Implemented robust backend APIs with Node.js and Express, ensuring seamless data integration and secure \textbf{JWT}-based authentication.}
            \resumeItem{Achieved 100\% test coverage via Jest and Test-Driven Development (TDD), improving reliability and maintainability.}
            \resumeItem{Followed \textbf{SOLID} principles and clean code standards, resulting in 40\% improved code quality and extensibility.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed a cloud-native expense tracking solution leveraging \textbf{AWS Lambda}, \textbf{API Gateway}, and \textbf{DynamoDB} for scalable, serverless architecture.}
            \resumeItem{Integrated \textbf{Amazon Textract} for intelligent receipt data extraction, reducing manual input errors by 50\% and improving user efficiency.}
            \resumeItem{Automated user notifications using Python scripts in \textbf{AWS Lambda}, triggering alerts via \textbf{SNS} to enhance user engagement.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Contributed to a project simulating power outages for Hurricane Fiona, building scalable algorithms for \textbf{data-intensive} recovery planning.}
            \resumeItem{Implemented core restoration logic in \textbf{Java} with comprehensive unit testing using \textbf{JUnit} to ensure reliability and correctness.}
            \resumeItem{Applied advanced data structures and algorithms to optimize routing and reduce restoration times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}