\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer and AI/ML practitioner} with 5+ years of experience delivering cloud-native applications and scalable machine learning solutions for financial and enterprise domains. Proficient in \textbf{Python} for data processing, \textbf{Java/Spring Boot} backend services, and \textbf{LLM fine-tuning} using frameworks such as OpenAI APIs and LangChain. Experienced in \textbf{model deployment} using CI/CD pipelines, container orchestration with Kubernetes, and cloud platforms including \textbf{AWS} and \textbf{Azure}. Proven track record working with cross-functional teams at \textbf{TD Bank} and \textbf{Microsoft} to enhance automation, data quality, and AI-powered business solutions.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python (NumPy, Pandas, Scikit-learn, PyTorch), Java, SQL, Bash, C++, C\# \\
     \textbf{AI/ML Frameworks}: OpenAI APIs, LangChain, LangSmith, TensorFlow, PyTorch, MLflow, Kubeflow \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS, Azure (DevOps, Data Factory, AKS, Azure AI Studio), GCP \\
     \textbf{DevOps and MLOps Tools}: Docker, Kubernetes, Jenkins, GitHub Actions, Azure DevOps, Airflow, CI/CD Pipelines \\
     \textbf{Data Processing}: Spark, Jupyter, SQL, Kusto, Real-time Data Processing \\
     \textbf{Development Practices}: Agile/Scrum, Test Automation, Code Reviews, System Design, Scalability Optimization
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Develop and deploy scalable \textbf{machine learning pipelines} for fraud detection data validation using \textbf{Python} and \textbf{SQL} in \textbf{Azure}, improving data quality and enabling automated decision-making.}
        \resumeItem{Built and automated \textbf{CI/CD pipelines} to deploy services with regression and functional tests implemented in \textbf{Java}/Cucumber, enhancing reliability of fraud monitoring systems by 40\%.}
        \resumeItem{Implemented robust fraud monitoring workflows using large-scale transactional datasets, integrating with third-party tools to automate suspicious activity detection and case management.}
        \resumeItem{Collaborated with data engineering and operations teams in an \textbf{Agile} environment for continuous delivery and improvement of scalable, secure backend services and APIs.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led training, evaluation, and tuning of \textbf{large language models (LLMs)} using \textbf{OpenAI APIs} and \textbf{Azure OpenAI}, achieving improved accuracy and latency for enterprise AI services.}
        \resumeItem{Enhanced product quality of \textbf{Azure Cognitive Services} by validating model outputs and APIs, leveraging \textbf{Python}, \textbf{SDKs}, and \textbf{REST APIs} to identify defects and optimize stability.}
        \resumeItem{Collaborated closely with cross-disciplinary teams to design and deploy scalable \textbf{AI/ML microservices} in production environments via container orchestration on Azure Kubernetes Service (AKS).}
        \resumeItem{Implemented monitoring tools to detect model drift and performance degradation, ensuring continuous reliability of AI systems in enterprise workloads.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Accelerated learning and ownership of complex codebase involving \textbf{Azure} cloud services, \textbf{C\#}, and \textbf{C++}, enabling timely delivery of software features and bug fixes.}
        \resumeItem{Contributed to improving code quality and development velocity through application of refactoring techniques and adoption of best practices supported by mentorship and online training.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed interactive frontend applications using \textbf{React} integrated with backend APIs to deliver responsive user experiences, collaborating with engineering and design teams.}
        \resumeItem{Designed, tested, and integrated \textbf{haptic feedback} features for automotive applications, validating hardware-software interaction in real scenarios.}
        \resumeItem{Implemented \textbf{CI/CD pipelines} using \textbf{Jenkins} and automated builds/testing processes, reducing deployment time and increasing integration reliability.}
        \resumeItem{Contributed to infotainment UI and interaction workflows using \textbf{C++}, \textbf{Qt}, and embedded systems tools in a regulated automotive environment.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed high-performance analytical models and core software components using \textbf{Python}, \textbf{Java}, and \textbf{C\#}, improving runtime efficiency by 40\% on multiple business-critical processes.}
        \resumeItem{Built Python applications to preprocess and optimize large datasets, reducing data load times and improving runtime performance for downstream analytics.}
        \resumeItem{Applied \textbf{Lean Six Sigma} methodologies to streamline engineering workflows and enhance product reliability while mentoring team members and serving as \textbf{Scrum Master}.}
        \resumeItem{Collaborated with product management and research teams to translate business requirements into scalable and maintainable enterprise software solutions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}