\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of expertise developing cloud-native applications and backend services, including strong proficiency in \textbf{C\# .NET}, \textbf{SQL}, and \textbf{Python}. Experienced in building robust backend architectures, RESTful APIs, and data integration solutions primarily for \textbf{financial services} and \textbf{capital markets} domains. Skilled with \textbf{DevOps} practices including \textbf{CI/CD pipelines} and working with \textbf{Azure} and \textbf{Databricks} platforms. Proven ability to lead technical design and implement effective solutions under ambiguous business requirements, delivering enhancements, TechDebt resolution, and new business tools.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: C\#, Java, Python, SQL, Bash, PowerShell, C++ \\
     \textbf{Backend and Frameworks}: .NET Core, RESTful APIs, Microservices Architecture, Spring Boot \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS, Plotly, PowerBI (reporting) \\
     \textbf{Databases}: MSSQL Server, PostgreSQL, MySQL, Oracle, MongoDB, Databricks (Spark SQL, Python) \\
     \textbf{Cloud Platforms}: Azure (DevOps, AKS, Data Factory), AWS, GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub, Azure DevOps, CI/CD Pipelines, Autosys, Batch Scripts, SSIS \\
     \textbf{Data Processing}: Databricks, SQL Server Integration Services (SSIS), ETL pipelines \\
     \textbf{Messaging Services}: Solace, MQ \\
     \textbf{Development Practices}: Agile/Scrum, System Design, Code Reviews, JIRA
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained backend services on \textbf{C\# .NET} platform supporting \textbf{capital markets} funding and collateral management applications leveraging \textbf{MSSQL Server} and \textbf{Databricks} integration.}
        \resumeItem{Led functional design and coding efforts for platform enhancements, including DevOps deliverables such as \textbf{CI/CD pipeline} automation, and developed batch scripts and \textbf{Autosys} jobs to improve workflow automation and reliability.}
        \resumeItem{Created and optimized complex \textbf{T-SQL} queries and Python scripts to support business reporting and data transformations, improving processing speed and data quality.}
        \resumeItem{Collaborated with cross-functional teams on platform upgrades and smaller bug fixes under Agile methodology, improving platform stability and feature delivery times.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Azure Cognitive Services} by testing and validating APIs and SDKs, integrating Python and \textbf{C\#} tools to automate data processing using \textbf{Databricks} and \textbf{RESTful WebAPI} calls.}
        \resumeItem{Developed and maintained ETL pipelines using \textbf{Azure Data Factory} and \textbf{Databricks}, incorporating automated tests and monitoring to ensure high data integrity and timely delivery.}
        \resumeItem{Collaborated on performance tuning and deployment pipelines with DevOps teams, leveraging \textbf{GitHub Actions}, containerization, and \textbf{Azure DevOps} services to enhance CI/CD workflows.}
        \resumeItem{Worked alongside product and engineering teams to deliver scalable AI-powered services, applying \textbf{Python} and \textbf{C\#} for backend logic development.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained strong hands-on experience in \textbf{C\#} and \textbf{Azure} cloud services by independently managing user stories and fixing production issues on enterprise applications.}
        \resumeItem{Introduced and implemented code quality improvements and refactoring practices to accelerate development and improve maintainability within the team.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed automotive haptic feedback features using embedded C++ and conducted system-level testing ensuring compliance with strict automotive standards.}
        \resumeItem{Designed interactive frontend applications with React and integrated backend APIs with strong focus on user experience and performance.}
        \resumeItem{Implemented CI/CD pipelines for software builds and tests using \textbf{Jenkins} and source control tools, improving delivery efficiency for automotive infotainment software.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Implemented analytical models and backend components in \textbf{C\#}, \textbf{Python}, and \textbf{SQL}, improving performance of business-critical risk models by 40\%.}
        \resumeItem{Built data transformation tools in Python that reduced large model data size and processing time, supporting efficient downstream computations.}
        \resumeItem{Led a team of engineers and acted as \textbf{Scrum Master}, coordinating Agile development while mentoring new hires and enhancing delivery processes.}
        \resumeItem{Diagnosed and resolved complex production issues through profiling, root cause analysis, and developed robust bug fixes, improving platform reliability.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}