\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Senior Full-Stack Software Engineer} with 5+ years of experience delivering scalable, high-quality, and robust software solutions across cloud-native web applications and backend systems in financial services and enterprise domains. Expert in \textbf{Java/Spring Boot}, \textbf{Node.js/React}, and \textbf{Python} with deep knowledge in designing and maintaining RESTful/GraphQL APIs, database modeling, microservices architecture, containerization, and CI/CD pipelines in \textbf{AWS} and \textbf{Azure} environments. Proven ability to lead technical implementation, promote engineering best practices, and collaborate with cross-functional teams to build performant and resilient full-stack systems with strong ownership and craftsmanship.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, C++, C\#, Typescript, JavaScript, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Spring MVC, Node.js, RESTful and GraphQL APIs, Microservices Architecture, Containerization (Docker) \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS, Responsive Design Principles \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB, Data Modeling \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, Data Factory, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines, Infrastructure as Code (IaC) \\
     \textbf{Data Streaming}: Apache Kafka, Real-time Data Processing, Event-driven Architecture \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, TDD/BDD, Automated Testing, Performance and Penetration Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle, Code Quality and Refactoring
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Created and maintained high-quality, reusable Python and SQL validation scripts in Azure Data Notebooks to ensure data integrity from fraud detection pipelines, significantly enhancing the scalability and reliability of financial transaction processing systems.}
        \resumeItem{Automated regression and functional testing utilizing Java-based test suites with Cucumber and Selenium, adopting BDD practices to deliver robust, maintainable test solutions reducing manual testing efforts by 40\%.}
        \resumeItem{Built and optimized fraud monitoring workflows leveraging large-scale transactional datasets integrated with third-party tools such as OFSAA, driving rapid detection and efficient case management for suspicious activities.}
        \resumeItem{Collaborated within Agile teams to design, deploy, and maintain backend services and APIs, emphasizing engineering best practices, code quality, and scalable solutions for high-impact financial applications.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led quality assurance and testing for \textbf{Azure Cognitive Services} features by implementing SDK, REST API, and Azure AI Studio tests that improved system robustness and performance under real-world workloads.}
        \resumeItem{Streamlined code testing, containerized workflows, and database query optimizations using \textbf{Jupyter}, \textbf{Postman}, \textbf{Java}, \textbf{Python}, \textbf{C\#}, and \textbf{Kusto}, increasing product reliability and operational efficiency by 30\%.}
        \resumeItem{Developed and optimized OpenAI GPT model deployments on Azure OpenAI environment, enhancing inference latency and throughput for scalable AI services through benchmarking and configuration tuning.}
        \resumeItem{Collaborated closely with engineering and product teams to translate requirements into scalable AI-powered solutions, driving production-readiness and adoption for enterprise-grade cognitive service features.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained rapid proficiency in \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure} technologies, taking ownership of sprint deliverables and production bug fixes while maintaining high coding standards.}
        \resumeItem{Introduced code quality improvements and refactoring best practices via mentorship and self-learning, increasing team code maintainability and development velocity by 10-15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led end-to-end development of haptic feedback features for Cadillac vehicles, collaborating closely with cross-functional teams to align technical implementation with product requirements and UX goals.}
        \resumeItem{Developed interactive, performant frontend web application using React with component-based architecture, consuming backend APIs to deliver responsive UX, while applying design system principles for consistency.}
        \resumeItem{Designed and validated haptics functionality on prototype hardware under realistic scenarios, ensuring feature robustness and user experience.}
        \resumeItem{Contributed to automotive infotainment UI workflows utilizing \textbf{Qt}, \textbf{Rhapsody}, \textbf{WeCAN}, and \textbf{C++}, enhancing system responsiveness and reliability.}
        \resumeItem{Implemented and maintained CI/CD pipelines with \textbf{Jenkins}, \textbf{SourceTree}, and \textbf{Bitbucket}, automating builds, tests, and deployments to accelerate development cycles.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed scalable analytical models and backend components using \textbf{Java}, \textbf{C\#}, \textbf{Python}, \textbf{C++}, and \textbf{SQL}, achieving 40\% performance gains across critical insurance analytics applications.}
        \resumeItem{Engineered a high-performance \textbf{Python} application for converting model data into optimized binary formats, reducing data footprint and improving processing efficiency.}
        \resumeItem{Diagnosed and resolved complex production issues including memory leaks and performance bottlenecks, applying thorough root cause analysis and debugging across the full technology stack.}
        \resumeItem{Achieved \textbf{Lean Six Sigma} certification and applied best practices to improve engineering workflows, reduce technical debt, and enhance code quality through systematic process improvements.}
        \resumeItem{Mentored and onboarded new engineers, leading code reviews and pair programming sessions to cultivate an engineering culture focused on quality and craftsmanship.}
        \resumeItem{Partnered with Product Management and Research teams to translate feature requirements into scalable solutions; served as \textbf{Scrum Master} driving Agile delivery and project execution excellence.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}