\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Software Engineer} with 5+ years of experience developing scalable data pipelines and backend systems in financial and enterprise domains. Proficient in \textbf{Python}, \textbf{SQL}, and modern \textbf{Data Engineering} tools including \textbf{Airflow}, \textbf{pandas}, and \textbf{cloud platforms} like \textbf{AWS} and \textbf{Azure}. Skilled in building automated test suites, deploying CI/CD pipelines, and supporting data-driven research workflows. Proven ability to collaborate with cross-functional teams and deliver robust, maintainable solutions with a focus on system reliability and performance optimization.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, SQL, Java, C++, C\#, Bash, PowerShell \\
     \textbf{Data Engineering}: Airflow, pandas, polars, Snowflake workflows, data pipeline development \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation), Azure (Data Factory, DevOps, AKS) \\
     \textbf{Containers and DevOps}: Docker, Kubernetes, Jenkins, CI/CD Pipelines, GitHub Actions, Azure DevOps \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MongoDB, Redis, DynamoDB \\
     \textbf{Machine Learning Infrastructure}: Experience with ML model training workflows, monitoring, and optimization \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS (for dashboard development) \\
     \textbf{Testing and QA}: Automated Testing frameworks, BDD/TDD, Postman, JUnit, Selenium
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Wipro Technologies (TD Bank)}}{\textbf{Oct 2024 -- Present}}
      {Toronto, Canada}{Software Engineer}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and \textbf{SQL} data validation and ingestion scripts in Azure Data Notebooks to ensure integrity of large-scale transactional and fraud detection datasets, improving \textbf{data quality} and downstream analytics.}
        \resumeItem{Built and maintained automated workflows and pipelines for fraud monitoring using third-party tools and custom data processing scripts, increasing speed and accuracy of suspicious transaction detection.}
        \resumeItem{Developed and optimized \textbf{unit} and \textbf{integration tests} with \textbf{Java} and \textbf{Cucumber} using BDD/Selenium frameworks, enhancing \textbf{code quality} and reducing regression testing effort by 40\%.}
        \resumeItem{Collaborated within Agile/Scrum teams to design and optimize complex SQL queries and data transformations supporting fraud analytics, ensuring timely delivery of high-quality releases.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{LTI Mindtree LTD (Microsoft)}}{\textbf{Dec 2023 -- Apr 2024}}
      {Calgary, Canada}{Senior Data Engineer}
      \resumeItemListStart
        \resumeItem{Drove quality improvements for \textbf{Azure Cognitive Services} by rigorously testing and validating features using \textbf{REST APIs}, \textbf{SDKs}, and \textbf{Azure AI Studio}, resolving critical issues to improve reliability and scalability.}
        \resumeItem{Streamlined development and testing workflows by integrating \textbf{Python}, \textbf{Java}, \textbf{Postman}, \textbf{Jupyter}, and \textbf{Kusto} query tools, contributing to 30\% improvement in system observability and robustness.}
        \resumeItem{Led evaluation and performance tuning of large language models on \textbf{Azure OpenAI}, improving inference latency and model effectiveness by 25\% through systematic benchmarking and configuration optimization.}
        \resumeItem{Collaborated with cross-functional teams to validate AI and ML capabilities, supporting production readiness and scalable \textbf{ML Ops} workflows for enterprise deployments.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{ESO}}{\textbf{Jan 2024 -- Apr 2024}}
      {Halifax, Canada}{Software Development Engineer Co-op}
      \resumeItemListStart
        \resumeItem{Acquired expertise in \textbf{C\#}, \textbf{C++}, \textbf{XSLT}, and \textbf{Azure} to own sprint deliverables and resolve production bugs on a complex, multi-technology codebase.}
        \resumeItem{Introduced code quality and refactoring improvements via mentorship and training, contributing to 10-15\% improvement in development velocity and software maintainability across team projects.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{People Tech Group Private Ltd.}}{\textbf{Jan 2022 -- Aug 2022}}
      {Hyderabad, India}{Software Engineer}
      \resumeItemListStart
        \resumeItem{Led development of haptic feedback features for Cadillac vehicles, including design, implementation, and validation to align with automotive safety and UX guidelines.}
        \resumeItem{Developed responsive frontend applications in \textbf{React} integrated with backend APIs, optimizing user experience for automotive design platforms.}
        \resumeItem{Engineered and tested haptics functionality using prototype hardware, validating vibration patterns for realistic driving scenarios to ensure quality and reliability.}
        \resumeItem{Contributed to automotive infotainment UI and interaction features using \textbf{Qt} and \textbf{C++} in embedded HMI systems, enhancing responsiveness and robustness.}
        \resumeItem{Implemented \textbf{CI/CD pipelines} using \textbf{Jenkins}, \textbf{Bitbucket}, and \textbf{SourceTree}, automating builds and testing, reducing deployment time and integration issues.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Verisk Analytics}}{\textbf{Sep 2018 -- Jan 2022}}
      {Hyderabad, India}{Software Engineer II}
      \resumeItemListStart
        \resumeItem{Implemented core analytical components and models in \textbf{Java}, \textbf{Python}, and \textbf{C++}, achieving 40\% performance improvement for business-critical risk assessment models.}
        \resumeItem{Developed a \textbf{Python}-based utility to convert large model data into optimized binary formats, reducing storage size and load times by over 85\%, facilitating faster downstream damage computations.}
        \resumeItem{Diagnosed and resolved complex production issues including memory leaks and bottlenecks using profiling and root cause analysis, increasing system stability and uptime.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process improvements to enhance software development workflows and reduce waste.}
        \resumeItem{Mentored new hires and led as \textbf{Scrum Master}, fostering collaborative Agile development culture and accelerating onboarding processes.}
        \resumeItem{Partnered with Product Management and Research teams to translate requirements into scalable solutions, leading a team of three engineers delivering high-quality releases.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}