\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience designing, building, and optimizing scalable end-to-end web applications and backend services. Proficient in \textbf{Java}, \textbf{Node.js}, \textbf{Python}, and \textbf{React} for developing clean, testable code and RESTful APIs. Experienced with relational and NoSQL databases including \textbf{PostgreSQL}, \textbf{MySQL}, \textbf{MongoDB}, and caching systems like \textbf{Redis}. Skilled in deploying cloud-native applications using \textbf{AWS}, \textbf{Azure}, containerization technologies such as \textbf{Docker} and \textbf{Kubernetes}, and establishing CI/CD pipelines. Adept at collaborating with cross-functional teams, contributing to system design discussions, and mentoring peers to build scalable, reliable systems that deliver impactful business value.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, JavaScript, TypeScript, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, Express, RESTful APIs, Microservices Architecture \\
     \textbf{Frontend}: React, JavaScript, TypeScript, HTML/CSS \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (AKS, DevOps, Data Factory), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Testing and QA}: JUnit, Cucumber, Selenium, Jest, Postman, TDD/BDD, Automated Testing, Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Designed and implemented scalable backend services and REST APIs using \textbf{Python} and \textbf{SQL} to validate and process large fraud detection datasets, improving data quality and system reliability.}
        \resumeItem{Automated end-to-end regression and functional testing with \textbf{Java}-based \textbf{Cucumber} and \textbf{Selenium} test suites applying BDD methodology, reducing testing cycles by 40\% and enhancing feature stability.}
        \resumeItem{Collaborated cross-functionally in Agile/Scrum teams to build fraud monitoring workflows consuming large-scale transactional data, supporting case creation and tracking suspicious activities through third-party tools like OFSAA.}
        \resumeItem{Optimized complex SQL queries and tuned system performance, contributing to improved scalability and maintainability of critical financial applications serving thousands of users daily.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Azure Cognitive Services} performance by testing SDKs, \textbf{REST APIs}, and AI workloads in \textbf{Azure AI Studio}, ensuring production readiness and system scalability.}
        \resumeItem{Improved observability and reliability for containerized microservices by automating testing and analysis workflows using \textbf{Jupyter}, \textbf{Postman}, \textbf{Java}, and \textbf{Python}, increasing product stability by 30\%.}
        \resumeItem{Led model training and optimization on \textbf{Azure OpenAI} services, benchmarking \textbf{OpenAI GPT} models for latency and throughput improvements, aligning with enterprise deployment standards.}
        \resumeItem{Partnered with engineering and product teams in design discussions to architect scalable cognitive AI features for enterprise applications, enhancing overall service maintainability and performance.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly mastered \textbf{Azure} cloud services and frontend/backend technologies including \textbf{C\#}, \textbf{C++}, \textbf{XSLT}, and \textbf{XML} to contribute independently to sprint deliverables and production bug fixes in a fast-paced Agile environment.}
        \resumeItem{Introduced code quality improvements and refactoring strategies through self-directed learning and mentorship, helping the team enhance code maintainability and delivery speed by up to 15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led frontend and backend development of haptic feedback features for Cadillac vehicles using \textbf{React} and integrated APIs, delivering seamless UX aligned with safety and brand standards.}
        \resumeItem{Developed interactive frontend components with \textbf{React} and modern architectures, ensuring responsive UI and smooth integration with backend services in a complex automotive infotainment ecosystem.}
        \resumeItem{Designed and validated haptics on prototype hardware, refining vibration patterns for realistic driving experience prior to vehicle integration.}
        \resumeItem{Contributed to automotive HMI workflows and UI using \textbf{Qt}, \textbf{C++}, and \textbf{WeCAN}, enhancing system responsiveness and reliability.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines with \textbf{Jenkins}, \textbf{Bitbucket}, and \textbf{SourceTree} to automate build and test processes for automotive software, improving deployment efficiency and collaboration.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed scalable analytical models and backend components using \textbf{Java}, \textbf{Python}, \textbf{C\#}, \textbf{C++}, and \textbf{SQL}, boosting performance by 40\% across multiple business-critical applications.}
        \resumeItem{Created a \textbf{Python}-based tool for converting large data sets into optimized binary formats, reducing file size by 90\% and improving downstream processing speed significantly.}
        \resumeItem{Diagnosed and remedied critical production issues like memory leaks and bottlenecks through profiling and root cause analysis, ensuring system robustness.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification to implement process improvements, reducing development cycle inefficiencies and enhancing team productivity.}
        \resumeItem{Mentored junior engineers through onboarding, pair programming, and code reviews, strengthening team capabilities and engineering culture.}
        \resumeItem{Collaborated with Product Management and Research teams to refine requirements and design scalable, high-performance features; acted as \textbf{Scrum Master} leading a team of three engineers for multiple successful releases.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}