\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Data Engineer} and \textbf{Full-Stack Software Engineer} with 5+ years of experience building end-to-end data processing pipelines, reporting solutions, and backend services for enterprise organizations. Skilled in \textbf{SQL/MySQL}, \textbf{Bash scripting} in \textbf{Linux} environments, and \textbf{Python/Java}, with a strong foundation in \textbf{ETL development}, performance optimization, and data integrity validation. Proven ability to develop and optimize complex SQL queries and automate data workflows, ensuring high data quality and system reliability in dynamic, fast-paced environments.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: SQL (MySQL, PostgreSQL), Bash, Python, Java, C++, C\#, PowerShell \\
     \textbf{ETL and Scripting}: Bash scripting, Cron jobs, Data extraction, transformation, and loads in Linux/Unix environments \\
     \textbf{Databases}: MySQL, PostgreSQL, Oracle, MSSQL, MongoDB, Redis \\
     \textbf{Data Validation}: Data quality checks, anomaly detection, data integrity validation using SQL and scripts \\
     \textbf{Tools}: Azure Data Notebooks, Jupyter, Postman, Git, Jenkins, Docker, Kubernetes \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, DynamoDB), Azure (Data Factory, DevOps, AKS) \\
     \textbf{Data Analysis and Reporting}: MS Excel (pivot tables, vlookup, charts/graphs), performance tuning using query explain plans \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, Testing (JUnit, Selenium, Cucumber), CI/CD Pipelines
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{\textbf{Developed and optimized complex SQL queries and Python data validation scripts to improve data quality} in fraud detection pipelines, ensuring integrity of transactional data loaded in cloud databases.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber, Selenium, and BDD practices, reducing manual testing effort by 40\% and increasing feature reliability.}
        \resumeItem{Built and maintained fraud monitoring workflows leveraging large-scale transactional datasets and third-party tools such as OFSAA, enabling rapid detection, case creation, and tracking of suspicious financial transactions.}
        \resumeItem{Delivered high-quality releases by collaborating within cross-functional teams following Agile methodologies and optimizing SQL queries based on explain plans to improve performance.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Rigorously tested and validated cloud-based AI services using SDKs, REST APIs, and Azure AI Studio, improving data reliability and service stability.}
        \resumeItem{Streamlined code testing, database analysis, and container workflows using Jupyter, Postman, Visual Studio, Java, Python, C\#, and Kusto queries, enhancing observability by 30\%.}
        \resumeItem{\textbf{Developed Bash scripts and automated ETL workflows in Linux environments to efficiently extract, transform, and load data} between systems, ensuring timely data availability for reporting.}
        \resumeItem{Collaborated with engineering and product teams to deliver scalable Azure AI capabilities, validating next-generation cognitive services.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Ramped up on XSLT, XML, C\#, C++, and Azure within the first month on a complex codebase, enabling independent ownership of sprint user stories and production bug fixes.}
        \resumeItem{Leveraged Pluralsight courses and mentorship programs to introduce code-quality and refactoring improvements, helping the team deliver key Medic1 milestones on time and increasing development velocity by an estimated 10 to 15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of new haptic feedback features for Cadillac vehicles from concept to integration, including requirements analysis, implementation, and client communication to align UX behavior with safety and brand guidelines.}
        \resumeItem{Developed interactive frontend application for Cadillac design platform using React with modern component architecture, integrating with backend APIs to deliver responsive user experience while collaborating with design and engineering teams.}
        \resumeItem{Designed and tested haptics functionality on prototype hardware, validating vibration patterns and timing in realistic driving scenarios before in-car integration.}
        \resumeItem{Contributed to infotainment UI and interaction workflows using Qt, Rhapsody, WeCAN, and C++ in a complex automotive HMI environment, improving responsiveness and reliability of production systems.}
        \resumeItem{Implemented CI/CD pipelines for automotive software using Jenkins, SourceTree, and Bitbucket, automating builds and tests and reducing deployment issues across teams.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Implemented next-generation analytical models and core components using Java, C\#, Python, C++, SQL, data structures, and algorithms, delivering an average 40\% performance improvement across 5+ business-critical models.}
        \resumeItem{Built a Python-based application to convert large model data into optimized binary formats, reducing file sizes from approx. 2GB to 200MB and significantly cutting load and processing times.}
        \resumeItem{\textbf{Developed and optimized complex SQL stored procedures and queries to support critical data reporting workloads}, improving data processing speed and accuracy.}
        \resumeItem{Diagnosed and resolved complex production issues, including critical memory leaks and performance bottlenecks, using systematic debugging and profiling techniques.}
        \resumeItem{Earned Lean Six Sigma certification and applied process-improvement practices to streamline development workflows and reduce waste.}
        \resumeItem{Mentored new hires and led a team of engineers as Scrum Master, coordinating Agile development cycles and enhancing team productivity.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}