\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience designing and developing intuitive, AI-assisted web applications and backend services. Expert in \textbf{Python}, \textbf{Typescript}, \textbf{React}, and \textbf{Node.js}, with a strong background in implementing scalable RESTful and GraphQL APIs and integrating with databases such as PostgreSQL and MongoDB. Experienced in collaborating closely with product, design, and machine learning teams to create user-centric, responsive applications that improve customer engagement and reduce churn. Skilled in modern cloud platforms including \textbf{AWS} and \textbf{Azure}, with a focus on performance optimization and maintainable, reusable code.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Typescript, Java, SQL, C++, C\#, Bash \\
     \textbf{Backend and Frameworks}: Django, Node.js, Spring Boot, RESTful APIs, GraphQL, Microservices Architecture \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (Lambda, S3, EC2), Azure (DevOps, Cognitive Services, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, CI/CD Pipelines \\
     \textbf{AI and Data Processing}: OpenAI GPT, Azure AI Studio, Data Validation, ETL, Performance Tuning \\
     \textbf{Testing and QA}: Cucumber, Selenium, JUnit, Postman, TDD/BDD, Automated Testing \\
     \textbf{Development Practices}: Agile/Scrum, System Design, Scalability, Code Reviews, JIRA
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and optimized \textbf{Python}-based data validation scripts and \textbf{SQL} queries within Azure Data Notebooks to ensure high-quality, reliable input data for fraud detection pipelines, improving accuracy and system stability.}
        \resumeItem{Automated regression and functional testing using \textbf{Java}, \textbf{Cucumber}, and \textbf{BDD} principles, decreasing manual testing time by 40\% and improving application reliability and user experience.}
        \resumeItem{Maintained and enhanced fraud monitoring workflows using large transactional datasets, integrating backend services and supporting frontend components to accelerate detection and resolution of fraudulent activities.}
        \resumeItem{Collaborated closely with cross-functional teams using Agile/Scrum methodologies to design and deliver high-performance, maintainable backend and frontend solutions, focusing on end-user usability and system responsiveness.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led quality improvements for \textbf{Azure Cognitive Services} by end-to-end testing and validation of new features using \textbf{REST APIs}, \textbf{SDKs}, and \textbf{Azure AI Studio}, significantly enhancing performance and stability of AI platforms.}
        \resumeItem{Streamlined code testing, database queries, and container-based workflows using \textbf{Jupyter}, \textbf{Python}, \textbf{C\#}, and \textbf{Kusto}, improving observability and production readiness by 30\%.}
        \resumeItem{Pioneered fine-tuning and deployment of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, boosting inference speed and accuracy by 25\%, directly contributing to AI-powered product features engaging end users.}
        \resumeItem{Collaborated with product and engineering teams to build scalable AI-driven services, enabling novel integration architecture and delivering intuitive user experiences.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained expertise in \textbf{C\#}, \textbf{XSLT}, \textbf{XML}, and \textbf{Azure} technologies to independently deliver sprint user stories and resolve production issues, enhancing product usability and reliability.}
        \resumeItem{Introduced code-quality improvements and refactoring practices, contributing to successful delivery of key healthcare software modules under tight deadlines.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed interactive frontend applications for Cadillac's design platform using \textbf{React} and modern component architecture, ensuring a responsive and user-friendly interface aligned with client UX expectations.}
        \resumeItem{Led end-to-end design and integration of new haptic feedback features, collaborating with cross-functional teams to align product functionality with safety and brand standards.}
        \resumeItem{Implemented and tested software components using \textbf{Qt}, \textbf{C++}, and integration tools in a complex automotive infotainment environment improving system responsiveness and reliability.}
        \resumeItem{Streamlined CI/CD automation pipelines with \textbf{Jenkins}, reducing build and deployment times and enhancing software integration processes across teams.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented high-performance analytical models and core components using \textbf{Java}, \textbf{Python}, \textbf{C++}, and \textbf{SQL}, improving execution efficiency by 40\% and scalability for insurance analytics.}
        \resumeItem{Built a \textbf{Python}-based data transformation tool that optimized large-scale model data storage and retrieval by reducing file sizes and speeding up loading times, enhancing downstream processing efficiency.}
        \resumeItem{Performed root cause analysis and debugging of critical production issues including memory leaks and performance bottlenecks, increasing system stability and client satisfaction.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process improvements to development workflows, increasing team productivity and product quality.}
        \resumeItem{Mentored engineers in backend best practices and Agile methodologies, acted as \textbf{Scrum Master}, and led a team of three engineers to deliver robust, user-centered enterprise software solutions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}