\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience including key exposure to \textbf{QA and testing methodologies}, \textbf{automation}, and \textbf{system integration testing} in complex domains. Skilled at collaborating with global teams and managing defect triage, root cause analysis, and production support to ensure \textbf{quality and SLA compliance}. Proven ability to lead testing efforts in enterprise environments with expertise in \textbf{Java, Python, Selenium}, and defect tracking tools such as \textbf{JIRA} and \textbf{HP ALM}, delivering robust solutions aligned with business needs and continuous improvement initiatives.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, SQL, Bash, C++, C\#, PowerShell \\
     \textbf{Testing and QA Tools}: Selenium, SoapUI, JUnit, Cucumber, HP ALM, JIRA, Postman, Automated Regression Testing, Performance Testing \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, CI/CD Pipelines, Maven, Gradle \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, Root Cause Analysis (RCA), Incident Management, Defect Triage \\
     \textbf{Other}: Telecom OSS/BSS knowledge, Billing Lifecycle Operations, UAT, Regression and System Integration Testing
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Lead end-to-end \textbf{QA and testing} strategy for critical billing and fraud detection systems including invoice validation, usage verification, and dispute management, ensuring adherence to business requirements and SLA targets.}
        \resumeItem{Automated and executed \textbf{UAT, regression}, and \textbf{system integration testing} workflows using \textbf{Selenium} and \textbf{Cucumber}, enhancing detection of defects and reducing test cycle times by 40\%.}
        \resumeItem{Collaborated extensively with development, QA, and business stakeholders via \textbf{JIRA} and Azure DevOps to manage defect triage, streamline releases, and facilitate continuous quality improvements.}
        \resumeItem{Performed detailed \textbf{root cause analysis (RCA)} on critical production billing issues, driving permanent fixes that lowered post-release defect rates and improved system stability.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Data Engineer}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led rigorous testing and quality validation of cloud AI services using \textbf{REST APIs}, \textbf{Postman}, and \textbf{SDKs}, uncovering defects and enhancing reliability critical for enterprise-scale deployments.}
        \resumeItem{Optimized automated testing and infrastructure workflows with containerized environments, leveraging \textbf{Jupyter}, \textbf{Python}, and \textbf{Kusto} queries, improving issue detection efficiency by 30\%.}
        \resumeItem{Facilitated cross-team collaboration for product validation, incorporating feedback from QA and business teams to ensure features met high-quality standards in live cloud environments.}
        \resumeItem{Documented and tracked defects and improvements using \textbf{JIRA}, contributing to faster resolution times and better communication across distributed teams.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Development Engineer Co-op}{\textbf{Jan 2024 -- Apr 2024}}
      {ESO}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Developed test automation scripts and conducted manual testing of \textbf{C\#} and \textbf{C++} components within the \textbf{Azure} environment, ensuring smooth sprint deliveries and higher feature quality.}
        \resumeItem{Utilized industry best practices and mentorship to improve code quality and test coverage, accelerating feedback loops and minimizing production bugs.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{\textbf{Jan 2022 -- Aug 2022}}
      {People Tech Group Private Ltd.}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Contributed to integration and functional testing of complex automotive infotainment systems, aligning user experience with safety and brand compliance requirements.}
        \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins}, enhancing continuous testing and deployment for automotive software systems, reducing integration issues and increasing delivery speed.}
        \resumeItem{Developed and validated embedded software features including \textbf{haptics} on prototype hardware, performing detailed tests to ensure robustness under real-world conditions.}
        \resumeItem{Participated in requirement analysis and collaborated closely with cross-functional teams to test and deliver quality software in automotive HMI platforms.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer II}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and executed extensive test cases for next-generation analytical models and core services, improving quality and reducing performance bottlenecks in insurance risk calculations.}
        \resumeItem{Automated data conversion and validation processes with Python, significantly improving processing speed and accuracy, supporting robust data ingestion pipelines.}
        \resumeItem{Conducted \textbf{production support} including \textbf{L2/L3 incident management}, defect triage, and root cause analysis, effectively minimizing downtime and improving system reliability.}
        \resumeItem{Applied \textbf{Lean Six Sigma} methodologies to enhance QA and development processes, contributing to decreased defect rates and increased team productivity.}
        \resumeItem{Mentored junior engineers and led Agile \textbf{Scrum Master} activities, fostering a culture of quality, accountability, and continuous improvement.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}