\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Software Engineer} with 5+ years of experience designing, developing, and optimizing scalable, secure, and high-performance \textbf{distributed systems} and \textbf{microservices} architectures primarily for financial services and enterprise platforms. Skilled in \textbf{Java/Spring Boot}, \textbf{Python}, and \textbf{C++}, with strong expertise in building cloud-native solutions on \textbf{AWS} and \textbf{Azure}, integrating relational and NoSQL databases, and applying event-driven designs. Proven ability to mentor teams and collaborate cross-functionally to ensure regulatory compliance, system reliability, and high-quality delivery at \textbf{TD Bank}, \textbf{Microsoft}, and other global organizations.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: \textbf{Java, Python, C++, C\#}, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: \textbf{Spring Boot, Microservices Architecture, RESTful APIs, Event-Driven Design}, Node.js \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS \\
     \textbf{Databases}: \textbf{PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB} \\
     \textbf{Cloud Platforms}: \textbf{AWS} (EC2, Lambda, S3, CloudFormation, DynamoDB), \textbf{Azure} (DevOps, Data Factory, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Data Streaming}: \textbf{Apache Kafka}, Real-time Data Processing, Event-driven Architecture \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, TDD/BDD, Automated Testing, Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Designed and developed \textbf{cloud-native, scalable microservices} for fraud detection pipelines, implementing Python and SQL-based validation scripts in Azure Data Notebooks to ensure \textbf{data integrity} and \textbf{regulatory compliance}.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber, Selenium, and BDD practices, reducing manual effort by 40\% and increasing feature reliability.}
        \resumeItem{Built and optimized fraud monitoring workflows for large-scale transactional datasets with third-party tools such as OFSAA, enabling timely detection, case creation, and tracking of suspicious \textbf{financial transactions} supporting millions of users.}
        \resumeItem{Collaborated in Agile teams focusing on \textbf{performance optimization}, system \textbf{scalability}, and ensuring compliance with security standards during design and deployment phases.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Azure Cognitive Services} reliability by testing and validating new features via SDKs, REST APIs, and Azure AI Studio, resolving critical defects to improve service stability in regulated enterprise environments.}
        \resumeItem{Utilized Jupyter, Postman, Visual Studio, Java, Python, C\#, and Kusto queries to streamline testing and data workflows, increasing product observability and robustness by 30\%.}
        \resumeItem{Led training, evaluation, and performance tuning of OpenAI GPT models on \textbf{Azure OpenAI}, optimizing real-time service latency and throughput by 25\%, aligned with enterprise-grade security and compliance requirements.}
        \resumeItem{Collaborated with cross-functional teams to design scalable, compliant AI services integrated into large-scale \textbf{cloud-native platforms} supporting high availability and fault tolerance.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained proficiency in \textbf{C++}, \textbf{C\#}, XSLT, XML, and Azure in a regulated environment, taking ownership of sprint deliverables and critical bug fixes.}
        \resumeItem{Initiated code-quality improvements leveraging best practices and refactoring techniques, contributing to enhanced system maintainability and velocity by 10-15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led design and development of haptic feedback modules for Cadillac vehicles, aligning software with client requirements and automotive safety standards.}
        \resumeItem{Developed responsive frontend features using React and integrated backend APIs, enhancing UI reliability and user experience under stringent automotive regulations.}
        \resumeItem{Tested and validated haptics on prototype hardware in real driving scenarios, ensuring performance and safety compliance.}
        \resumeItem{Contributed to infotainment UI and workflows using \textbf{C++}, Qt, Rhapsody, and WeCAN, improving system robustness and scalability within complex embedded environments.}
        \resumeItem{Implemented CI/CD pipelines via Jenkins and Bitbucket, optimizing build and test automation for frequent, reliable deployments.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed and optimized financial analytical models using \textbf{Java}, \textbf{C++}, Python, and \textbf{SQL}, achieving average 40\% performance improvements crucial to business-critical decision systems.}
        \resumeItem{Built a Python application to convert large datasets into optimized binary formats, reducing data storage and processing time by 90\%.}
        \resumeItem{Resolved critical memory and performance issues for large-scale distributed systems through advanced profiling and debugging, enhancing system stability and compliance with SLAs.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and improved engineering workflows, reducing development cycle times and defects.}
        \resumeItem{Mentored engineers in coding standards, system design, and best practices for scalability, acting as Scrum Master and leading a team aligned with product and architectural strategies.}
        \resumeItem{Collaborated proactively with Product Management and Research to ensure alignment of engineering deliverables with strategic business and regulatory requirements.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {\textbf{Dalhousie University}, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {\textbf{GRIET}, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}