\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience designing, developing, and deploying scalable, high-performance backend systems and cloud-native web applications, specializing in \textbf{distributed systems}, \textbf{service-oriented architecture}, and \textbf{microservices}. Skilled in \textbf{Java/Spring Boot}, \textbf{Python}, \textbf{Node.js}, and experienced with \textbf{AWS} and \textbf{Kubernetes} environments. Proven ability to lead engineering teams, deliver complex technical projects, and foster a culture of quality and ownership. Strong collaborator with cross-functional teams including Product, Design, and Data Science, with a focus on driving user growth and engagement through intelligent, scalable services.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, Kotlin, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Spring MVC, Node.js, RESTful APIs, Microservices, Event-Driven Architecture \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS \\
     \textbf{Databases}: MySQL, PostgreSQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms \& Infrastructure}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (AKS, DevOps, Data Factory), Kubernetes, Docker \\
     \textbf{DevOps and Tools}: Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Data Streaming \& Processing}: Apache Kafka, Real-time Processing, Event-driven services \\
     \textbf{Testing}: JUnit, Cucumber, Postman, TDD/BDD, Automated Testing, Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Review, System Design, Scalability, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained highly available backend validation and monitoring services in \textbf{Python} and \textbf{SQL} using Azure infrastructure to ensure data integrity in fraud detection pipelines, enhancing system reliability and supporting large-scale transactional workflows.}
        \resumeItem{Automated regression and functional testing with Java-based frameworks such as \textbf{Cucumber} and Selenium under \textbf{BDD}, boosting test coverage and delivery confidence.}
        \resumeItem{Built scalable workflows integrating large datasets and third-party systems like OFSAA for real-time fraud case creation and tracking, improving responsiveness of fraud monitoring platforms.}
        \resumeItem{Collaborated closely with cross-functional teams following Agile practices to deliver robust solutions with optimized SQL queries and backend improvements, supporting business-critical fraud detection services and scalability.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led testing and quality assurance of new \textbf{Azure Cognitive Services} features using SDKs, REST APIs, and \textbf{Azure AI Studio}, identifying and resolving critical defects for stable, scalable cloud AI services.}
        \resumeItem{Optimized code testing, database queries, and containerized workflows across \textbf{Java}, \textbf{Python}, \textbf{C\#}, and Kusto data queries, improving observability and fault tolerance of distributed service components by 30\%.}
        \resumeItem{Implemented scalable and efficient training, evaluation, and benchmarking of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, reducing inference latency for real-time applications with improved performance metrics.}
        \resumeItem{Partnered with engineering, product, and data science teams to validate and scale next-gen AI services deployed in production environments, ensuring extensible and maintainable system architectures.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Quickly gained expertise in \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure} technologies, contributing to feature development and production fixes with strong ownership and delivery focus.}
        \resumeItem{Promoted code quality and refactoring improvements through learning initiatives, improving team development velocity by 10-15\% and aligning development practices with scalable software design principles.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led end-to-end development of haptic feedback systems for Cadillac vehicles, managing requirements, implementation, and client communication to ensure seamless integration and compliance with safety standards.}
        \resumeItem{Developed an interactive React frontend integrated with backend APIs to provide intuitive configuration for automotive design, enhancing user experience and responsiveness.}
        \resumeItem{Designed and validated \textbf{haptics} on prototypes for precise vibration timing and pattern fidelity, enabling reliable in-car user feedback systems.}
        \resumeItem{Worked with \textbf{Qt}, \textbf{Rhapsody}, and \textbf{C++} to build responsive infotainment UI components in a distributed automotive software ecosystem.}
        \resumeItem{Established automated CI/CD pipelines leveraging \textbf{Jenkins} and Bitbucket, reducing build times and increasing deployment safety in multi-team automotive software releases.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed scalable analytical models and core components in \textbf{Java}, \textbf{C\#}, and \textbf{Python}, improving performance by 40\% across multiple business-critical distributed systems.}
        \resumeItem{Built a Python application to convert large datasets into optimized binary formats, reducing data size by 90\% and minimizing load and processing times for downstream services.}
        \resumeItem{Led root cause analysis and resolution of complex production issues including memory leaks and performance bottlenecks in high-availability distributed applications.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process improvements to enhance software development lifecycle efficiency and quality.}
        \resumeItem{Mentored new engineers through onboarding, code reviews, and pairing, fostering a culture of ownership, best practices, and quality across the team.}
        \resumeItem{Collaborated with Product Management and Research on feature requirement refinement and delivered scalable backend solutions; served as \textbf{Scrum Master}, leading agile ceremonies and sprint planning.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}