\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Software Engineer} with 5+ years of experience in software development and operational automation. Skilled in \textbf{Python} software engineering, cloud-native systems, container orchestration with \textbf{Kubernetes}, and infrastructure automation using \textbf{DevOps} and \textbf{IaC} tools across \textbf{AWS} and \textbf{Azure}. Strong experience with \textbf{Linux} systems, networking, and storage fundamentals. Proven ability to design, implement, and maintain scalable and reliable systems in fast-paced, high-pressure environments supporting mission-critical global services. Passionate about \textbf{automation}, \textbf{open source} technologies, and evolving modern infrastructure to optimize enterprise operations.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Infrastructure \& Automation}: Kubernetes, Docker, Terraform, Ansible, Jenkins, CI/CD Pipelines, IaC \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, AKS, Data Factory), GCP \\
     \textbf{Operating Systems}: Linux (Ubuntu, RedHat), Linux Networking, Software-Defined Storage \\
     \textbf{Development}: RESTful APIs, Microservices, Agile/Scrum, Code Reviews, System Design \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
     \textbf{Testing \& Monitoring}: Automated Testing, Performance Testing, JUnit, Cucumber, Prometheus, Grafana \\
     \textbf{Version Control \& Collaboration}: Git, GitHub Actions, Azure DevOps \\
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and automated Python-based validation scripts and data workflows in cloud environments to enhance data quality and system reliability, applying automation principles aligned with \textbf{DevSecOps} practices.}
        \resumeItem{Designed and maintained monitoring workflows for large-scale financial transactional data, improving real-time anomaly detection and alerting relevant to mission-critical production services.}
        \resumeItem{Worked collaboratively with cross-functional teams following Agile methodologies, ensuring smooth releases and operational stability for cloud services.}
        \resumeItem{Implemented continuous integration pipelines integrating code quality checks and automated testing to enhance reliability and operational efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Contributed to backend testing and automation for \textbf{Azure Cognitive Services} leveraging \textbf{Python} SDKs and APIs to validate AI models and infrastructure reliability under production scenarios.}
        \resumeItem{Built containerized workflows using \textbf{Jupyter}, \textbf{Postman}, and scripting languages to automate validation and observability tasks supporting cloud infrastructure.}
        \resumeItem{Collaborated with engineering teams to improve scalability and resiliency of cloud AI services, aligning to best practices in \textbf{open source infrastructure stack} and automated deployment approaches.}
        \resumeItem{Enhanced performance of AI workloads through systematic evaluation and tuning, incorporating telemetry and metrics-driven diagnostics.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained proficiency in \textbf{Azure} cloud services and backend development with \textbf{C\#}, \textbf{C++}, and \textbf{XML/XSLT}, enabling independent development and debugging of cloud-integrated services.}
        \resumeItem{Introduced code refactoring and build automation improvements that increased development productivity and software quality in sprint cycles.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led full software development lifecycle for automotive HMI features, integrating frontend React apps with backend APIs and ensuring alignment with performance and safety standards.}
        \resumeItem{Developed code and performed integration testing in complex embedded environments using \textbf{C++}, \textbf{Qt}, and \textbf{Rhapsody} within automotive infotainment systems.}
        \resumeItem{Implemented CI/CD pipelines using \textbf{Jenkins} and source control tools, automating build and deployment processes for embedded software modules.}
        \resumeItem{Communicated effectively with multidisciplinary teams to gather requirements and deliver high-quality software components meeting client needs.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed Python-based tools and backend components as part of critical analytical model systems, improving performance and reliability by up to 40\%, incorporating efficient data processing and storage optimizations.}
        \resumeItem{Authored automation scripts to convert large datasets into optimized binary formats, reducing loading times significantly for scalable compute systems.}
        \resumeItem{Troubleshot and resolved complex production issues in a high-availability environment, using profiling and root cause analysis to maintain service uptime.}
        \resumeItem{Facilitated Agile ceremonies and acted as \textbf{Scrum Master} for engineering teams to ensure continuous delivery of high-quality software aligned with evolving requirements.}
        \resumeItem{Mentored junior engineers on best practices in Python software development and operational excellence in a data-driven environment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}