\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \enspace | \enspace +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience designing and building backend systems and cloud-native applications. Proficient in \textbf{relational database schema design, SQL Server and PostgreSQL}, with proven expertise in \textbf{API design, code refactoring, and incremental system improvements}. Skilled in backend development with \textbf{Java/Spring Boot}, \textbf{Node.js}, and \textbf{Python}, and in implementing modular, maintainable architectures. Strong collaborator effective at simplifying complex, legacy distributed systems and delivering high-performance, resilient software solutions aligned with business and infrastructure needs.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices, Modular Monolith \\
     \textbf{Databases}: PostgreSQL, SQL Server, MySQL, Oracle, MongoDB \\
     \textbf{Cloud Platforms}: AWS, Azure (including Azure DevOps, Data Factory, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Terraform, CI/CD Pipelines \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, Automated Testing, TDD/BDD \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, Schema Design, Query Optimization, Observability (logging, metrics) \\
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{Oct 2024 -- Present}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{Python} and \textbf{SQL} validation scripts in Azure to verify incoming data integrating with backend pipelines, significantly improving data quality and system robustness.}
        \resumeItem{Automated regression and functional tests with \textbf{Java}, \textbf{Cucumber}, and \textbf{BDD} methods, reducing manual testing and ensuring reliability of critical flows.}
        \resumeItem{Designed and optimized complex \textbf{SQL queries} for transactional workflows, collaborating with cross-functional Agile teams to deliver stable backend services.}
        \resumeItem{Led backend API enhancements improving performance and maintainability, contributing to a modular and well-structured codebase aligned with business goals.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{Dec 2023 -- Apr 2024}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Enhanced data processing pipelines for \textbf{Azure Cognitive Services} using \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Postman}, improving observability, logging, and performance tuning.}
        \resumeItem{Maintained and refactored backend codebase using \textbf{Java}, \textbf{Python}, and \textbf{C\#}, improving schema discipline and reducing technical debt in a complex distributed system.}
        \resumeItem{Pioneered training and optimization of \textbf{OpenAI GPT} models in Azure environment, improving latency and throughput for AI-powered services.}
        \resumeItem{Collaborated with engineering teams to incrementally migrate and consolidate systems, ensuring stability and predictable, well-modeled backend behavior in production.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{Jan 2024 -- Apr 2024}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained proficiency in \textbf{C\#}, \textbf{Azure}, and legacy \textbf{XSLT}/\textbf{XML} codebase, contributing to production bug fixes and refactoring to improve maintainability and code clarity.}
        \resumeItem{Introduced best practices to enforce schema and code quality, helping the team deliver reliable backend services aligned with strict stability requirements.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{Jan 2022 -- Aug 2022}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led full-stack development for automotive infotainment systems, including API design and integration, emphasizing robust, scalable backend services using \textbf{React} and \textbf{C++}.}
        \resumeItem{Implemented and tested embedded haptics functionality with real-time constraints, validating safety-critical vibration patterns for vehicle UX.}
        \resumeItem{Built \textbf{CI/CD pipelines} using \textbf{Jenkins} and \textbf{Bitbucket} for automotive software, automating deployment and reducing integration issues.}
        \resumeItem{Contributed to architectural improvements simplifying complex distributed systems for better modularity and reliability within automotive software stacks.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{Sep 2018 -- Jan 2022}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented data-intensive backend systems using \textbf{Java}, \textbf{C\#}, \textbf{Python}, and \textbf{SQL}, focusing on schema discipline and query optimization to improve performance by 40\%.}
        \resumeItem{Developed \textbf{Python} tools converting large datasets into optimized binary formats, reducing processing times and improving data pipeline efficiency.}
        \resumeItem{Diagnosed and mitigated production issues including memory and performance bottlenecks through root cause analysis and systematic profiling.}
        \resumeItem{Led \textbf{Lean Six Sigma} process improvements, mentoring new hires and fostering an engineering culture focused on scalable and maintainable backend solutions.}
        \resumeItem{Collaborated closely with product and research teams while acting as \textbf{Scrum Master}, orchestrating incremental backend improvements in legacy distributed systems.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}