\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Data Engineer} with 5+ years of experience in data extraction, transformation, and validation across enterprise cloud and on-premise systems including \textbf{Azure}, \textbf{Oracle}, and \textbf{SAP}. Skilled in \textbf{Celonis Process Mining}, \textbf{SQL/PQL scripting}, and \textbf{Python} (including \textbf{Pandas}, \textbf{NumPy}, \textbf{Matplotlib}), with proven expertise building ETL pipelines and integrating process mining insights to enhance operational efficiency. Experience collaborating with technical and non-technical stakeholders to identify inefficiencies and create actionable KPIs and dashboards using \textbf{Power BI} and \textbf{Tableau}. Strong foundation in \textbf{ERP systems} and process improvement techniques.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: SQL, PQL, Python (Pandas, Numpy, Seaborn, Matplotlib, Sklearn), Java, Bash \\
     \textbf{Process Mining}: Celonis, basic knowledge of Signavio \\
     \textbf{Databases/ETL}: Oracle, MSSQL, PostgreSQL, Azure Data Factory, Dataflows, ETL/ELT pipelines \\
     \textbf{BI Tools}: Power BI, Tableau \\
     \textbf{Cloud Platforms}: Azure (Data Factory, DevOps), AWS (EC2, Lambda, S3), Kubernetes \\
     \textbf{Systems Knowledge}: ERP (SAP, Oracle), CRM (Salesforce, ServiceNow), ITSM tools (BMC Remedy), Process Mapping \\
     \textbf{DevOps and Tools}: Git, Jenkins, Docker, Azure DevOps \\
     \textbf{Methodologies}: Agile, Scrum, Lean Six Sigma, Process Improvement, Automated Testing
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{Python} and \textbf{SQL validation scripts} in Azure Data Notebooks to validate data ingestion and accuracy between multiple source systems and fraud detection pipelines, supporting \textbf{process data validation} in business workflows.}
        \resumeItem{Automated data extraction and transformation pipelines integrating diverse data sources \textbf{including cloud platforms and databases}, improving **data quality and operational monitoring** for key financial fraud metrics.}
        \resumeItem{Leveraged complex SQL queries including \textbf{joins, window functions, and unions} to build scalable transformation logic supporting analytics and reporting.}
        \resumeItem{Collaborated with cross-functional teams applying \textbf{agile practices} to deliver data solutions, enhancing detection and monitoring with actionable insights on transactional data flows.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Contributed to \textbf{Azure Cognitive Services} testing and evaluation by building \textbf{data validation} scripts, improving data pipeline reliability with \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Kusto queries}.}
        \resumeItem{Streamlined ETL workflows and data quality checks using \textbf{Python (Pandas)} and \textbf{SQL}, facilitating enhanced data insights and operational diagnostics across cloud systems.}
        \resumeItem{Developed and optimized complex SQL queries and scripts to extract and transform data for analytics, implementing \textbf{process improvement} insights.}
        \resumeItem{Worked alongside product and engineering teams to prioritize and implement data-driven features enabling automated and actionable \textbf{process mining insights}.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly acquired skills in \textbf{C\#}, \textbf{Azure}, and XML-based data processing to develop and refactor key modules supporting complex enterprise workflows.}
        \resumeItem{Introduced coding improvements to enhance maintainability and data handling robustness, aligning with best practices in \textbf{process automation} and \textbf{data validation}.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led frontend and backend development for automotive software platforms, integrating client feedback to optimize user experience and operational workflows.}
        \resumeItem{Collaborated in process workflow analysis and automation, supporting integration and validation of haptic feedback features aligned with product requirements.}
        \resumeItem{Applied \textbf{CI/CD pipelines} using \textbf{Jenkins} and \textbf{Bitbucket} to accelerate deployment cycles and improve software quality in automotive infotainment systems.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented core data processing pipelines and analytical models using \textbf{Python}, \textbf{Java}, and \textbf{SQL} that improved data transformation efficiency by 40\%.}
        \resumeItem{Built Python tools to convert large datasets into optimized formats supporting faster process mining and analytics workflows.}
        \resumeItem{Applied \textbf{Lean Six Sigma} principles to improve data quality and development processes, driving enhanced system reliability and reduced cycle times.}
        \resumeItem{Mentored engineers and served as \textbf{Scrum Master}, fostering collaboration and delivery of complex data-driven projects aligned with business process improvements.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}