\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building scalable, cloud-native applications and backend services with strong focus on \textbf{automation}, \textbf{distributed systems}, and \textbf{end-to-end ownership}. Skilled in \textbf{Java/Spring Boot}, \textbf{Node.js/React}, and \textbf{Python}, with expertise designing APIs and microservice architectures deployed on \textbf{AWS} and \textbf{Azure}. Proven ability to ship features rapidly in collaboration with cross-functional teams, improving system robustness and customer experience in fast-paced environments.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, TypeScript, C++, C\#, SQL, Bash \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, Nest.js, RESTful APIs, Microservices, Serverless architecture \\
     \textbf{Frontend}: React, Next.js, JavaScript, HTML/CSS \\
     \textbf{Databases}: PostgreSQL, DynamoDB, MongoDB, Redis \\
     \textbf{Cloud Platforms}: AWS (Lambda, S3, ECS/EKS, CloudFormation), Azure (DevOps, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, GitHub Actions, Terraform, CI/CD Pipelines \\
     \textbf{Data Streaming \& Processing}: Apache Kafka, Event-driven Architecture, Asynchronous Processing \\
     \textbf{Testing and QA}: JUnit, Selenium, Cucumber, TDD/BDD, Automated and Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, System Design, Scalability Optimization, JIRA, Maven, Code Reviews
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and SQL validation scripts to verify data quality in fraud detection pipelines, improving system reliability and reducing incident response times.}
        \resumeItem{Automated regression and functional testing with Java, Cucumber, and Selenium, achieving 40\% reduction in manual testing and enhancing feature stability and release velocity.}
        \resumeItem{Built and maintained complex workflows coordinating large-scale transaction data to identify fraudulent activity and automate case creation and monitoring, driving faster fraud detection.}
        \resumeItem{Collaborated with cross-functional teams using Agile methods to design and optimize SQL queries and data pipelines, ensuring delivery of scalable, high-quality releases aligned to business needs.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Data Engineer}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led testing and validation of \textbf{Azure Cognitive Services} features via SDKs, REST APIs, and \textbf{Azure AI Studio}, identifying critical defects and improving service reliability and scalability.}
        \resumeItem{Optimized code testing and containerized workflows using Jupyter, Postman, Java, Python, and C\#, increasing product observability and reducing time to detect issues by 30\%.}
        \resumeItem{Trained and fine-tuned \textbf{OpenAI GPT} models on \textbf{Azure OpenAI} with benchmarking, improving runtime performance and reducing latency for real-time conversational workloads.}
        \resumeItem{Collaborated asynchronously with global teams to validate and integrate cloud AI services, contributing to scalable, production-ready enterprise applications.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Development Engineer Co-op}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly onboarded and contributed independently within 4 weeks on a complex \textbf{Azure} based codebase including \textbf{XSLT}, \textbf{XML}, C\#, and C++, enabling quick feature delivery and production bug fixes.}
        \resumeItem{Implemented code quality improvements and refactoring using mentorship and Pluralsight training, improving sprint velocity and maintainability in a collaborative environment.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led end-to-end development and integration of innovative haptic feedback features for Cadillac vehicles, ensuring alignment with UX and safety standards in a cross-disciplinary team.}
        \resumeItem{Developed interactive frontend components using React and modern UI architecture, integrating backend APIs to improve responsiveness and usability for automotive design platforms.}
        \resumeItem{Designed and validated haptic feedback on prototype hardware, applying iterative testing and adjustments to perfect in-car vibration behavior for real-world driving conditions.}
        \resumeItem{Contributed to automotive infotainment UI and workflow enhancements using Qt, Rhapsody, and C++, improving system responsiveness and reliability.}
        \resumeItem{Automated CI/CD pipelines via Jenkins and Bitbucket integration, increasing deployment frequency and reducing integration errors across development teams.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer II}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Implemented scalable analytical models and core backend components using Java, C\#, Python, and advanced data structures, achieving 40\% average performance improvement on production services.}
        \resumeItem{Developed Python tools to convert large model datasets into optimized binary formats, drastically reducing file sizes and processing times for damage computations.}
        \resumeItem{Systematically diagnosed and resolved critical memory leaks and performance bottlenecks, improving service uptime and efficiency of key business applications.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process improvements to reduce technical debt and enhance software delivery pipelines.}
        \resumeItem{Mentored engineers and led a team of three, serving as \textbf{Scrum Master} to coordinate Agile ceremonies and facilitate cross-team collaboration.}
        \resumeItem{Partnered with Product and Research to refine feature requirements, designing scalable backend APIs and workflows to reduce manual intervention and improve automation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}