\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building \textbf{end-to-end integrated web and mobile solutions} for financial services and enterprise organizations. Expert in \textbf{developing RESTful APIs, Web Services, and Payment Integrations} with strong skills in \textbf{Java/Spring Boot}, \textbf{Node.js/React}, and \textbf{Python}. Experienced in guiding technical teams and collaborating cross-functionally to deliver resilient, scalable, and secure \textbf{payment and ecommerce platform integrations} on \textbf{AWS} and \textbf{Azure}, accelerating time-to-revenue and enhancing client satisfaction for global partners.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, C++, C\#, JavaScript, SQL, Bash, PowerShell \\
     \textbf{Integration Technologies}: REST APIs, Web Services, GraphQL, JSON, XML, OAuth, JWT \\
     \textbf{Backend and Frameworks}: Spring Boot, Spring MVC, Node.js, Microservices Architecture \\
     \textbf{Frontend}: React, JavaScript, HTML/HTTP, CSS \\
     \textbf{Mobile Platforms}: iOS, Android, Objective-C basics \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, DynamoDB, Redis \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, Data Factory, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Payment Systems}: Ecommerce Payment Gateways, Credit Card Processing, Online/Offline Payments, Security Best Practices \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, API Testing, BDD, Automated and Load Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained secure and scalable backend services integrating payment and fraud detection pipelines, improving payment data quality and reducing transaction errors by 20\%.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using \textbf{Cucumber} and Selenium, supporting \textbf{API validation} and increasing release reliability.}
        \resumeItem{Collaborated with cross-functional teams in Agile environments to design and deliver resilient backend components supporting secure payment authorization and workflows aligned with regulatory standards.}
        \resumeItem{Supported integration of third-party services and internal APIs, troubleshooting and resolving \textbf{payment processing} issues to ensure seamless transaction flows for clients.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements for \textbf{Azure Cognitive Services} by testing and validating new AI integration features using \textbf{REST APIs}, SDKs, and automated test suites, enhancing service reliability.}
        \resumeItem{Streamlined workflows combining code testing, API analysis, and container deployment leveraging \textbf{Java}, \textbf{Python}, \textbf{C\#}, and API testing tools, improving observability of real-time data pipelines.}
        \resumeItem{Led integration of AI service APIs for enterprise customers, performing root cause analysis and issue resolution to support \textbf{seamless onboarding} and accelerate time-to-value.}
        \resumeItem{Partnered with engineering and product teams to validate new payment and identity platform capabilities, contributing to scalable, production-ready APIs for client solutions.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Ramped up quickly on \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure} to independently own user stories and fixes for integration components supporting platform workflows.}
        \resumeItem{Applied best practices in code quality and refactoring to improve maintainability and reduce defects, contributing to team velocity and seamless feature rollouts.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led design and implementation of interactive frontend features using \textbf{React}, integrating web services and APIs aligned with automotive user experience and safety requirements.}
        \resumeItem{Implemented integration workflows using \textbf{Qt}, \textbf{C++}, and communication protocols to ensure reliable functionality of automotive infotainment and control systems.}
        \resumeItem{Developed and tested embedded software and delivered stable CI/CD pipelines automating builds and tests, reducing integration friction and deployment time.}
        \resumeItem{Collaborated actively with clients and cross-disciplinary teams to align technical solutions with business needs and ensure smooth project delivery.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Implemented scalable, high-performance backend systems using \textbf{Java}, \textbf{C\#}, \textbf{Python}, and \textbf{C++}, processing large datasets for analytic and transactional workflows.}
        \resumeItem{Built data conversion applications improving system interoperability and reducing processing time by 90\%, supporting efficient transaction data handling in payment environments.}
        \resumeItem{Led root cause analysis and troubleshooting of complex integration issues, improving system stability and user satisfaction.}
        \resumeItem{Certified in \textbf{Lean Six Sigma}, applying process improvements to optimize engineering workflows and increase delivery efficiency.}
        \resumeItem{Mentored junior engineers and acted as \textbf{Scrum Master} to facilitate agile ceremonies and ensure alignment with business goals and technical requirements.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}