\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    Results-driven \textbf{AI Engineer} and Full-Stack Software Engineer with 5+ years of experience designing, developing, and deploying scalable AI/ML and cloud-native solutions. Proficient in \textbf{Python}, \textbf{Bayesian modeling}, and \textbf{SQL} with deep hands-on expertise in cloud platforms including \textbf{Google Cloud Platform (GCP)}, \textbf{Vertex AI}, and \textbf{Azure}. Skilled at integrating advanced AI/ML models such as transformer-based and generative AI to derive data-driven insights for business impact at organizations like \textbf{TD Bank}, \textbf{Microsoft}, and others. Strong background in designing CI/CD pipelines for ML, developing ETL workflows, and utilizing tools like \textbf{BigQuery}, \textbf{Cloud Storage}, \textbf{Google Analytics}, and \textbf{Google Tag Manager} to support enterprise-scale analytics and marketing tech stacks.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, SQL, C++, C\#, Bash, PowerShell \\
     \textbf{AI/ML \& Data Science}: Bayesian Modeling, Probabilistic Inference, Transformer-based Models, Generative AI, Data Analytics, Predictive Modeling, Causal Inference \\
     \textbf{Cloud \& ML Platforms}: GCP (Vertex AI, BigQuery, Cloud Storage, Cloud Build, CI/CD Pipelines), AWS, Azure, Azure Cognitive Services \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices \\
     \textbf{Marketing Analytics}: Google Tag Manager (GTM), Google Analytics 4 (GA4), GA360 \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, GitHub Actions, Terraform, Jupyter Notebooks \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Development Practices}: Agile/Scrum, TDD/BDD, System Design, Code Reviews, Scalability Optimization
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and \textbf{SQL} validation scripts in \textbf{Azure Data Notebooks} to verify incoming data from fraud detection pipelines, improving data quality and reliability.}
        \resumeItem{Automated and optimized regression and functional testing by building Java-based test suites with Cucumber, Selenium, and BDD, enhancing workflow reliability by 40\%.}
        \resumeItem{Designed and deployed scalable AI/ML workflows leveraging large-scale transactional datasets for fraud monitoring, integrating with ETL pipelines to support real-time suspicious transaction detection.}
        \resumeItem{Collaborated in agile teams to deliver data-driven solutions, optimizing complex SQL queries and ensuring alignment with business objectives through continuous integration and deployment.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements in \textbf{Azure Cognitive Services}, testing new AI features using SDKs, REST APIs, and \textbf{Azure AI Studio}, enhancing service stability and performance.}
        \resumeItem{Streamlined testing, database analysis, and container workflows leveraging \textbf{Python}, \textbf{Jupyter}, \textbf{C\#}, and \textbf{Kusto} queries, improving observability by 30\%.}
        \resumeItem{Led training, tuning, and evaluation of \textbf{OpenAI GPT} models on Azure OpenAI with generative AI techniques, increasing model accuracy and reducing latency for real-time applications.}
        \resumeItem{Worked cross-functionally to validate and deploy scalable AI-powered cognitive and LLM services, advancing Azure’s AI capabilities for enterprise use.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Acquired expertise in \textbf{Azure} and programming languages \textbf{C++}, \textbf{C\#}, and \textbf{XSLT}, independently owning sprint stories and addressing production bugs.}
        \resumeItem{Applied best practices and automated testing improvements, accelerating development velocity by 10-15\% while contributing to cloud-based software products.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of haptic feedback features from concept through client delivery, ensuring compliance with safety and UX standards.}
        \resumeItem{Built frontend React applications and integrated backend APIs, improving responsiveness and user experience for automotive design platforms.}
        \resumeItem{Tested and validated haptic functionality on hardware prototypes, analyzing data to ensure accuracy of vibration patterns in real scenarios.}
        \resumeItem{Designed and maintained CI/CD pipelines using \textbf{Jenkins}, \textbf{Bitbucket}, and \textbf{SourceTree} to automate builds and testing, ensuring smooth deployment and integration.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Built and optimized analytical models using \textbf{Java}, \textbf{Python}, \textbf{C++}, and \textbf{SQL}, improving processing performance by 40\% across critical systems.}
        \resumeItem{Developed Python tools to convert large model datasets into binary formats, reducing load times and improving efficiency for downstream AI workflows.}
        \resumeItem{Led root-cause analysis and fixed memory leaks and performance issues, enhancing system stability for probabilistic and predictive modeling platforms.}
        \resumeItem{Applied Lean Six Sigma principles to streamline development processes and mentored engineers, fostering a culture of continuous improvement and collaboration.}
        \resumeItem{Collaborated with Product Management and Research teams to refine AI-driven features, acted as Scrum Master, and led a team of three engineers in agile releases.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}