\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Systems Engineer} and \textbf{Full-Stack Software Engineer} with 5+ years of experience designing, building, and deploying large-scale distributed systems and cloud-native applications. Demonstrated skills in \textbf{Python}, \textbf{C++}, and \textbf{Java} with expertise in container orchestration using \textbf{Kubernetes} and automation for AI/ML workloads and cloud infrastructure. Strong background in scheduling, resource management, and performance optimization for GPU-accelerated platforms. Proven ability to collaborate with cross-functional teams to deliver high-performance and scalable solutions, with exposure to NVIDIA GPU technologies and AI frameworks.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, C++, Java, Go, C\#, SQL, Bash \\
     \textbf{Systems}: Kubernetes, Docker, Containerd, CRI-O, Linux namespaces, CRIU \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3), Azure (AKS, DevOps), GCP \\
     \textbf{AI/ML Frameworks}: TensorRT, ML Compilers, Azure Cognitive Services, OpenAI GPT, CUDA \\
     \textbf{Backend and Frameworks}: Spring Boot, RESTful APIs, Microservices Architecture \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
     \textbf{DevOps and Tools}: Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Testing}: JUnit, Cucumber, Selenium, Postman, TDD/BDD \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and \textbf{SQL} validation scripts in Azure Data Notebooks ensuring high data quality for fraud detection pipelines, improving system reliability and trustworthiness of inference data.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using \textbf{Cucumber}, \textbf{Selenium}, and \textbf{BDD} practices, enhancing feature stability and reducing manual effort by 40\%.}
        \resumeItem{Designed and optimized backend workflows leveraging large-scale transactional datasets and fraud monitoring tools, emphasizing low-latency and real-time alerting for suspicious activity detection.}
        \resumeItem{Collaborated with cross-functional teams following \textbf{Agile/Scrum} methodologies to improve scheduling and pipeline efficiency, integrating containerized microservices conducive for scalable deployment.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Contributed to \textbf{Azure Cognitive Services} by developing and testing features involving \textbf{ML compilers}, \textbf{performance prediction}, and inference workloads, improving service scalability and efficiency.}
        \resumeItem{Streamlined container-based workflows with \textbf{Jupyter}, \textbf{Postman}, and codebases in \textbf{Python}, \textbf{C\#}, and \textbf{Java} optimizing reliability and observability for cloud hosted GPU workloads.}
        \resumeItem{Pioneered training and fine-tuning of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, deploying scalable ML inference services with improved latency and throughput performance.}
        \resumeItem{Collaborated with adjacent teams integrating scheduler and inference engines, contributing to cohesive AI platform solutions for large-scale AI model deployment.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly developed proficiency in \textbf{C++}, \textbf{C\#}, \textbf{Azure}, and \textbf{XML} technologies while owning sprint deliverables and resolving production issues within a complex software environment.}
        \resumeItem{Introduced best practices for code quality and system design leveraging \textbf{Pluralsight} training and mentorship programs, contributing to increased team velocity and robustness in feature delivery.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led full lifecycle development of automotive haptic feedback features, involving design, implementation, and testing of embedded systems with real-time requirements.}
        \resumeItem{Built interactive frontend using \textbf{React} integrated with backend APIs, supporting automotive UX initiatives aligned with safety and performance guidelines.}
        \resumeItem{Tested and validated embedded \textbf{haptics} functionality on prototype hardware, ensuring reliable performance under real driving scenarios.}
        \resumeItem{Contributed to infotainment UI workflows using \textbf{C++}, \textbf{Qt}, and automotive communication protocols, focusing on responsiveness and robustness.}
        \resumeItem{Implemented CI/CD automation pipelines using \textbf{Jenkins}, \textbf{Bitbucket}, and \textbf{SourceTree} improving build and release efficiency in multi-team environments.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented high-performance analytical models and core components in \textbf{Java}, \textbf{C++}, \textbf{Python}, and \textbf{C\#}, achieving 40\% faster processing for critical business workflows.}
        \resumeItem{Developed \textbf{Python} tools to convert model data into optimized binary formats reducing memory footprint and speeding up inference computations.}
        \resumeItem{Diagnosed and fixed complex memory leaks and performance bottlenecks using systematic profiling and debugging methods on distributed systems.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process improvement techniques to enhance software development workflows and reduce waste.}
        \resumeItem{Mentored new engineers and led multiple Agile teams as \textbf{Scrum Master}, driving delivery of scalable, maintainable software solutions in fast-paced environments.}
        \resumeItem{Collaborated closely with Product Management and Research to refine feature requirements focused on scalable and efficient AI/ML system integration.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}