\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience delivering \textbf{clean, modern, testable, and well-documented code} for cloud-native web applications and backend services. Proficient in \textbf{Node.js, Express, JavaScript, MongoDB}, and \textbf{AWS Lambda} serverless architectures. Skilled in designing RESTful APIs and distributed systems with strong problem-solving and cross-team collaboration experience. Proven track record working with enterprise clients and complex domains including financial services and transportation. Adept at working remotely as part of senior engineering teams, delivering scalable, high-quality digital products that interact with millions of users and data points.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: JavaScript, Java, Python, C++, C\#, SQL, Bash \\
     \textbf{Backend and Frameworks}: Node.js, Express, Spring Boot, RESTful APIs, Microservices Architecture, Serverless (AWS Lambda, Azure Functions) \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS \\
     \textbf{Databases}: MongoDB, PostgreSQL, MySQL, Oracle, MSSQL, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (Functions, DevOps, Data Factory), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Testing and QA}: Jest, JUnit, Cucumber, Selenium, TDD/BDD, Automated and Performance Testing \\
     \textbf{Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, significantly improving \textbf{data quality} and overall system reliability.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber, Selenium, and BDD practices, reducing manual testing effort by 40\% and increasing feature reliability.}
        \resumeItem{Designed and enhanced backend microservices using \textbf{Node.js} and \textbf{Express} for fraud monitoring workflows, ensuring scalability and high availability of transactional data processing.}
        \resumeItem{Collaborated effectively with cross-functional agile teams, delivering high-impact features and maintaining code quality standards aligned with enterprise best practices.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements for \textbf{Azure Cognitive Services} by rigorously testing new features using SDKs, REST APIs, and Azure AI Studio, identifying and resolving critical defects.}
        \resumeItem{Streamlined code testing, database analysis, and container-based workflows using Jupyter, Postman, Visual Studio, Java, Python, C\#, and Kusto queries, increasing system observability and reliability.}
        \resumeItem{Led training, evaluation, and optimization of \textbf{OpenAI GPT} models leveraging \textbf{Azure OpenAI} services, reducing latency and improving performance for real-time AI workloads.}
        \resumeItem{Collaborated with engineering and product teams to validate and deploy \textbf{scalable cloud-native AI solutions} for enterprise applications.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly ramped up on XSLT, XML, C\#, C++, and Azure cloud services, independently owning sprint user stories and production bug fixes.}
        \resumeItem{Introduced improvements in code quality and refactoring, leveraging learning resources and mentorship to boost team development velocity by 10 to 15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of automotive haptic feedback features from requirements analysis to integration, ensuring compliance with safety and UX standards.}
        \resumeItem{Developed and maintained frontend components with React, utilizing modern practices and secure design to improve user experience in automotive design platforms.}
        \resumeItem{Contributed to infotainment UI workflows using Qt, Rhapsody, WeCAN, and C++, enhancing responsiveness and reliability in complex automotive systems.}
        \resumeItem{Implemented CI/CD pipelines automating build, test, and deployment processes with Jenkins, SourceTree, and Bitbucket, improving software delivery efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed analytical models and core components using Java, C\#, Python, C++, SQL, delivering 40\% performance improvements across business-critical workflows.}
        \resumeItem{Built Python-based tools to convert large datasets into optimized binary formats, reducing load times and improving data processing efficiency.}
        \resumeItem{Diagnosed and resolved critical production issues including memory leaks and performance bottlenecks via profiling and detailed root cause analysis.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process improvement techniques to enhance software development workflows.}
        \resumeItem{Mentored engineers, facilitated Agile ceremonies as Scrum Master, and collaborated with Product and Research teams to deliver scalable solutions for complex domains including insurance and transportation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}