\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building end-to-end, cloud-native applications and backend services, with additional expertise in \textbf{QA Test Automation} and \textbf{hardware/software validation} for real-world applications. Skilled in \textbf{Python}, \textbf{Java}, \textbf{Linux}, and scripting with strong understanding of \textbf{Containerization}, \textbf{CI/CD}, and \textbf{Version Control} tools like \textbf{GIT}. Proven ability to collaborate effectively with R&D teams, write reusable test automation code, manage QA test suites, and ensure releases meet high-quality customer standards.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, Bash, SQL, PowerShell, VBA, C++ \\
     \textbf{Testing and QA}: Automated Testing, Test Automation Frameworks, JUnit, Cucumber, Selenium, Scripting for QA, Performance Testing \\
     \textbf{Tools and Platforms}: Linux, Docker, Kubernetes, GIT, GitLab, Jenkins, CI/CD Pipelines, Azure DevOps, Containerization \\
     \textbf{Networking Concepts}: TCP/IP, UDP, Broadcast Protocols, Troubleshooting \\
     \textbf{Cloud Platforms}: AWS, Azure, GCP \\
     \textbf{Development Practices}: Agile/Scrum, Peer Reviews, Documentation, JIRA, Test Suite Management
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained automated test scripts using \textbf{Python} and \textbf{Java} integrated with \textbf{Cucumber} and \textbf{Selenium} to validate software modules, improving regression test coverage and reducing manual test time by 40\%.}
        \resumeItem{Authored and maintained detailed test documentation to support validation of banking software releases, ensuring compliance with customer standards and regulatory requirements.}
        \resumeItem{Collaborated effectively with development teams to test bug fixes and verify feature enhancements, contributing to high software quality and on-time project deliveries.}
        \resumeItem{Worked within an Agile environment preparing and monitoring Quality Assurance (QA) test suites, ensuring adherence to \textbf{CI/CD} processes and frequent release cycles.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Executed rigorous QA testing of AI-based features in \textbf{Azure Cognitive Services}, using \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Azure AI Studio} to validate functionality and performance.}
        \resumeItem{Developed and automated test workflows combining \textbf{Python}, \textbf{Postman}, and containerized environments (Docker) to enhance testing accuracy and repeatability.}
        \resumeItem{Collaborated with cross-functional teams, including Test Automation Engineers, to build reusable test automation code and improve overall QA efficiency.}
        \resumeItem{Contributed to continuous integration deployments and version control activities using \textbf{GitLab} and \textbf{CI/CD} pipelines, ensuring smooth QA test releases and quality control.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained hands-on experience with \textbf{C\#}, \textbf{C++}, \textbf{Azure}, and \textbf{XML/XSLT} on a complex codebase, developing strong debugging and troubleshooting skills pertinent to software validation and integration.}
        \resumeItem{Engaged in peer reviews and collaborated with the team to improve code quality and assist in bug identification and resolution within sprint cycles.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led end-to-end development and validation of haptic feedback features on prototype hardware, performing detailed functionality testing to ensure alignment with \textbf{automotive safety} and design standards.}
        \resumeItem{Worked closely with cross-disciplinary teams including R\&D engineers and designers to resolve product functionality challenges and optimize user experience.}
        \resumeItem{Designed and executed manual and automated tests on infotainment hardware and software components using \textbf{Qt}, \textbf{Rhapsody}, and \textbf{C++} in embedded environments.}
        \resumeItem{Implemented and managed \textbf{CI/CD pipelines} using \textbf{Jenkins}, \textbf{SourceTree}, and \textbf{Bitbucket} to automate software builds, test execution, and deployment, improving development cycle times and consistency.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed core analytical software modules using \textbf{Java}, \textbf{Python}, \textbf{C++}, and \textbf{SQL}, incorporating automated unit and integration tests to enhance reliability and performance.}
        \resumeItem{Created Python scripts and tools to automate data processing and format conversion, improving accuracy and reducing manual steps in QA data validation processes.}
        \resumeItem{Performed root cause analysis and troubleshooting on production issues, applying systematic debugging and diagnostic strategies to resolve defects quickly.}
        \resumeItem{Led peer reviews and contributed to comprehensive quality control of development and testing outputs, fostering a culture of continuous improvement.}
        \resumeItem{Applied \textbf{Lean Six Sigma} methodologies to refine testing workflows and reduce defects early in the development lifecycle.}
        \resumeItem{Mentored junior engineers and acted as \textbf{Scrum Master}, coordinating QA and development teams to ensure consistent quality delivery in Agile environments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}