\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{AI and LLM Engineer} with 5+ years of experience in developing, fine-tuning, and deploying \textbf{large-scale language models (LLMs)} and NLP-driven automation solutions. Proficient in \textbf{Python}, \textbf{PyTorch}, \textbf{TensorFlow}, and \textbf{Hugging Face} ecosystems, with expertise in building production-grade AI pipelines and integrating autonomous agentic AI workflows. Adept at leveraging prompt engineering, vector databases, and knowledge graphs to optimize model inference and enhance AI-driven systems. Demonstrated success delivering scalable AI solutions at \textbf{LTI Mindtree}, \textbf{Wipro}, and other leading tech organizations.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, C++, C\#, SQL, Bash \\
     \textbf{LLM Frameworks}: PyTorch, TensorFlow, Hugging Face Transformers, LangChain, LangGraph \\
     \textbf{AI and NLP Tools}: OpenAI GPT Models, Azure Cognitive Services, Prompt Engineering, Fine-tuning LLMs, DeepEval Frameworks \\
     \textbf{Databases}: PostgreSQL, MongoDB, Redis, Vector Databases (conceptual knowledge) \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, DynamoDB), Azure (Functions, OpenAI Studio), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, CI/CD Pipelines \\
     \textbf{Development Practices}: Agile/Scrum, Test-Driven Development, Code Reviews, System Design, Performance Optimization
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and validated \textbf{Python} scripts in Azure Data Notebooks to ensure data integrity from autonomous AI and fraud-detection pipelines, improving overall system robustness and auditability.}
        \resumeItem{Automated \textbf{testing frameworks} including regression and functional tests using \textbf{Java}, \textbf{Cucumber}, and BDD methodologies, enhancing reliability of automated workflows and integrations.}
        \resumeItem{Architected fraud detection workflows processing large-scale transactional data, enabling near real-time analysis using AI-powered tools complying with enterprise-grade security and compliance standards.}
        \resumeItem{Collaborated on pipeline optimization, improving SQL query efficiency and supporting Agile release cycles to deploy scalable AI solutions aligned with business objectives.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led training, fine-tuning, and evaluation of \textbf{OpenAI GPT models} on \textbf{Azure OpenAI}, leveraging \textbf{Python}, \textbf{PyTorch}, and \textbf{DeepEval} techniques to improve model accuracy and inference efficiency by 25\%.}
        \resumeItem{Implemented \textbf{prompt engineering} strategies and \textbf{prompt tuning} to optimize AI-driven automation workflows and improve response relevance and speed in production environments.}
        \resumeItem{Enhanced product quality by systematically testing and benchmarking \textbf{Azure Cognitive Services} using SDKs, REST APIs, and \textbf{AI Studio}, reducing defects and increasing AI service stability.}
        \resumeItem{Collaborated with product and engineering teams to build \textbf{agentic AI} workflows and integrate \textbf{knowledge graphs} and \textbf{vector databases}, advancing scalable autonomous AI solutions for enterprise deployments.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly adapted to complex \textbf{Azure} cloud services and XML-based technologies, independently owning sprint deliverables and performing critical bug fixes to enhance software stability.}
        \resumeItem{Implemented backend improvements and code quality enhancements, increasing maintainability and development speed by integrating modern software engineering best practices.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and developed haptic feedback features and corresponding frontend applications using React and C++ for automotive platforms, integrating system-level event response logic.}
        \resumeItem{Collaborated closely with cross-functional teams to validate hardware-software integration, improving system responsiveness and safety through iterative testing and refinements.}
        \resumeItem{Authored and maintained CI/CD pipelines enhancing deployment automation and reducing integration failures, supporting continuous software delivery best practices.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed performance-critical analytical models using \textbf{Python}, \textbf{Java}, and \textbf{C++} focusing on scalable data structures and algorithms, delivering up to 40\% runtime improvements.}
        \resumeItem{Built \textbf{Python}-based tools for model data conversion optimizing storage and processing efficiency, critical for high-volume damage computation applications.}
        \resumeItem{Applied Lean Six Sigma methodologies to improve development workflows, contributing to waste reduction and quality enhancement in engineering processes.}
        \resumeItem{Mentored engineers and led Agile teams as \textbf{Scrum Master}, fostering collaboration to deliver high-quality software solutions on schedule.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}