\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      Results-driven \textbf{Full-Stack Software Engineer} with 5+ years experience designing, developing, and supporting cloud-native applications and automated solutions, specializing in \textbf{Azure Cloud}, \textbf{PowerShell}, \textbf{Python}, and \textbf{SQL} scripting for scalable, resilient, and secure systems. Strong background in \textbf{DevOps} practices including CI/CD, infrastructure automation, and cloud deployment (IaaS, PaaS), with demonstrated ability to architect and maintain complex \textbf{infrastructure components}, perform systems administration, and deliver enhancements aligned with enterprise standards. Proven track record delivering high-impact initiatives and collaborating effectively within Agile teams at \textbf{TD Bank}, \textbf{Microsoft}, and other organizations.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: PowerShell, Python, Bash, Java, C\#, SQL, Shell Scripting \\
     \textbf{Cloud Platforms}: Azure (Virtual Machines, AKS, Blob Storage, ASE, Event Hub), AWS, GCP \\
     \textbf{DevOps and Configuration Management}: CI/CD (Jenkins, Azure DevOps), Terraform, Ansible, SALT, Docker, Kubernetes \\
     \textbf{Databases}: MSSQL, PostgreSQL, MySQL, MongoDB, SSIS, SSRS \\
     \textbf{Monitoring and Logging}: Splunk, DataDog, ELK Stack, ITRS, Sensu, Foglight \\
     \textbf{Tools and Methodologies}: ServiceNow (Change Management), JIRA, Git, Bitbucket, Agile/Scrum \\
     \textbf{Other}: Infrastructure as Code (IaC), Automated Build and Deploy Pipelines, High-Performance Computing (HPC) Basics \\
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Develop, maintain, and automate \textbf{PowerShell} and Python scripts for data validation and system monitoring within \textbf{Azure} cloud environments, improving operational efficiency and system reliability.}
        \resumeItem{Implement and support cloud infrastructure components including Azure Virtual Machines, Blob Storage, and AKS, ensuring scalability, security, and compliance with enterprise architecture principles.}
        \resumeItem{Perform systems administration tasks: configure, tune, backup, deploy applications, monitor services, and manage authentication across hybrid cloud environments, aligned with TD security and change management standards.}
        \resumeItem{Collaborate with cross-functional teams to design automated build and deployment pipelines using Jenkins and Azure DevOps, facilitating Continuous Integration and Continuous Deployment (CI/CD).}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Azure Cognitive Services} capabilities by developing and testing SDKs and REST APIs, contributing to improved service stability and performance.}
        \resumeItem{Streamlined infrastructure automation and deployments using \textbf{Python}, \textbf{PowerShell}, and containerization technologies in cloud environments, increasing system observability and reliability.}
        \resumeItem{Collaborated on implementing monitoring and logging solutions with tools such as \textbf{DataDog} and \textbf{Splunk} for cloud service health tracking.}
        \resumeItem{Applied Agile practices to support automation and cloud-native development processes, improving delivery cycles and infrastructure management.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained experience configuring and supporting \textbf{Azure} cloud services and infrastructure, including virtual machines and application services, aligning with organizational security policies.}
        \resumeItem{Contributed to scripting and automation efforts using PowerShell and Python, enhancing deployment and operational workflows within cloud environments.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led feature development and integration using React and backend APIs, emphasizing scalable and maintainable solutions with a focus on reliability.}
        \resumeItem{Implemented CI/CD pipelines using Jenkins and Bitbucket that automated build, test, and deployment phases, reducing deployment errors and accelerating integration processes.}
        \resumeItem{Improved system stability and responsiveness in automotive infotainment software through targeted refactoring and performance tuning.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented scalable software components using Java, C\#, Python, and SQL, improving data processing performance by 40\% on critical analytical models.}
        \resumeItem{Automated data transformation and processing pipelines with Python, handling large datasets efficiently and enabling faster analytical computations.}
        \resumeItem{Applied engineering best practices to troubleshoot, profile, and optimize software for performance, stability, and scalability.}
        \resumeItem{Led Agile teams as Scrum Master, coordinating development efforts, managing sprint planning, and delivering continuous improvements to engineering workflows.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}