\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Data Scientist and Software Engineer} with 5+ years of experience in data analysis, algorithm development, and end-to-end data pipeline ownership. Skilled in \textbf{Python, SQL, machine learning}, and \textbf{data visualization} to drive data-centric decision-making. Proven ability to design and implement analytical frameworks, perform rigorous statistical analysis, and collaborate cross-functionally to improve product quality and user experience. Experience in building data-driven solutions and validating models in production at organizations including \textbf{TD Bank}, \textbf{Microsoft}, and industry-leading technology firms.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, SQL, Java, C++, C\#, Bash, PowerShell \\
     \textbf{Data Science \& ML}: Pandas, NumPy, Scikit-learn, PyTorch, TensorFlow, Keras, Statistical Analysis, Online Experimentation, A/B Testing \\
     \textbf{Data Engineering}: ETL Pipelines, Data Aggregation, Data Validation, Azure Data Notebooks, Jupyter, Kusto Queries \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3), Azure (DevOps, Data Factory, AKS, AI Studio), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, Azure DevOps, CI/CD Pipelines \\
     \textbf{Data Visualization}: Matplotlib, Seaborn, Power BI, Tableau \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, JIRA
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and \textbf{SQL} validation scripts in Azure Data Notebooks to improve \textbf{data quality} and consistency for fraud detection pipelines, supporting reliable business insights and operational decision-making.}
        \resumeItem{Collaborated with cross-functional teams to build workflows using large transactional datasets that monitored suspicious activities and supported real-time fraud detection, improving monitoring efficiency.}
        \resumeItem{Designed and analyzed technical experiments improving feature quality and ensuring reliable integration, aligning with team objectives and enhancing product reliability.}
        \resumeItem{Delivered high-quality solutions by creating and optimizing complex SQL queries, and leveraging Agile methodologies to meet project timelines and deliverables.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led quality improvements of \textbf{Azure Cognitive Services} by testing and validating \textbf{ML models} integrating \textbf{Python}, \textbf{REST APIs}, and \textbf{Azure AI Studio}, driving 30\% increased stability and performance.}
        \resumeItem{Streamlined data ingestion and processing pipelines through \textbf{ETL workflows} using \textbf{Jupyter}, \textbf{Kusto} queries, and container-based environments, enhancing robustness and operational observability.}
        \resumeItem{Developed benchmarks and systematically tuned \textbf{OpenAI GPT} model deployments on \textbf{Azure OpenAI}, enabling improved latency and model accuracy for real-time applications.}
        \resumeItem{Collaborated cross-functionally with engineering and product teams to ensure \textbf{ML feature validation}, data quality, and service scalability in large-scale AI offerings.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Acquired proficiency in \textbf{Azure} cloud services, \textbf{C\#}, \textbf{C++}, and data transformation via \textbf{XSLT}/\textbf{XML} enabling independent contribution to sprint deliverables and bug fixes.}
        \resumeItem{Supported the team by applying best coding practices and refactoring legacy code, increasing maintainability and efficiency in ongoing development efforts.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led end-to-end development of haptic feedback features for Cadillac vehicles, including requirement analysis and validation to ensure alignment with safety and customer experience goals.}
        \resumeItem{Developed frontend React components integrated with backend APIs to visualize automotive configurations, collaborating with design and engineering teams on UX improvements.}
        \resumeItem{Tested and validated haptic patterns on prototype hardware, integrating data-driven insights about real-world feature behaviors impacting user safety and experience.}
        \resumeItem{Contributed to automotive infotainment UI and interaction workflows using \textbf{Qt}, \textbf{C++}, and related tools, enhancing system responsiveness and stability.}
        \resumeItem{Implemented \textbf{CI/CD pipelines} automating software builds and tests, improving deployment reliability and reducing integration risks.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Built and optimized next-generation \textbf{analytical models} using \textbf{Java}, \textbf{Python}, \textbf{C++}, and \textbf{SQL}, delivering 40\% performance improvements impacting critical business functions.}
        \resumeItem{Developed \textbf{Python}-based tools for data conversion and aggregation, reducing model data footprint by 90\% and enabling faster travel-time estimations and computations.}
        \resumeItem{Diagnosed and fixed complex performance issues using data profiling and debugging, improving system reliability and scaling model validation efforts.}
        \resumeItem{Applied \textbf{Lean Six Sigma} principles to automate and improve engineering workflows, increasing operational efficiency and reducing waste.}
        \resumeItem{Mentored junior engineers, supported onboarding, and led agile ceremonies as \textbf{Scrum Master}, fostering collaboration and high-quality deliveries.}
        \resumeItem{Partnered with Product and Research teams to translate business requirements into data-driven solutions, shaping strategy through analytical insights and presentations.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}