\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Senior Full-Stack Software Engineer} with 5+ years of experience delivering \textbf{scalable, high-quality} software solutions across both frontend and backend systems. Expertise in \textbf{Java/Spring Boot}, \textbf{Node.js/React}, and \textbf{Python} including building and maintaining \textbf{RESTful APIs} and \textbf{microservices}. Experienced in owning full software lifecycle from design to production with strong focus on \textbf{technical excellence}, \textbf{code quality}, and \textbf{engineering best practices}. Proven ability to troubleshoot complex full-stack systems, optimize performance, and collaborate cross-functionally at \textbf{TD Bank}, \textbf{Microsoft}, and enterprise organizations.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, C++, C\#, TypeScript, JavaScript, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Spring MVC, Node.js, RESTful APIs, GraphQL, Microservices Architecture \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS, Responsive Design, Frontend Performance Optimization \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB, Data Modelling \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, Data Factory, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines, Infrastructure as Code (IaC) \\
     \textbf{Data Streaming}: Apache Kafka, Real-time Data Processing, Event-driven Architecture \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, TDD/BDD, Automated Testing, Performance and Penetration Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{scalable RESTful APIs} and backend data validation scripts using \textbf{Python} and SQL in \textbf{Azure} environment ensuring high data integrity and accessibility for fraud monitoring systems.}
        \resumeItem{Automated regression and functional testing using \textbf{Java}, \textbf{Cucumber}, and \textbf{BDD}, improving \textbf{code quality} and reducing manual testing time by 40\%.}
        \resumeItem{Collaborated cross-functionally to design and optimize complex database queries, enhancing performance and maintainability consistent with scalable product standards.}
        \resumeItem{Contributed to \textbf{full lifecycle ownership} by managing bug fixes, regression testing, and improving system robustness in financial transaction monitoring workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led quality improvements on \textbf{Azure Cognitive Services} by extensively working with \textbf{REST APIs} and SDKs, debugging complex issues, and ensuring \textbf{high performance} and reliability in cognitive services deployments.}
        \resumeItem{Optimized scalable data processing workflows using \textbf{Python}, \textbf{C\#}, and \textbf{containerized environments}, applying engineering best practices for maintainability and performance.}
        \resumeItem{Drove the training and deployment of \textbf{OpenAI GPT} models using \textbf{Azure OpenAI}, improving latency and scalability through systematic performance tuning and automation.}
        \resumeItem{Worked closely with engineering and product teams to translate complex product requirements into high-quality technical solutions with \textbf{strong ownership} of deliverables.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Accelerated onboarding by mastering \textbf{C\#}, \textbf{XSLT}, \textbf{XML}, and \textbf{Azure} for backend systems, independently resolving sprint user stories and production bugs with high quality.}
        \resumeItem{Introduced refactoring and code quality improvements to enhance system maintainability and developer efficiency within the team, following \textbf{best practices} in codecraftsmanship.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented frontend application for automotive design platform using \textbf{React} and modern architectures, improving code reusability and scalability with component libraries and responsive design techniques.}
        \resumeItem{Collaborated on backend API integration supporting interactive HMI systems, emphasizing \textbf{clean, maintainable code} aligned with scalable product expectations.}
        \resumeItem{Engineered CI/CD pipelines using \textbf{Jenkins}, enhancing development velocity and ensuring smooth, automated testing and deployment cycles for automotive software components.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed high-performance, scalable analytical components using \textbf{Java}, \textbf{Python}, \textbf{C\#} with a focus on maintainability and technical excellence, improving model performance by up to 40\%.}
        \resumeItem{Built robust data conversion tools and maintained reliable backend services, reducing data processing time through optimized binary formats and effective debugging.}
        \resumeItem{Led a team of engineers and acted as \textbf{Scrum Master}, delivering scalable software solutions and enforcing engineering best practices, including thorough code reviews and technical documentation.}
        \resumeItem{Mentored engineers and collaborated closely with product management to ensure clear communication of technical designs, assumptions, and challenges throughout the project lifecycle.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}