\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building end-to-end, cloud-native web applications and backend services with expertise in \textbf{Node.js}, \textbf{React.js}, and \textbf{Microservices Architecture}, focused on scalable, secure \textbf{financial services} solutions. Skilled in designing and implementing RESTful APIs, integrating \textbf{NoSQL databases} like \textbf{MongoDB} and \textbf{Redis}, and deploying applications with container orchestration tools such as \textbf{Kubernetes}. Adept at applying security best practices including \textbf{oAuth2}, SSO, and CI/CD pipelines in Agile environments. Proven track record delivering high-impact projects at \textbf{TD Bank}, \textbf{Microsoft}, and other global organizations, with strong emphasis on mentoring and code quality.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: JavaScript (ES6+), TypeScript, Java, Python, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Node.js, Express.js, Spring Boot, RESTful APIs, Microservices Architecture \\
     \textbf{Frontend}: React.js, JavaScript, HTML/CSS, Jest, Protractor \\
     \textbf{Databases}: MongoDB, Redis, PostgreSQL, MySQL, Oracle, MSSQL, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, Data Factory, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Cloud Foundry, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Security}: oAuth2, SSO, Security scanning and best practices implementation \\
     \textbf{Data Streaming}: Apache Kafka, Real-time Data Processing, Event-driven Architecture \\
     \textbf{Testing and QA}: Jest, Protractor, JUnit, Cucumber, Postman, TDD/BDD, Automated Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, significantly improving data quality and overall system reliability.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber, Selenium, and BDD practices, reducing manual testing effort by 40\% and increasing feature reliability.}
        \resumeItem{Built and maintained fraud monitoring workflows leveraging large-scale transactional datasets and third-party tools such as OFSAA, enabling rapid detection, case creation, and tracking of suspicious financial transactions.}
        \resumeItem{\textbf{Collaborated closely with Architects and cross-functional teams to ensure technical vision and solution design alignment, focusing on security best practices in authentication and authorization domains.}}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove major quality improvements for \textbf{Azure Cognitive Services} by rigorously testing new features using \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Azure AI Studio}, identifying and resolving critical defects to enhance performance and stability.}
        \resumeItem{Streamlined code testing, database analysis, and container-based workflows using \textbf{Jupyter}, \textbf{Postman}, \textbf{Visual Studio}, \textbf{Java}, \textbf{Python}, \textbf{C\#}, and \textbf{Kusto} queries, improving product reliability and observability by an estimated 30\%.}
        \resumeItem{\textbf{Developed and enhanced CI/CD pipelines to support continuous integration and deployment of AI-driven services, ensuring secure and automated release management.}}
        \resumeItem{Collaborated with cross-functional engineering and product teams to validate next-generation \textbf{Azure AI} capabilities, contributing to more scalable, production-ready cognitive and LLM-based services used in enterprise scenarios.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Development Engineer Co-op}{Jan 2024 -- Apr 2024}
      {ESO}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Ramped up on \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure} within the first month on a complex codebase, enabling independent ownership of sprint user stories and production bug fixes.}
        \resumeItem{Leveraged \textbf{Pluralsight} courses and mentorship programs to introduce code-quality and refactoring improvements, helping the team deliver key Medic1 milestones on time and increasing development velocity by an estimated 10 to 15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Jan 2022 -- Aug 2022}
      {People Tech Group Private Ltd.}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of new haptic feedback features for Cadillac vehicles from concept to integration, including requirements analysis, implementation, and client communication to align UX behavior with safety and brand guidelines.}
        \resumeItem{Developed interactive frontend application for Cadillac design platform using \textbf{React} with modern component architecture, integrating with backend APIs to deliver responsive user experience while collaborating with design and engineering teams.}
        \resumeItem{Designed and tested \textbf{haptics} functionality on prototype hardware, validating vibration patterns and timing in realistic driving scenarios before in-car integration.}
        \resumeItem{Contributed to infotainment UI and interaction workflows using \textbf{Qt}, \textbf{Rhapsody}, \textbf{WeCAN}, and \textbf{C++} in a complex automotive HMI environment, improving responsiveness and reliability of production systems.}
        \resumeItem{Implemented \textbf{CI/CD pipelines} for automotive software using \textbf{Jenkins}, \textbf{SourceTree}, and \textbf{Bitbucket}, automating builds and tests for infotainment components and reducing deployment time and integration issues.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Implemented next-generation analytical models and core components using \textbf{Java}, \textbf{C\#}, \textbf{Python}, \textbf{C++}, \textbf{SQL}, data structures, and algorithms, delivering an average 40\% performance improvement across 5+ business-critical models.}
        \resumeItem{Built a \textbf{Python}-based application to convert large model data into optimized binary formats, reducing file sizes from approximately 2GB to 200MB and significantly cutting load and processing times.}
        \resumeItem{Diagnosed and resolved complex production issues, including critical memory leaks and performance bottlenecks, using systematic debugging, profiling, and root-cause analysis techniques.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process-improvement practices to streamline development workflows and reduce waste in engineering processes.}
        \resumeItem{Mentored new hires through induction sessions, pair programming, and peer reviews, helping onboard engineers faster and strengthening overall engineering culture.}
        \resumeItem{\textbf{Led a team of three engineers and served as Scrum Master, facilitating Agile ceremonies and driving continuous improvement in delivery and team performance.}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using \textbf{React}, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with \textbf{Node.js} and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}