\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Software Engineer} with 5+ years of experience delivering robust, high-quality software in fast-paced financial services and enterprise environments. Skilled in \textbf{Java/Spring Boot}, with strong expertise in designing and maintaining complex backend systems, system integration, and testing automation. Adept at collaborating across business and technical teams to analyze requirements and implement scalable solutions for Capital Markets, including \textbf{Repo trading} and \textbf{trading platform} integrations. Proven ability to thrive in dynamic environments while owning critical deliverables and mentoring team members.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Spring MVC, RESTful APIs, Microservices Architecture \\
     \textbf{Databases}: Oracle, PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
     \textbf{Operating Systems}: Linux, Windows \\
     \textbf{Tools and Platforms}: Oracle SQL Developer, JIRA, Maven, Gradle, Jenkins, Git, GitHub Actions, Azure DevOps \\
     \textbf{Testing and Automation}: JUnit, Cucumber, Selenium, Automated Functional and Regression Testing \\
     \textbf{Messaging and Integration}: Apache Kafka, MQ, REST, SOAP, JSON, FIX Protocol \\
     \textbf{Cloud Platforms}: AWS, Azure (AKS, Data Factory, DevOps) \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, Release and Change Management, Continuous Integration/Delivery
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, significantly improving data quality and overall system reliability.}
        \resumeItem{Automated \textbf{Java}-based regression and functional testing suites using \textbf{Cucumber} and \textbf{Selenium}, enhancing test coverage and reducing manual effort by 40\%.}
        \resumeItem{Collaborated with development teams and business stakeholders to analyze and document technical and business requirements for complex data and system integration tasks aligned to financial services needs.}
        \resumeItem{Supported release and change management activities by utilizing automated deployment tools and managing application upgrades, ensuring platform currency and minimal downtime.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements in \textbf{Azure Cognitive Services} by testing features through SDKs, REST APIs, and Azure AI Studio, resulting in enhanced platform stability.}
        \resumeItem{Streamlined workflows using \textbf{Java}, Python, C\#, and Kusto queries, improving product reliability and observability by 30\%.}
        \resumeItem{Collaborated with cross-functional product and engineering teams to validate next-generation AI capabilities and contribute to scalable cloud services.}
        \resumeItem{Enhanced monitoring and troubleshooting processes applying best practices that align with automated support for escalated incidents.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Acquired expertise in \textbf{C\#}, \textbf{C++}, \textbf{XSLT}, and \textbf{Azure} technologies to independently own sprint tasks and production bug fixes.}
        \resumeItem{Introduced code-quality and refactoring improvements, collaborating closely with cross-functional teams to enhance development velocity and software robustness.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led design and implementation of automotive haptic feedback features integrating frontend React apps and backend APIs, ensuring seamless user experience.}
        \resumeItem{Developed features in \textbf{Qt}, \textbf{C++}, and \textbf{WeCAN}, enhancing UI responsiveness within complex automotive systems.}
        \resumeItem{Implemented CI/CD pipelines using Jenkins and Bitbucket to automate builds, tests, and deployments, improving release efficiency and quality.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed core components and analytical models using \textbf{Java}, \textbf{C\#}, \textbf{Python}, and SQL, achieving a 40\% performance improvement across business-critical solutions.}
        \resumeItem{Built a \textbf{Python}-based tool converting large datasets into optimized binary formats, enhancing data processing efficiency across teams.}
        \resumeItem{Served as Scrum Master while mentoring engineers and collaborating with Product Management to refine feature requirements and improve agile processes.}
        \resumeItem{Diagnosed and resolved production issues, including memory leaks and performance bottlenecks, ensuring high system availability and reliability.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}