\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Senior Data Engineer} with 6+ years of experience architecting, developing, and deploying \textbf{cloud-native data engineering solutions} leveraging \textbf{AWS} services including \textbf{AWS Glue}, \textbf{AWS Lambda}, and \textbf{S3}. Expert in building scalable \textbf{data pipelines} using Python and SQL with a strong focus on data quality, orchestration, and cloud automation. Proven ability to consult clients on \textbf{data and AI engagements}, improve data architectures, and deliver impactful \textbf{big data} solutions in fast-paced environments. Collaborative team player with excellent communication skills and dedication to mentorship and quality delivery.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, SQL, Java, C++, C\#, Bash, PowerShell \\
     \textbf{Data Engineering}: AWS Glue, AWS Lambda, Medallion Architecture, Apache Airflow, Jenkins, Azure Data Factory, DBT \\
     \textbf{Cloud Platforms}: AWS (EC2, S3, Lambda, Glue, CloudFormation, DynamoDB), Azure, GCP \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, DynamoDB, Oracle, MSSQL, Redis \\
     \textbf{Big Data \& Analytics}: Spark, Apache Kafka, Real-time Data Processing, Event-driven Architecture \\
     \textbf{DevOps Tools}: Docker, Kubernetes, Jenkins, Git, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, Automated Testing, Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, Scalable Systems Design, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed scalable \textbf{data validation workflows} using \textbf{Python} and \textbf{SQL} on \textbf{Azure Data Notebooks} to ensure integrity of \textbf{fraud detection pipeline} data, enhancing downstream reliability.}
        \resumeItem{Automated functional and regression testing using Java with \textbf{Cucumber}, \textbf{Selenium}, and Behavior-Driven Development, improving software delivery efficiency by 40\%.}
        \resumeItem{Supported fraud monitoring initiatives by designing and maintaining ETL workflows handling large-scale transactional datasets, collaborating with cross-functional teams to optimize data processing.}
        \resumeItem{Authored complex SQL queries and contributed to pipeline orchestration improvements following Agile methodologies, ensuring high-quality releases and robust ETL performance.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led design and validation of cloud data pipelines using \textbf{Azure} and \textbf{Python}, enhancing quality of \textbf{Azure Cognitive Services} and enabling efficient integration of AI-driven solutions.}
        \resumeItem{Conducted extensive testing and debugging of \textbf{REST APIs} and SDKs with \textbf{Postman} and automated container pipelines to improve system observability by 30\%.}
        \resumeItem{Pioneered training and evaluation of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, improving latency and throughput for real-time AI workloads through systematic benchmarking and tuning.}
        \resumeItem{Collaborated with engineering and product teams to build scalable, production-ready \textbf{AI} and data solutions, strengthening platform capabilities for enterprise customers.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Quickly onboarded into critical components using \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure}, achieving independent development and production issue resolution.}
        \resumeItem{Propelled code quality and refactoring initiatives through self-directed and mentorship-driven learning, increasing delivery velocity and maintainability by up to 15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led end-to-end development of haptic feedback features for Cadillac vehicles including requirement analysis, implementation, and client interactions to ensure alignment with UX and brand standards.}
        \resumeItem{Built interactive React frontend integrated with backend APIs for Cadillac design platform, delivering smooth user experiences aligned with automotive use cases.}
        \resumeItem{Tested and validated haptics features on prototype hardware, ensuring reliability and accuracy prior to in-vehicle deployment.}
        \resumeItem{Contributed to automotive infotainment UI workflows with \textbf{Qt}, \textbf{Rhapsody}, \textbf{WeCAN}, and \textbf{C++}, enhancing system responsiveness for production.}
        \resumeItem{Implemented \textbf{CI/CD} pipelines with \textbf{Jenkins} and Git-based tools, automating builds and minimizing integration issues in the automotive software lifecycle.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed and optimized analytical models using \textbf{Java}, \textbf{C\#}, \textbf{Python}, \textbf{C++}, and \textbf{SQL}, improving performance by 40\% across multiple business-critical applications.}
        \resumeItem{Built Python tools to convert large datasets into compact binary formats, reducing load times by 90\% for downstream computations.}
        \resumeItem{Investigated and resolved complex production issues through profiling and root-cause analysis, improving system reliability.}
        \resumeItem{Achieved \textbf{Lean Six Sigma} certification and applied process improvements to enhance development efficiency and reduce defects.}
        \resumeItem{Mentored new engineers, facilitating faster onboarding and fostering a collaborative engineering culture.}
        \resumeItem{Collaborated closely with Product Management and Research, leading a team of three, and served as \textbf{Scrum Master} ensuring Agile team delivery excellence.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}