\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years experience designing and delivering secure, scalable, enterprise-ready web applications and backend services. Expert in \textbf{React}, \textbf{JavaScript/TypeScript}, and \textbf{Python} API development using frameworks such as \textbf{FastAPI} and \textbf{Django}, with strong skills integrating diverse data sources including relational and NoSQL databases. Proven ability deploying and troubleshooting on \textbf{Azure} and \textbf{AWS}, applying \textbf{DevOps} best practices like CI/CD, containerization with \textbf{Docker}, and cloud orchestration. Collaborative team player experienced working in cross-functional teams to embed AI workflows and deliver high-quality client solutions.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, JavaScript, TypeScript, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: FastAPI, Django, Flask, Spring Boot, Node.js, RESTful APIs, Microservices Architecture \\
     \textbf{Frontend}: React, Angular, JavaScript, HTML/CSS \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: Azure (AKS, DevOps, Data Factory), AWS (EC2, Lambda, S3, CloudFormation), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Data Streaming}: Apache Kafka, Real-time Data Processing, Event-driven Architecture \\
     \textbf{Testing and QA}: PyTest, Selenium, Cucumber, JUnit, Postman, TDD/BDD, Automated Testing \\
     \textbf{Security}: OAuth, Azure AD Authentication, Application Security Best Practices \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, significantly improving data quality and system reliability.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber, Selenium, and BDD practices, reducing manual testing effort by 40\% and increasing feature reliability.}
        \resumeItem{\textbf{Designed and integrated frontend React components and backend Python APIs, ensuring seamless end-to-end feature delivery for fraud monitoring workflows.}}
        \resumeItem{Delivered multiple high-impact initiatives by designing and optimizing complex SQL queries, collaborating within cross-functional Agile teams to ensure timely, high-quality releases.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Data Engineer}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements for \textbf{Azure Cognitive Services} by testing new features with \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Azure AI Studio}, enhancing performance and stability.}
        \resumeItem{\textbf{Collaborated with engineering teams to build and integrate Python backend services using FastAPI, facilitating AI workflow embedding and scalable API delivery.}}
        \resumeItem{Pioneered training and optimization of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, achieving performance gains and latency reduction for real-time workloads.}
        \resumeItem{Contributed to next-gen \textbf{Azure AI} capabilities by validating scalable, production-ready cognitive and LLM-based services in collaboration with product teams.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Development Engineer Co-op}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Ramped up on \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure} within first month on a complex codebase, enabling independent ownership of sprint user stories and production bug fixes.}
        \resumeItem{\textbf{Implemented secure authentication features and contributed to backend API development, enhancing application security and integration on Azure cloud environment.}}
        \resumeItem{Leveraged \textbf{Pluralsight} courses and mentorship programs to introduce code-quality and refactoring improvements, increasing team development velocity by 10-15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of new haptic feedback features for Cadillac vehicles from concept through integration, including client communication to align UX with safety and brand guidelines.}
        \resumeItem{Developed interactive frontend applications using \textbf{React} with modern component architecture, integrating backend APIs to create responsive user experiences.}
        \resumeItem{Designed and tested \textbf{haptics} functionality on prototype hardware, validating vibration patterns and timing in realistic scenarios.}
        \resumeItem{Contributed to infotainment UI and interaction workflows using \textbf{Qt}, \textbf{Rhapsody}, \textbf{WeCAN}, and \textbf{C++}, improving system responsiveness and reliability.}
        \resumeItem{Implemented \textbf{CI/CD pipelines} using \textbf{Jenkins}, \textbf{SourceTree}, and \textbf{Bitbucket}, automating builds and tests for infotainment components and reducing integration issues.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer II}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Implemented next-generation analytical models and core components using \textbf{Java}, \textbf{C\#}, \textbf{Python}, \textbf{C++}, and \textbf{SQL}, delivering 40\% performance improvements across business-critical models.}
        \resumeItem{\textbf{Built Python-based tools to convert large model data into optimized binary formats, accelerating downstream processing and reducing file sizes significantly.}}
        \resumeItem{Diagnosed and resolved complex production issues including memory leaks and bottlenecks using detailed profiling and root-cause analysis.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process-improvement methods to streamline engineering workflows and reduce waste.}
        \resumeItem{Mentored new hires through pair programming and code reviews, improving onboarding effectiveness and code quality.}
        \resumeItem{Collaborated with Product Management and Research on feature requirements, leading a team of three engineers and serving as \textbf{Scrum Master} for multiple releases.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed expense tracking solution leveraging AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation for serverless architecture.}
            \resumeItem{Enhanced monitoring by integrating Amazon Textract for intelligent extraction of data from receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications through Python Lambda scripts, extracting critical information and triggering alerts via SNS, increasing user efficiency.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Contributed to a project simulating Hurricane Fiona’s power outages in Atlantic Canada, supporting efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java and JUnit test cases to ensure high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to optimize power restoration routes, reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}