\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Software Development Engineer in Test (SDET)} with 5+ years of experience in \textbf{Java, Selenium, and API automation} leveraging \textbf{BDD frameworks}. Strong expertise in designing, implementing, and troubleshooting \textbf{automation frameworks}, including \textbf{Cucumber}, \textbf{Maven}, \textbf{Jenkins}, and version control with \textbf{Git/Bitbucket}. Skilled in \textbf{RESTful API} testing with \textbf{REST Assured} and integrating automation within Agile \textbf{Scrum} environments. Proven ability to improve test coverage, reduce manual testing efforts, and enhance software quality for enterprise-grade applications.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Automation and Frameworks}: Selenium WebDriver, Cucumber (BDD), REST Assured, JUnit, TestNG, Maven, Jenkins \\
     \textbf{Version Control}: Git, Bitbucket \\
     \textbf{Backend and API Testing}: RESTful APIs, Postman, API Automation \\
     \textbf{Cloud Platforms}: AWS, Azure \\
     \textbf{Development Practices}: Agile/Scrum, TDD/BDD, Code Reviews, CI/CD Pipelines \\
     \textbf{Tools}: Maven, Jenkins, JIRA, Visual Studio, Docker, Kubernetes
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Java}-based automated test suites leveraging \textbf{Selenium}, \textbf{Cucumber (BDD)}, and \textbf{Maven} frameworks to enhance regression testing and increase test coverage by 40\%.}
        \resumeItem{Built robust \textbf{API automation} tests for \textbf{RESTful services} using \textbf{REST Assured}, validating request/response payloads and ensuring early defect detection.}
        \resumeItem{Collaborated within Agile teams following \textbf{Scrum} methodology to implement \textbf{in-sprint automation}, enabling faster feedback cycles and continuous integration with \textbf{Jenkins}.}
        \resumeItem{Managed \textbf{Git} and \textbf{Bitbucket} repositories to establish consistent coding standards and branch strategies, improving team code quality and collaboration.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Designed and executed comprehensive automated tests for \textbf{Azure Cognitive Services} APIs using \textbf{Java}, \textbf{Postman}, and \textbf{RESTful API} frameworks, driving higher reliability and performance.}
        \resumeItem{Developed code automation and containerized workflows integrating \textbf{Jupyter}, \textbf{Postman}, \textbf{Visual Studio}, and \textbf{Java/Python} tools, improving testing efficiency and deployment consistency.}
        \resumeItem{Applied \textbf{BDD} methodologies with \textbf{Cucumber} to foster Behavior Driven Development, enhancing cross-team communication and delivery speed.}
        \resumeItem{Contributed to the creation and maintenance of automation frameworks supporting Agile teams, enabling rapid validation of cloud AI services and APIs.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Enhanced automation efforts by integrating \textbf{BDD} testing principles into legacy services using \textbf{Java} and \textbf{C\#}, boosting test reliability and coverage.}
        \resumeItem{Leveraged Agile planning and \textbf{Scrum} ceremonies to rapidly deliver automated test cases and bug fixes within sprints, improving software quality and development velocity.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed and tested infotainment software with automated and manual approaches using \textbf{Java}, \textbf{Selenium}, and \textbf{Jenkins}, enhancing functional and regression test reliability.}
        \resumeItem{Established and maintained \textbf{CI/CD pipelines} using \textbf{Jenkins}, \textbf{Bitbucket}, and \textbf{SourceTree}, streamlining build, test, and deployment workflows for automotive software.}
        \resumeItem{Collaborated on framework enhancements and reusable utilities for automation, improving test efficiency and maintainability across complex automotive HMI systems.}
        \resumeItem{Implemented feature and regression tests automating interaction workflows and \textbf{API} endpoints, improving defect detection before production integrations.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented automated test suites using \textbf{Java}, \textbf{JUnit}, and \textbf{TestNG} to validate critical business models and analytics, improving release confidence and defect containment.}
        \resumeItem{Created reusable test utilities and automation framework components, facilitating faster creation and maintenance of automated tests for diverse product lines.}
        \resumeItem{Led Agile \textbf{Scrum} teams as \textbf{Scrum Master}, coordinating in-sprint automation efforts to enhance testing speed and quality in continuous delivery cycles.}
        \resumeItem{Collaborated with Product Managers and Developers to refine requirements and integrate automated testing strategies, minimizing manual regression testing and accelerating deployment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}