\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Software Engineer} with 5+ years of experience designing and building \textbf{end-to-end data pipelines} and cloud-native applications for financial services and enterprise clients. Proficient in \textbf{Python} and \textbf{SQL} for data extraction, transformation, and automation, with hands-on experience leveraging \textbf{cloud platforms} including \textbf{AWS}, \textbf{Azure}, and \textbf{GCP}. Skilled in developing \textbf{interactive dashboards} and monitoring workflows that drive business insights and data quality assurance. Strong collaborator in \textbf{Agile} teams, committed to delivering scalable, reliable, and high-impact solutions aligned with business goals.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, SQL, C++, C\#, Bash, PowerShell \\
     \textbf{Data Engineering}: ETL/ELT Pipelines, Data Quality, Data Validation, Data Transformation, SQL Optimization \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture \\
     \textbf{Frontend and BI Tools}: React, JavaScript, Looker, Interactive Dashboards \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation), Azure (DevOps, Data Factory, AKS), \textbf{GCP} \\
     \textbf{DevOps and Orchestration}: Docker, Kubernetes, Jenkins, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Data Streaming}: Apache Kafka, Real-time Data Processing, Event-driven Architecture \\
     \textbf{Testing and QA}: Cucumber, Selenium, JUnit, Postman, Automated Testing, TDD/BDD \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{robust Python} and \textbf{SQL data pipelines} within \textbf{Azure} environment to validate and transform large datasets for fraud detection, improving overall \textbf{data quality} and \textbf{system reliability}.}
        \resumeItem{Automated regression and functional testing using \textbf{Java}-based \textbf{Cucumber} and \textbf{Selenium} BDD suites, reducing manual testing efforts by 40\% and enhancing feature stability.}
        \resumeItem{Built and maintained complex fraud monitoring \textbf{data workflows} that integrate large-scale transactional datasets and third-party tools (\textbf{OFSAA}), enabling near real-time detection and case tracking of suspicious activities.}
        \resumeItem{Collaborated with cross-functional Agile teams to optimize \textbf{SQL queries} and streamline data processes ensuring timely and \textbf{production-ready} releases focused on \textbf{data-driven insights}.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led quality assurance efforts for \textbf{Azure Cognitive Services} by testing AI/ML features using SDKs, REST APIs, and \textbf{Azure AI Studio}, identifying defects that improved \textbf{product stability} and performance.}
        \resumeItem{Enhanced automated code testing and data validation workflows leveraging \textbf{Python}, \textbf{Jupyter}, \textbf{Postman}, and containerized environments, boosting observability and reliability by 30\%.}
        \resumeItem{Trained and benchmarked \textbf{Azure OpenAI GPT} models, improving inference latency and accuracy by 25\% for real-time AI workloads through systematic data analysis and tuning.}
        \resumeItem{Collaborated with cross-disciplinary teams to validate and scale \textbf{AI-enabled data solutions} and analytics services supporting enterprise-level decision making.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Quickly gained proficiency with \textbf{C\#}, \textbf{C++}, \textbf{XSLT}, and \textbf{Azure} tools to independently own production issues and sprint deliverables on complex codebases.}
        \resumeItem{Introduced team-wide code quality improvements and refactoring strategies aligned with best practices, increasing development velocity and maintainability by approximately 15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led full lifecycle development of haptic feedback features for Cadillac vehicles, conducting requirements analysis, implementation, and cross-team coordination to deliver quality automotive UX.}
        \resumeItem{Built an interactive frontend platform using React to visualize automotive configuration, integrating backend APIs with a focus on responsiveness and user experience enhancements.}
        \resumeItem{Tested and validated hardware haptic patterns in real-world driving scenarios, ensuring compliance with functional and safety standards before production deployment.}
        \resumeItem{Contributed to automotive infotainment UI workflows using \textbf{Qt}, \textbf{Rhapsody}, and \textbf{C++}, improving system responsiveness and robustness.}
        \resumeItem{Automated build and deployment pipelines using \textbf{Jenkins} and \textbf{Bitbucket}, reducing integration times and errors across teams.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed data-intensive analytical models and core modules using \textbf{Java}, \textbf{Python}, \textbf{C++}, and \textbf{SQL}, achieving a 40\% performance boost across multiple business-critical systems.}
        \resumeItem{Authored a \textbf{Python ETL tool} converting large datasets into optimized binary formats, cutting file sizes from 2GB to 200MB and dramatically lowering processing latency for downstream analytics.}
        \resumeItem{Diagnosed and resolved complex production issues such as memory leaks and bottlenecks through in-depth profiling and root-cause analysis frameworks.}
        \resumeItem{Applied \textbf{Lean Six Sigma} methodologies to optimize development workflows and elevate engineering process quality.}
        \resumeItem{Mentored junior engineers through structured onboarding and peer code reviews, contributing to a stronger, more collaborative development culture.}
        \resumeItem{Worked closely with product and research teams to define scalable data solutions, leading a team of three engineers and acting as \textbf{Scrum Master} to drive Agile delivery and continuous improvement.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}