\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience designing and developing scalable, cloud-native applications and backend services. Proficient in \textbf{Python}, \textbf{Java}, \textbf{C++}, and \textbf{JavaScript}, with hands-on experience in building distributed systems, performing system analysis, and participating in software architecture design. Skilled in developing and optimizing \textbf{database-driven applications} using relational (PostgreSQL, MySQL) and NoSQL (MongoDB) databases. Experienced in \textbf{unit testing}, \textbf{automated testing frameworks}, and leveraging modern development tools in Agile environments. Strong collaborator with a focus on quality, innovation, and aligning technology solutions with business objectives.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, C++, C\#, Go, Bash, SQL, JavaScript, Perl \\
     \textbf{Backend and Frameworks}: RESTful APIs, Microservices, Spring Boot, Node.js, Unit Testing, Automated Testing Frameworks \\
     \textbf{Frontend}: React, JavaScript, HTML, CSS, Bootstrap, Webpack, Vue \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS, Azure, GCP; Containers and Kubernetes \\
     \textbf{DevOps and Tools}: Git, Jenkins, Docker, Kubernetes, CI/CD Pipelines, Datadog (System Monitoring), GitHub Copilot (AI-assisted coding) \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Solution Documentation, Collaboration with Stakeholders \\
     \textbf{Operating Systems}: Linux, Mac OS, Windows
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Designed and developed backend services using \textbf{Python} and \textbf{SQL} to validate and process large transactional datasets from fraud detection pipelines, improving data integrity and reliability.}
        \resumeItem{Automated regression and functional testing via Java-based frameworks (\textbf{Cucumber}, \textbf{Selenium}) improving feature quality and accelerating delivery cycles.}
        \resumeItem{Built and optimized complex \textbf{SQL} queries and workflows integrated with third-party tools (e.g., OFSAA) enabling effective fraud monitoring and alerting.}
        \resumeItem{Collaborated with cross-functional teams and business stakeholders to align technical implementations with objectives, using Agile methodologies and producing detailed solution documentation.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Contributed to design and testing of scalable AI-based Azure Cognitive Services integrations using multiple programming languages (\textbf{Java}, \textbf{Python}, \textbf{C\#}) and \textbf{REST APIs}.}
        \resumeItem{Improved system observability and reliability by developing containerized workflows and leveraging automated testing tools such as \textbf{Postman} and \textbf{Jupyter}.}
        \resumeItem{Optimized \textbf{OpenAI GPT} model training and evaluation pipelines using Azure OpenAI services, achieving latency reductions and improved performance in production.}
        \resumeItem{Participated in code reviews, solution validation, and collaborated closely with product and engineering teams to ensure robust software architecture and compliance with business goals.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained software components using \textbf{C\#}, \textbf{C++}, and \textbf{XSLT} within Azure cloud environments, adhering to best practices of unit testing and code quality.}
        \resumeItem{Introduced refactoring improvements and enhanced testing coverage, improving system maintainability and sprint delivery velocity by up to 15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led full-stack development efforts for automotive HMI applications using \textbf{React}, \textbf{C++}, and \textbf{Qt}, focusing on system design and responsive user experiences.}
        \resumeItem{Implemented and validated \textbf{haptic feedback} features on prototype hardware with iterative testing and close collaboration across design and engineering teams.}
        \resumeItem{Established and maintained \textbf{CI/CD} pipelines using Jenkins and Bitbucket, streamlining build, test, and deployment cycles for large-scale automotive infotainment software.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented core analytical components and distributed systems in \textbf{Java}, \textbf{Python}, \textbf{C++}, and \textbf{SQL}, improving performance by 40\%.}
        \resumeItem{Developed Python tools for data format optimization reducing payload size by 90\%, enhancing processing efficiency for large-scale disaster modeling applications.}
        \resumeItem{Performed systematic code reviews, debugging, and profiling to identify and fix memory leaks and performance bottlenecks in production systems.}
        \resumeItem{Led Agile Scrum teams as \textbf{Scrum Master}, facilitating delivery alignment with business stakeholders and promoting robust coding standards and solution documentation.}
        \resumeItem{Mentored junior engineers and new hires, sharing knowledge of system design, testing strategies, and coding best practices.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}