\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building end-to-end, cloud-native web applications and backend services for financial services and enterprise organizations. Skilled in \textbf{Python}, \textbf{Java/Spring Boot}, and \textbf{Node.js/React}, with strong experience in \textbf{model development}, \textbf{data preparation}, and deploying applications on \textbf{AWS} and \textbf{Azure}. Proven ability to transform complex datasets into actionable insights to support business decisions and pricing strategies. Strong collaborator with experience working in Agile teams and communicating technical results to both technical and non-technical stakeholders.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, SQL, C++, C\#, Bash, PowerShell \\
     \textbf{Data Science \& ML}: Data Preparation, Model Development, MLOps Concepts, Machine Learning Algorithms, Data Exploration Tools \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, Data Factory, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, TDD/BDD, Automated Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and \textbf{SQL} validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, improving \textbf{data quality} and system \textbf{reliability}.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber, Selenium, and BDD practices, reducing manual testing effort by 40\% and increasing feature reliability.}
        \resumeItem{Built and maintained fraud monitoring workflows leveraging large-scale transactional datasets and third-party tools such as OFSAA, enabling rapid detection and tracking of suspicious financial transactions.}
        \resumeItem{\textbf{Collaborated with cross-functional teams} in an \textbf{Agile environment} to deliver high-impact projects, and contributed to \textbf{continuous improvement} of backend services supporting critical financial operations.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements for \textbf{Azure Cognitive Services} by rigorously testing new features and identifying critical defects, enhancing performance and scalability.}
        \resumeItem{Streamlined data validation, code testing, and container-based workflows using \textbf{Jupyter}, \textbf{Postman}, \textbf{Java}, \textbf{Python}, and \textbf{Kusto} queries, improving product reliability by 30\%.}
        \resumeItem{Led training, evaluation, and optimization of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, improving model performance and reducing latency for real-time use cases.}
        \resumeItem{Supported deployment and integration of machine learning models according to \textbf{MLOps best practices} and collaborated with engineering teams to validate production readiness.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly acquired skills in \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, and \textbf{Azure} on a complex codebase, enabling independent ownership of sprint user stories and critical production bug fixes.}
        \resumeItem{Introduced code-quality and refactoring improvements, increasing development velocity and supporting team adherence to best practices and maintainability.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of automotive haptic feedback features from concept to integration, collaborating closely with clients and engineering teams to ensure performance and safety compliance.}
        \resumeItem{Developed React-based frontend application integrating with backend services to deliver interactive UI solutions for automotive design platforms.}
        \resumeItem{Validated haptic functionality on prototype hardware in real-time scenarios, ensuring accuracy and user experience alignment.}
        \resumeItem{Implemented automated CI/CD pipelines using Jenkins and Bitbucket, enabling efficient build and test cycles for automotive software projects.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed high-performance analytical models and core components using \textbf{Java}, \textbf{Python}, \textbf{SQL}, and advanced algorithms, improving execution speed by 40\% for key insurance pricing models.}
        \resumeItem{Created a \textbf{Python} application converting large model datasets into optimized binary formats, reducing processing times and supporting scalable damage and loss computations.}
        \resumeItem{Troubleshot and resolved complex production issues such as memory leaks and performance bottlenecks using profiling and root-cause analysis techniques.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process improvements to enhance efficiency and reduce waste in development workflows.}
        \resumeItem{Mentored new engineers on data science workflows, code quality, and Agile practices, leading as \textbf{Scrum Master} to drive team collaboration and successful deliveries.}
        \resumeItem{Collaborated with Product and Research teams to refine feature requirements and ensured alignment of analytical models with pricing strategy objectives.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}