\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Detail-oriented \textbf{Software Engineer} with 5+ years of experience in backend development, algorithm design, and AI model evaluation. Proficient in \textbf{Python}, \textbf{JavaScript}, \textbf{C\#}, and \textbf{C++} with strong skills in data structures, debugging workflows, and coding problem solving. Experienced in integrating and optimizing code for performance, testing, and supporting AI chatbot evaluation and training workflows. Proven ability to communicate technical solutions clearly and collaborate effectively in remote, agile environments.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, JavaScript, Java, C++, C\#, SQL, Bash \\
     \textbf{Backend and Frameworks}: Node.js, Spring Boot, RESTful APIs, Microservices \\
     \textbf{Algorithms \& Data Structures}: Problem Solving, Debugging, LeetCode, HackerRank \\
     \textbf{Testing \& Tools}: JUnit, Cucumber, Selenium, Postman, TDD/BDD \\
     \textbf{Cloud Platforms}: AWS, Azure, GCP \\
     \textbf{DevOps}: Docker, Kubernetes, Jenkins, CI/CD Pipelines \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Code Optimization \\
     \textbf{AI/ML Tools}: Azure AI Studio, OpenAI GPT, AI Model Training and Evaluation
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained Python and SQL validation scripts in Azure to ensure correctness of incoming fraud detection data, directly contributing to improved data quality and system accuracy.}
        \resumeItem{Automated regression and functional testing with Java and Cucumber, enforcing BDD practices and reducing manual effort by 40\% while improving feature stability.}
        \resumeItem{Engineered backend workflows processing large-scale transactional data, enhancing fraud monitoring and alert systems to improve detection times.}
        \resumeItem{Collaborated within Agile teams to deliver high-quality releases by optimizing complex SQL queries and backend logic.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led testing and evaluation of \textbf{Azure Cognitive Services} and \textbf{OpenAI GPT} models by designing and executing coding challenges, measuring model output quality, and improving AI chatbot logic and performance.}
        \resumeItem{Streamlined debugging workflows and code validation with \textbf{Python}, \textbf{Java}, \textbf{C\#}, \textbf{Jupyter}, and \textbf{Postman} to enhance AI model reliability by 30\%.}
        \resumeItem{Benchmark-tested and optimized AI models for real-time workloads on Azure OpenAI, achieving significant improvements in correctness and latency.}
        \resumeItem{Collaborated cross-functionally to assess and refine next-generation Azure AI capabilities for scalable, production-ready cognitive services.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained expertise in \textbf{C\#}, \textbf{C++}, \textbf{XML}, and \textbf{Azure}, taking ownership of sprint tasks including bug fixes and feature delivery in a complex, modular codebase.}
        \resumeItem{Applied code-quality improvements and refactoring, contributing to faster delivery of Medic1 project milestones by enhancing reliability and maintainability.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and developed haptic feedback features for Cadillac vehicles, integrating software and hardware to meet user experience and safety requirements.}
        \resumeItem{Built React-based frontend applications interacting with backend APIs, ensuring responsive and seamless user interaction aligned with client specifications.}
        \resumeItem{Tested and validated haptics functionality on prototype hardware to ensure accuracy and real-world applicability prior to vehicle integration.}
        \resumeItem{Developed automotive infotainment UI using \textbf{Qt}, \textbf{C++}, and \textbf{Rhapsody}, improving interaction responsiveness and reliability in production environments.}
        \resumeItem{Implemented CI/CD pipelines using \textbf{Jenkins} and \textbf{Bitbucket}, improving automated build and test processes for automotive software.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed advanced analytical models using \textbf{Python}, \textbf{Java}, \textbf{C\#}, and \textbf{C++}, utilizing strong understanding of data structures and algorithms to enhance model performance by 40\%.}
        \resumeItem{Created Python tools to optimize model data conversion and file compression, improving processing speed and resource use.}
        \resumeItem{Executed root-cause analysis and debugging to resolve complex production issues, improving system stability and reliability.}
        \resumeItem{Applied Lean Six Sigma methodologies to drive process improvements in development workflows.}
        \resumeItem{Mentored junior engineers and led Scrum processes, fostering collaborative agile environments and accelerating team delivery.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}