\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Azure Architect and DevOps Engineer} with 5+ years of experience designing and managing scalable, secure, and highly available cloud infrastructures on \textbf{Azure} and \textbf{AWS}. Skilled in \textbf{Infrastructure as Code} using \textbf{Terraform} and \textbf{ARM templates}, scripting with \textbf{Python}, \textbf{PowerShell}, and \textbf{Bash}, and implementing \textbf{CI/CD pipelines} using \textbf{Azure DevOps}. Experienced in automation, cost optimization, monitoring, and driving cloud-native innovations with a focus on \textbf{Azure Virtual Desktop} deployments and cloud security compliance. Proven ability to support enterprise-grade solutions, mentor teams, and collaborate across global technology environments.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, PowerShell, Bash, Java, C\#, SQL, Terraform HCL \\
     \textbf{Cloud Platforms}: Azure (VMs, Azure Virtual Desktop, AKS, DevOps, Data Factory), AWS (EC2, Lambda, S3), GCP \\
     \textbf{Infrastructure as Code}: Terraform, ARM Templates, CloudFormation \\
     \textbf{DevOps Tools}: Azure DevOps, Jenkins, Git, GitHub Actions, CI/CD Pipelines, Docker, Kubernetes \\
     \textbf{Networking}: VPN, Routing, Firewall Configuration, Network Security in Cloud Environments \\
     \textbf{Containers and Orchestration}: Docker, Kubernetes, AKS \\
     \textbf{Databases}: MSSQL, PostgreSQL, MySQL, MongoDB, Redis \\
     \textbf{Monitoring and Automation}: Automated Scripting, System Analysis, Performance and Capacity Planning \\
     \textbf{Development Practices}: Agile/Scrum, System Design, Code Reviews, Security Compliance, JIRA
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in \textbf{Azure Data Notebooks} to verify incoming data from fraud detection pipelines, improving data quality and system reliability critical for cloud-based solutions.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber and Selenium, improving pipeline delivery and accelerating release cycles by 40\%.}
        \resumeItem{Built and maintained fraud monitoring workflows leveraging large-scale transactional datasets and third-party tools, enabling rapid detection and case management aligned with security and compliance standards.}
        \resumeItem{Collaborated in Agile teams to design and optimize SQL queries and backend processes, ensuring secure, scalable solutions deployed on \textbf{Azure Cloud} environments.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements for \textbf{Azure Cognitive Services} by rigorous testing leveraging \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Azure AI Studio} adhering to cloud best practices.}
        \resumeItem{Streamlined container-based workflows and automated code testing using \textbf{Jupyter}, \textbf{Postman}, and \textbf{Azure DevOps}, improving cloud solution reliability and observability by 30\%.}
        \resumeItem{Led training and evaluation of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, reducing response latency and improving performance metrics by 25\% through optimized cloud deployment techniques.}
        \resumeItem{Partnered with engineering teams to validate scalable \textbf{Azure AI} services, contributing to enhanced cloud-native architecture and deployment methodologies.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Accelerated proficiency with \textbf{Azure} services alongside \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, and \textbf{C++}, gaining ability to manage cloud-related user stories and bug fixes efficiently.}
        \resumeItem{Improved code quality and development velocity by introducing best practices in code refactoring and leveraging \textbf{Pluralsight} Azure and DevOps training resources.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led end-to-end development of features and integration aligning front-end and back-end systems, with emphasis on automation and performance in embedded systems.}
        \resumeItem{Developed interactive frontend applications with React and backend integration, delivering responsive user experience within complex system architecture.}
        \resumeItem{Contributed to infotainment user interfaces and workflows using \textbf{Qt} and \textbf{C++} in a multi-threaded environment, enhancing system robustness.}
        \resumeItem{Implemented and managed \textbf{CI/CD pipelines} using \textbf{Jenkins}, \textbf{Bitbucket}, and \textbf{SourceTree}, automating builds and deployments to streamline development cycles.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and optimized core analytical models and infrastructure using \textbf{Java}, \textbf{Python}, \textbf{C\#}, and \textbf{SQL}, improving performance and scalability by over 40\%.}
        \resumeItem{Developed Python automation tools converting large datasets into efficient binary formats, significantly reducing processing and loading times within cloud-related systems.}
        \resumeItem{Resolved critical production issues and memory leaks via systematic debugging and root-cause analysis, improving system reliability and availability.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and implemented process improvements for cloud and on-prem automation workflows, enhancing engineering efficiency.}
        \resumeItem{Mentored new hires and led Agile/Scrum teams as \textbf{Scrum Master}, fostering collaboration and continuous delivery principles.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {\textbf{Dalhousie University, Halifax, Canada}}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {\textbf{GRIET, Hyderabad, India}}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}