\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience designing and developing scalable, high-performance web applications and backend services. Proficient in modern frontend frameworks including \textbf{React} and \textbf{JavaScript/TypeScript}, with strong expertise in building intuitive, performant user interfaces for enterprise SaaS platforms. Demonstrated ability to deliver end-to-end solutions on cloud environments such as \textbf{AWS} and \textbf{Azure}, with a focus on CI/CD automation and infrastructure optimization. Proven leadership experience mentoring engineers and collaborating across product, design, and AI/ML teams to deliver complex initiatives for clients including \textbf{TD Bank} and \textbf{Microsoft}. Passionate about driving excellent UX and frontend architecture for AI/ML platforms at scale.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: JavaScript, TypeScript, Java, Python, C++, C\# \\
     \textbf{Frontend Frameworks}: React, Angular (familiar), HTML5, CSS3, JSX \\
     \textbf{Backend and Frameworks}: Node.js, Spring Boot, RESTful APIs, Microservices \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, Data Factory, AKS) \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, GitHub Actions, Azure DevOps, CI/CD Pipelines, Terraform \\
     \textbf{Testing and QA}: Jest, Cucumber, Selenium, TDD/BDD, Automated Testing, Performance Testing \\
     \textbf{Data Streaming}: Apache Kafka, Event-driven Architecture \\
     \textbf{Development Practices}: Agile/Scrum, System Design, Scalability Optimization, Code Reviews
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Designed and implemented performant, scalable frontend components using \textbf{React} and \textbf{JavaScript}, enhancing user workflows for financial fraud detection platforms.}
        \resumeItem{Automated regression and functional testing by developing test suites using \textbf{Cucumber}, \textbf{Selenium}, and \textbf{BDD} methodologies, increasing feature reliability and reducing manual QA effort by 40\%.}
        \resumeItem{Built and maintained complex data validation pipelines with Python and SQL in Azure Data Notebooks, improving data accuracy for mission-critical fraud detection workloads.}
        \resumeItem{Collaborated effectively in Agile teams with product managers and designers, contributing to UX refinement and on-time delivery of multiple high-impact initiatives.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led frontend testing and validation of \textbf{Azure Cognitive Services} features using SDKs, REST APIs, and \textbf{Azure AI Studio}, ensuring robust and performant AI/ML capabilities.}
        \resumeItem{Improved product observability and reliability for AI workloads by integrating tooling such as \textbf{Jupyter}, \textbf{Postman}, and \textbf{Kusto} queries, contributing to a 30\% reduction in support incidents.}
        \resumeItem{Optimized \textbf{OpenAI GPT} model training and evaluation pipelines, reducing latency in real-time inferencing scenarios by 25\%, directly impacting user experience in AI services.}
        \resumeItem{Collaborated with ML researchers, product managers, and engineers to design scalable, user-friendly interfaces and workflows for cutting-edge \textbf{AI/ML platform} capabilities.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Worked on frontend and backend improvements using \textbf{C\#} and \textbf{Azure}, quickly learning new technologies to enhance platform performance and user experience.}
        \resumeItem{Introduced code quality and refactoring best practices, improving maintainability and development velocity, supporting timely delivery of core product milestones.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of interactive frontend application for Cadillac design platform using \textbf{React} and modern component architectures, enhancing responsiveness and UX.}
        \resumeItem{Collaborated closely with design and engineering teams to model complex configurations and deliver intuitive automotive UI features.}
        \resumeItem{Designed and validated haptics functions on prototype hardware, contributing to user experience and system reliability in HMI applications.}
        \resumeItem{Improved CI/CD pipelines with \textbf{Jenkins}, \textbf{Bitbucket}, and SourceTree, automating deployment workflows and reducing integration errors.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed scalable backend systems and analytical models using \textbf{Java}, \textbf{Python}, and \textbf{C++}, improving model performance by 40\% in production environments.}
        \resumeItem{Built tools to optimize large data conversions from model outputs into binary formats, reducing load times by over 85\%, facilitating faster analytics.}
        \resumeItem{Diagnosed and fixed critical memory and performance bottlenecks through detailed profiling and root cause analysis, enhancing system stability.}
        \resumeItem{Mentored junior engineers, led feature design discussions, and served as \textbf{Scrum Master}, driving best practices, quality, and on-time delivery across multiple releases.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}