\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building scalable, cloud-native web applications and backend automation systems, specializing in enterprise and financial services domains. Proficient in \textbf{Java/Spring Boot}, \textbf{Node.js/React}, and \textbf{Python}, with expertise in designing \textbf{microservices}, RESTful APIs, and event-driven architectures. Experienced in deploying and optimizing systems on \textbf{AWS} and \textbf{Azure}, with a strong focus on \textbf{automation}, performance, and reliability. Demonstrated ability to build backend business logic that automates complex processes, improve system scalability, and mentor engineering teams. Passionate about leveraging innovation to deliver impactful solutions that enhance user experience and operational efficiency.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, TypeScript, C++, C\#, SQL, Bash \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, Nest.js, RESTful APIs, Microservices, Event-driven Architecture \\
     \textbf{Frontend}: React, Next.js, JavaScript, HTML/CSS \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis, DynamoDB, ClickHouse \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, ECS/EKS, CloudFormation, DynamoDB), Azure (DevOps, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Testing and QA}: JUnit, Cucumber, Selenium, Postman, TDD/BDD, Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and SQL validation scripts in \textbf{Azure Data Notebooks} to verify and automate incoming transactional data from fraud detection pipelines, significantly improving data quality and operational efficiency in production.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using \textbf{Cucumber}, Selenium, and BDD practices, decreasing manual testing effort by 40\% and boosting release reliability.}
        \resumeItem{Developed and optimized backend workflows and automation systems leveraging large-scale transactional datasets and third-party tools, enabling near real-time monitoring and alerting of suspicious activities with minimal manual intervention.}
        \resumeItem{Collaborated cross-functionally following Agile methodologies to deliver high-impact enhancements, emphasizing automation and system scalability in line with business goals.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led quality improvement efforts on \textbf{Azure Cognitive Services} via rigorous testing using SDKs, \textbf{REST APIs}, and \textbf{Azure AI Studio}, enabling highly reliable AI-driven automation features.}
        \resumeItem{Streamlined container-based testing, database pipeline debugging, and monitoring using \textbf{Jupyter Notebooks}, \textbf{Postman}, \textbf{Java}, \textbf{Python}, \textbf{C\#}, and \textbf{Kusto queries}, increasing observability and system uptime by 30\%.}
        \resumeItem{Trained, evaluated, and tuned \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, boosting performance metrics by 25\% and reducing latency for real-time, AI-powered automation tasks.}
        \resumeItem{Collaborated with cross-disciplinary teams to validate and deploy scalable backend AI automation capabilities, enhancing enterprise-grade cognitive service workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly acquired expertise in \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure} to independently own and deliver sprint user stories related to backend service automation and bug fixes.}
        \resumeItem{Improved code quality and system maintainability by introducing refactoring strategies and test coverage enhancements, helping accelerate feature delivery and reduce technical debt.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led end-to-end development of new haptic feedback features, driving safety and user experience improvements by aligning software behavior with automotive standards and client requirements.}
        \resumeItem{Built interactive frontend tools using \textbf{React} integrated with backend APIs, ensuring seamless real-time user interaction for automotive configuration platforms.}
        \resumeItem{Contributed to infotainment UI workflows using \textbf{Qt}, \textbf{Rhapsody}, \textbf{WeCAN}, and \textbf{C++}, enhancing system stability and responsiveness in complex automotive embedded systems.}
        \resumeItem{Designed and implemented \textbf{CI/CD pipelines} with \textbf{Jenkins} and \textbf{Bitbucket}, automating build, test, and deployment processes, facilitating faster delivery cycles with reduced integration risks.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed next-generation analytical models and core backend components using \textbf{Java}, \textbf{C\#}, \textbf{Python}, and \textbf{C++}, optimizing performance by 40\% and improving scalability to support business-critical insurance analytics.}
        \resumeItem{Created a \textbf{Python} toolchain to convert large model datasets into optimized binary formats, reducing data load times and enabling efficient damage computation for insurance risk assessment.}
        \resumeItem{Diagnosed and resolved complex production bottlenecks and memory leaks through systematic debugging and profiling, improving system reliability in high-throughput environments.}
        \resumeItem{Achieved \textbf{Lean Six Sigma} certification and applied process improvements to streamline engineering workflows and reduce waste across development cycles.}
        \resumeItem{Mentored new hires and led scrum teams, fostering knowledge sharing and continuous improvement in backend automation and system design practices.}
        \resumeItem{Partnered with product management and research teams to define scalable solutions that enhance automation and customer retention strategies within insurance product lines.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}