\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \enspace | \enspace +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} and Platform Development Engineer with 5+ years of experience building and automating secure, scalable, and cloud-native backend services and infrastructure. Skilled in \textbf{C\# .NET}, \textbf{Node.js}, \textbf{PowerShell}, and \textbf{Bash} scripting, with strong expertise in designing and maintaining \textbf{CI/CD pipelines} using \textbf{GitHub Actions}, \textbf{Azure DevOps}, and container orchestration via \textbf{Docker} and \textbf{Kubernetes}. Proven ability to deploy and manage applications on \textbf{AWS} and \textbf{Azure} clouds, improve platform reliability, and drive adoption of best DevOps practices. Experienced collaborating across teams to deliver resilient infrastructure supporting enterprise software products.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: C\#, Java, Python, SQL, Bash, PowerShell, C++ \\
     \textbf{Backend and Frameworks}: .NET, Spring Boot, Node.js, RESTful APIs, Microservices \\
     \textbf{DevOps/Infrastructure}: CI/CD (GitHub Actions, Azure DevOps, Jenkins), Terraform, Pulumi, Docker, Kubernetes \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, RDS, DynamoDB), Azure (DevOps, AKS, Data Factory) \\
     \textbf{Databases}: MongoDB, MySQL, PostgreSQL, RDS, Oracle \\
     \textbf{Messaging}: Kafka, RabbitMQ, AWS SQS \\
     \textbf{Testing}: JUnit, Cucumber, Selenium, TDD, BDD, Automated Testing \\
     \textbf{Monitoring}: Observability, Logging, Performance Monitoring \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability, Disaster Recovery
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, improving platform data integrity and reliability.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber and Selenium with BDD practices, enhancing quality and accelerating CI/CD pipeline throughput.}
        \resumeItem{Built and maintained fraud monitoring workflows to rapidly detect, escalate, and track suspicious transactions, integrating third-party tools in a secure and compliant manner.}
        \resumeItem{Collaborated extensively with cross-functional teams to optimize complex SQL queries and streamline delivery processes following Agile methodologies, driving timely and high-quality software releases.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led quality assurance efforts on Azure Cognitive Services, utilizing SDKs, REST APIs, and Azure AI Studio to identify and fix critical defects improving platform performance and stability.}
        \resumeItem{Streamlined automated testing and deployment workflows leveraging containerized environments, Java, Python, C\#, and Kusto queries, enhancing observability and platform scalability.}
        \resumeItem{Enhanced AI model training and deployment pipelines for Azure OpenAI, boosting key metrics by 25\% and reducing latency through hands-on optimization and benchmarking techniques.}
        \resumeItem{Collaborated with product and engineering teams to build scalable cognitive services, contributing to infrastructure automation and continuous integration improvements.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained rapid proficiency with XSLT, XML, C\#, C++, and Azure, independently handling sprint user stories and fixing production issues, contributing to platform stability and feature development.}
        \resumeItem{Introduced automated testing best practices and code refactoring improvements, increasing team agility and maintainability of critical healthcare platform codebases.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led feature development and integration of haptic feedback systems for automotive clients, ensuring compliance with safety standards and smooth UX across multiple platforms.}
        \resumeItem{Developed frontend React applications integrated with backend APIs, improving automotive design platform responsiveness and user interaction.}
        \resumeItem{Designed and tested haptics on prototype hardware, validating vibration patterns in real-world driving scenarios before deployment.}
        \resumeItem{Contributed to automotive infotainment UI development using Qt, Rhapsody, WeCAN, and C++ in complex HMI environments, focusing on reliability and responsiveness.}
        \resumeItem{\textbf{Automated build and deployment pipelines} using Jenkins, SourceTree, and Bitbucket, implementing CI/CD workflows that reduced integration friction and accelerated release cycles.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed and optimized analytic models and core components using Java, C\#, Python, C++, and SQL, achieving up to 40\% performance improvements for business-critical systems.}
        \resumeItem{Built Python tools to convert large datasets into optimized binary formats, reducing size by 90\% and significantly enhancing data load and processing times.}
        \resumeItem{Performed root cause analysis and resolved critical memory leaks and bottlenecks, improving platform reliability and uptime.}
        \resumeItem{Applied \textbf{Lean Six Sigma} methodologies to improve development processes, increasing efficiency and reducing waste.}
        \resumeItem{Mentored new engineers and led a team of three, providing technical guidance and acting as Scrum Master to facilitate agile delivery practices.}
        \resumeItem{Collaborated closely with product and research teams to design scalable solutions with strong focus on quality, scalability, and maintainability in distributed environments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}