\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building scalable backend services and cloud-native applications. Skilled in \textbf{Python}, \textbf{Java}, and \textbf{JavaScript/Node.js} with strong expertise in \textbf{API design}, \textbf{data pipelines}, and \textbf{containerized deployments using Docker and Kubernetes}. Experienced collaborating with ML teams to integrate \textbf{LLM} workflows and develop AI-powered applications. Proven ability to deliver impactful enterprise-grade solutions in fast-paced, Agile environments.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, JavaScript/TypeScript, C++, C\#, SQL, Bash \\
     \textbf{Backend \& Frameworks}: RESTful APIs, Microservices, Spring Boot, Node.js, Express \\
     \textbf{AI/ML/LLM Tools}: HuggingFace Transformers, LangChain, LlamaIndex, OpenAI GPT, WandB, LM Evaluation Harness \\
     \textbf{Data \& Vector Databases}: PostgreSQL, MongoDB, DynamoDB, Redis, Pinecone, FAISS \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation), Azure (OpenAI, Data Factory, AKS), GCP \\
     \textbf{DevOps \& Infrastructure}: Docker, Kubernetes, Jenkins, GitHub Actions, CI/CD, Terraform \\
     \textbf{Testing \& Monitoring}: JUnit, Cucumber, Postman, TDD/BDD, Observability best practices \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, Experiment Tracking (MLflow, WandB)
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and SQL data validation pipelines in \textbf{Azure} to verify data from fraud detection workflows, improving data quality and \textbf{system reliability} for large-scale transactional datasets.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using \textbf{Cucumber} and \textbf{BDD} practices, enhancing \textbf{feature reliability} and reducing testing cycles by 40\%.}
        \resumeItem{Built and maintained backend services integrating data workflows to support \textbf{AI-powered fraud monitoring}, collaborating with cross-functional teams under Agile methodologies to deliver high-impact solutions.}
        \resumeItem{Optimized complex SQL queries and pipelines to support large data volumes and reduce latency, enabling efficient detection and tracking of suspicious transactions in real time.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led development and rigorous testing of new features for \textbf{Azure Cognitive Services}, including integration with \textbf{OpenAI GPT} models and \textbf{Azure AI Studio}, improving model evaluation and deployment pipelines.}
        \resumeItem{Developed backend utilities using \textbf{Python}, \textbf{C\#}, and \textbf{Java} to automate data processing and containerized workflows, enhancing observability and reliability of ML services by 30\%.}
        \resumeItem{Collaborated closely with ML engineers on \textbf{model training, deployment, and experiment tracking} workflows using \textbf{WandB} and \textbf{Azure OpenAI}, improving inference latency and performance metrics by 25\%.}
        \resumeItem{Validated scalable cognitive and LLM service features via cross-team collaboration, contributing to production readiness of \textbf{custom LLM} models and \textbf{AI workflow automation} in enterprise contexts.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained expertise in \textbf{C\#}, \textbf{C++}, \textbf{Azure}, \textbf{XSLT}, and \textbf{XML} by owning sprint stories and fixing production bugs on a complex codebase, improving system stability and maintainability.}
        \resumeItem{Proposed and implemented code-quality and refactoring improvements, accelerating feature delivery by 10-15\% while mentoring peers through knowledge sharing and coding best practices.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of haptic feedback features for Cadillac vehicles, managing requirements, implementation, and client communication to ensure safety and UX compliance.}
        \resumeItem{Built interactive frontend platform using \textbf{React} integrating with backend APIs for responsive UX, collaborating effectively with design and engineering teams to deliver automotive configuration tools.}
        \resumeItem{Designed and tested haptic functionality on prototype hardware validating vibration patterns for realistic driving scenarios, improving user experience quality.}
        \resumeItem{Enhanced infotainment UI workflows using \textbf{Qt}, \textbf{Rhapsody}, \textbf{WeCAN}, and \textbf{C++}, increasing responsiveness and stability of complex automotive HMI systems.}
        \resumeItem{Implemented \textbf{CI/CD pipelines} for automotive software with \textbf{Jenkins} and \textbf{Bitbucket}, automating builds and tests, reducing integration issues across teams.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed core analytical models and key services in \textbf{Java}, \textbf{C\#}, \textbf{Python}, and \textbf{C++}, improving performance by 40\% across multiple business-critical systems.}
        \resumeItem{Created a \textbf{Python}-based tool to convert large model files into optimized binary formats, reducing data loading times and storage by over 80\%, supporting efficient model evaluation workflows.}
        \resumeItem{Resolved complex production issues including memory leaks and performance bottlenecks using profiling and root-cause analysis, enhancing system robustness.}
        \resumeItem{Achieved \textbf{Lean Six Sigma} certification and applied continuous improvement methodologies to increase engineering process efficiency and reduce waste.}
        \resumeItem{Mentored new hires via onboarding, pair programming, and code reviews, bolstering team knowledge and assisting in adoption of best engineering practices.}
        \resumeItem{Collaborated with Product Management and Research teams to refine features and release scalable solutions, serving as \textbf{Scrum Master} and technical lead for multiple project cycles.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}