\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience delivering high-quality \textbf{data analytics}, \textbf{reporting solutions}, and cloud-native applications. Proficient in \textbf{Python}, \textbf{SQL}, \textbf{Power BI}, and container orchestration technologies with strong background in \textbf{OLAP}, \textbf{ETL} frameworks, and \textbf{cloud platforms} including \textbf{AWS}, \textbf{Azure}, and \textbf{GCP}. Proven expertise in leading software development and deployment in Agile environments, optimizing performance, and leveraging \textbf{Generative AI} and \textbf{machine learning} for innovative BI and data workflows.  
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, SQL, JavaScript, C\# \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices, Power BI, SSRS \\
     \textbf{Frontend}: ReactJS, HTML/CSS, SASS, modern JavaScript (ES6+) \\
     \textbf{Databases}: SQL Server, PostgreSQL, MySQL, MongoDB, Redis \\
     \textbf{Cloud Platforms}: AWS, Azure, Google Cloud Platform (GCP), Azure AI Studio, Azure Cognitive Services \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Ansible, Git, Bitbucket, CI/CD pipelines \\
     \textbf{Analytics \& AI}: Power BI, Splunk, Dynatrace, Apigee, TensorFlow, PyTorch, Scikit-learn, Generative AI, OpenAI GPT \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, Unit Testing, TDD, JIRA, SonarQube, CheckMarx \\
     \textbf{Other}: OLAP, ETL, SQL Server Reporting Services (SSRS), Containerization, LLMs for NLP, RAG systems  
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and \textbf{SQL} validation scripts in Azure Data Notebooks to verify incoming operational data from fraud detection pipelines, improving data quality and compliance.}
        \resumeItem{Automated regression and functional testing with Java, Cucumber, and Selenium, enhancing reliability and reducing manual effort by 40\%.}
        \resumeItem{Built and maintained fraud monitoring workflows leveraging \textbf{large transactional data}, supporting rapid case creation and tracking of suspicious activities in compliance with internal policies.}
        \resumeItem{\textbf{Collaborated closely with cross-functional teams} following Agile methodologies to deliver high-quality releases aligned with business strategies and regulatory requirements.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Data Engineer}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements for \textbf{Azure Cognitive Services} with rigorous testing using \textbf{REST APIs} and \textbf{SDKs}, enhancing performance and stability for production environments.}
        \resumeItem{Streamlined containerized workflows and \textbf{code testing} using Python, Java, Postman, and Kusto, increasing observability and product reliability by 30\%.}
        \resumeItem{Led training, evaluation, and fine-tuning of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, improving response accuracy and reducing latency for data-driven AI applications.}
        \resumeItem{\textbf{Collaborated on technical design and implementation} for scalable AI platforms enabling next-generation LLM-based services, aligned with enterprise requirements.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Development Engineer Co-op}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly developed expertise in \textbf{Azure} technology stacks, \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, and \textbf{C++} to support production bug fixes and new feature delivery.}
        \resumeItem{Introduced \textbf{code quality and refactoring improvements}, increasing development velocity by 10-15\% and enhancing team collaboration and release reliability.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of interactive frontend application for automotive haptics using \textbf{ReactJS} and integrated backend APIs to deliver responsive UX aligned with client specifications.}
        \resumeItem{Designed and validated \textbf{haptic feedback} features on prototype hardware, ensuring compliance with safety and brand guidelines in realistic scenarios.}
        \resumeItem{Contributed to infotainment software using \textbf{Qt}, \textbf{WeCAN}, and \textbf{C++}, improving system responsiveness and reliability in a complex automotive HMI environment.}
        \resumeItem{Implemented fully automated \textbf{CI/CD pipelines} with Jenkins and Bitbucket, accelerating deployment and reducing integration issues for embedded software releases.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer II}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed \textbf{analytical models} and core platform components using Java, Python, C\#, and SQL, improving processing speed and accuracy by 40\%.}
        \resumeItem{Built a Python tool to optimize large model data formats, reducing file sizes tenfold and accelerating downstream damage calculations.}
        \resumeItem{Diagnosed and resolved complex production issues, including memory leaks, using systematic root-cause analysis and profiling tools.}
        \resumeItem{Applied \textbf{Lean Six Sigma} principles to streamline workflows, reduce defects, and improve operational efficiency within software development teams.}
        \resumeItem{Mentored new engineers and acted as \textbf{Scrum Master}, facilitating Agile ceremonies and leading a team to timely delivery of multiple releases.}
        \resumeItem{Collaborated closely with Product Management and Research to refine requirements and deliver scalable, high-quality software solutions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}