\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building end-to-end, cloud-native web applications and backend services, with strong expertise in \textbf{POS integration} and retail technologies. Skilled in \textbf{Java}, \textbf{Python}, and \textbf{automation frameworks}, with experience designing API workflows, developing troubleshooting tools, and implementing \textbf{monitoring systems} to improve distributed system performance. Proven track record delivering scalable solutions and leading cross-functional teams, with a focus on \textbf{technical product management} and driving quality in fast-paced environments.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Spring MVC, Node.js, RESTful APIs, Microservices Architecture, POS Integration \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, Data Factory, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Data Streaming}: Apache Kafka, Real-time Data Processing, Event-driven Architecture \\
     \textbf{Testing and QA}: JUnit, Cucumber, Selenium, Postman, TDD/BDD, Automated Testing, Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle, Automation Frameworks \\
     \textbf{Monitoring}: Developed tools for monitoring distributed system performance and troubleshooting
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and \textbf{SQL} validation scripts for data quality verification in complex pipelines, enhancing overall system integrity and reliability.}
        \resumeItem{Automated regression and functional testing by developing \textbf{Java}-based test suites using \textbf{Cucumber}, \textbf{Selenium}, and BDD practices, reducing manual effort and increasing feature stability.}
        \resumeItem{Built and maintained workflows monitoring transactional data to identify anomalies, improving detection accuracy and response times in mission-critical systems.}
        \resumeItem{\textbf{Collaborated closely with cross-functional teams} following Agile/Scrum, ensuring on-time delivery and high-quality system integration.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led quality improvements for \textbf{Azure Cognitive Services} by testing and validating new features via \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Azure AI Studio}, enhancing platform stability.}
        \resumeItem{Streamlined testing, database querying, and container workflows using \textbf{Jupyter}, \textbf{Postman}, \textbf{Java}, \textbf{Python}, and \textbf{C\#}, contributing to 30\% increased reliability.}
        \resumeItem{Pioneered experimentation and tuning of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, enabling accelerated benchmark-driven improvements for AI-enabled tools.}
        \resumeItem{Collaborated with engineering and product teams to validate scalable AI features, improving integration workflows for enterprise cognitive services.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained rapid proficiency in \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure}, enabling efficient development and independent feature ownership.}
        \resumeItem{Introduced improvements to code quality and refactoring guided by mentorship and online learning, increasing development velocity by 10-15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led design and integration of haptic feedback features for automotive infotainment, including requirements gathering and client communications aligning with product goals.}
        \resumeItem{Developed interactive frontend using React, integrating RESTful APIs delivering responsive user experiences for automotive design platforms.}
        \resumeItem{Conducted testing of haptics on prototype hardware, validating system behavior in controlled and field environments.}
        \resumeItem{Contributed to UI/UX workflows leveraging \textbf{Qt}, \textbf{Rhapsody}, \textbf{WeCAN}, and \textbf{C++}, improving responsiveness and system robustness.}
        \resumeItem{Implemented CI/CD pipelines using \textbf{Jenkins} and Bitbucket, automating build/test cycles to enhance software deployment efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed analytical models and core services using \textbf{Java}, \textbf{C\#}, \textbf{Python}, and \textbf{SQL}, improving computational performance by 40\%.}
        \resumeItem{Created Python-based tools for data format optimization, reducing large datasets from 2GB to 200MB and accelerating downstream processing.}
        \resumeItem{Diagnosed and fixed complex production memory leaks and performance bottlenecks to ensure system stability and scalability.}
        \resumeItem{Applied \textbf{Lean Six Sigma} methodologies to improve development workflows and reduce inefficiencies.}
        \resumeItem{Mentored new engineers and led a team of three while serving as \textbf{Scrum Master}, ensuring smooth agile delivery and stakeholder coordination.}
        \resumeItem{\textbf{Collaborated with Product Management to refine feature requirements} and developed scalable solutions aligned with business goals and customer needs.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}