\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building and debugging cloud-native web applications and backend services. Proficient in \textbf{Python}, \textbf{JavaScript}, and \textbf{C\#} for solving coding challenges and algorithmic problems leveraging strong understanding of \textbf{data structures} and \textbf{debugging workflows}. Experienced in evaluating software quality and performance, with proven collaboration skills in Agile teams. Looking to contribute expertise towards training, evaluating, and enhancing AI chatbot models while ensuring correctness and high-quality output.
    }}
  \end{itemize}
\vspace{-16pt}

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, JavaScript, Java, C++, C\#, SQL, HTML, Bash \\
     \textbf{Backend and Frameworks}: Node.js, Spring Boot, RESTful APIs, Microservices Architecture \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS, Azure, GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, Azure DevOps, CI/CD Pipelines \\
     \textbf{Data Structures \& Algorithms}: Proficient in problem-solving, debugging, and algorithm implementation \\
     \textbf{Testing and QA}: JUnit, Selenium, Cucumber, Postman, Test-Driven Development \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, JIRA
    }}
 \end{itemize}
\vspace{-16pt}

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and SQL validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, significantly improving data quality and overall system reliability.}
        \resumeItem{Automated regression and functional testing by developing \textbf{Java}-based test suites using Cucumber, Selenium, and BDD practices, reducing manual testing effort by 40\% and increasing feature reliability.}
        \resumeItem{Built and maintained fraud monitoring workflows leveraging large-scale transactional datasets and third-party tools, enabling rapid detection and tracking of suspicious financial transactions.}
        \resumeItem{Collaborated with cross-functional teams using Agile/Scrum methodology to deliver high-quality, timely releases, focusing on performance and correctness of outputs.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements for \textbf{Azure Cognitive Services} by testing new features using \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Azure AI Studio}, identifying defects impacting model outputs.}
        \resumeItem{Streamlined testing, database analysis, and container-based workflows using \textbf{Python}, \textbf{Java}, \textbf{C\#}, \textbf{Jupyter}, \textbf{Postman}, and \textbf{Kusto}, enhancing product reliability by 30\%.}
        \resumeItem{Led training and evaluation of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, systematically benchmarking and tuning configurations to improve AI model correctness and performance.}
        \resumeItem{Partnered with engineering and product teams to validate and optimize next-generation AI capabilities for scalable, production-ready cognitive services.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained proficiency in \textbf{C\#}, \textbf{C++}, \textbf{Azure}, \textbf{XSLT}, and \textbf{XML} within 1 month to take ownership of sprint user stories and production bug fixes.}
        \resumeItem{Introduced code-quality and refactoring improvements through Pluralsight courses and mentorship, enhancing team coding standards and velocity.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of interactive frontend features using \textbf{React} and integrated backend APIs to deliver responsive user experience on Cadillac design platform.}
        \resumeItem{Implemented UI and interaction workflows in \textbf{C++} and \textbf{Qt} in a complex automotive HMI environment, improving system responsiveness and reliability.}
        \resumeItem{Developed CI/CD pipelines automating builds and testing using \textbf{Jenkins}, reducing integration issues and deployment times.}
        \resumeItem{Designed and tested haptics functionality on prototype hardware, validating vibration patterns for user feedback accuracy.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed analytical models and core components using \textbf{Python}, \textbf{Java}, \textbf{C\#}, \textbf{C++}, and \textbf{SQL} with strong focus on data structures and algorithms, improving performance by 40\%.}
        \resumeItem{Built a \textbf{Python}-based data conversion tool reducing large model data sizes by 90\%, enhancing load efficiency for downstream processing.}
        \resumeItem{Diagnosed and resolved critical production issues via systematic debugging, profiling, and root-cause analysis techniques.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process improvements to engineering workflows.}
        \resumeItem{Mentored new hires through induction sessions, pair programming, and code reviews, strengthening engineering culture.}
        \resumeItem{Collaborated with Product and Research teams, leading Scrum in Agile environment to deliver scalable, high-quality solutions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, increasing accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and followed SOLID principles, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Improved expense monitoring by integrating Amazon Textract for intelligent data extraction from receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated user notifications by developing Python Lambda scripts extracting critical information and triggering SNS alerts, boosting user efficiency.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Contributed to Hurricane Fiona recovery simulation by developing core functionality in Java, enabling efficient disaster response planning.}
            \resumeItem{Validated restoration algorithms with JUnit test cases, ensuring high accuracy and reliability.}
            \resumeItem{Applied advanced data structures and algorithms to optimize power restoration routes, reducing recovery time by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}