\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Experienced \textbf{Senior Full Stack Engineer} with 5+ years of developing scalable, cloud-native applications with deep expertise in \textbf{Node.js}, \textbf{React}, and \textbf{Google Cloud Platform (GCP)}. Proficient in designing secure and efficient RESTful APIs, managing CI/CD pipelines, and implementing DevOps best practices. Adept at integrating front-end features with backend services, and committed to delivering high-quality, robust code in collaborative, fast-paced environments.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: JavaScript (ES6+), TypeScript, Java, Python, C++, C\#, SQL, Bash \\
     \textbf{Backend and Frameworks}: Node.js (Express.js), RESTful APIs, Microservices Architecture, Asynchronous Programming, PM2 Clustering \\
     \textbf{Frontend}: React (Hooks, State Management, Lifecycle), JavaScript, HTML/CSS, Component-driven Architecture \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: \textbf{Google Cloud Platform (GCP)} (Compute Engine, Cloud CDN, Identity Platform), AWS, Azure \\
     \textbf{DevOps and Tools}: BitBucket Pipelines, Docker, Kubernetes, Jenkins, Git, Terraform, CI/CD Pipelines \\
     \textbf{Security \& API Development}: OAuth 2.0, OpenID Connect, JWT, API Security Best Practices, XSS/CSRF Prevention, Rate Limiting \\
     \textbf{Testing and QA}: Jest, Mocha, Postman, TDD/BDD, Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Wipro Technologies (TD Bank)}}{\textbf{Oct 2024 -- Present}}
      {Toronto, Canada}{Software Engineer}
      \resumeItemListStart
        \resumeItem{Built and maintained robust backend services and secure RESTful APIs using \textbf{Node.js} and Express.js, enhancing transaction processing for financial applications.}
        \resumeItem{Implemented \textbf{asynchronous programming patterns} and utilized \textbf{PM2 clustering} for optimal performance and high availability of critical services.}
        \resumeItem{Designed and optimized SQL queries for large-scale transactional datasets, enabling efficient fraud monitoring workflows with integration to front-end platforms.}
        \resumeItem{Collaborated with cross-functional Agile teams to ensure high-quality releases and conducted code reviews following best practices for scalability and security.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{LTI Mindtree LTD (Microsoft)}}{\textbf{Dec 2023 -- Apr 2024}}
      {Calgary, Canada}{Senior Data Engineer}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Azure Cognitive Services} stability through rigorous testing of \textbf{REST APIs} and SDKs, contributing to improved real-time AI capabilities.}
        \resumeItem{Streamlined workflows using containerization and \textbf{DevOps} tools, achieving approximately 30\% improvement in reliability for AI service deployments.}
        \resumeItem{Collaborated in training and optimizing large language models, boosting AI performance while following cloud-native best practices.}
        \resumeItem{Contributed to API design and validation processes, ensuring compliance with security standards such as OAuth 2.0 and JWT token mechanisms.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{ESO}}{\textbf{Jan 2024 -- Apr 2024}}
      {Halifax, Canada}{Software Development Engineer Co-op}
      \resumeItemListStart
        \resumeItem{Developed and debugged backend components in \textbf{C\#} and integrated cloud services on \textbf{Azure}, gaining experience in secure API development and deployment.}
        \resumeItem{Improved team velocity by introducing best practices in code quality, automated testing, and CI/CD pipelines to meet sprint goals.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{People Tech Group Private Ltd.}}{\textbf{Jan 2022 -- Aug 2022}}
      {Hyderabad, India}{Software Engineer}
      \resumeItemListStart
        \resumeItem{Led frontend development of automotive infotainment platform using \textbf{React} with component-driven architecture, integrating with RESTful APIs for dynamic UI updates.}
        \resumeItem{Implemented \textbf{CI/CD pipelines} using \textbf{Jenkins} and \textbf{Bitbucket} for building and deploying automotive software, enhancing delivery efficiency and reliability.}
        \resumeItem{Developed backend services supporting integration with vehicle systems, applying asynchronous patterns and API security best practices including token validation.}
        \resumeItem{Collaborated with cross-functional teams to ensure frontend and backend synchronization, improving user experience and system stability.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Verisk Analytics}}{\textbf{Sep 2018 -- Jan 2022}}
      {Hyderabad, India}{Software Engineer II}
      \resumeItemListStart
        \resumeItem{Designed and implemented scalable backend components using \textbf{Java} and \textbf{Python}, improving performance of business-critical models by 40\%.}
        \resumeItem{Built a Python tool to convert and optimize large datasets, reducing load times and resource usage in production environments.}
        \resumeItem{Mentored engineers on \textbf{API development}, code reviews, and Agile methodologies, driving team adoption of best practices.}
        \resumeItem{Led Scrum teams and collaborated with product management to deliver features with secure, maintainable code adhering to REST API principles and versioning strategies.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Dalhousie University, Halifax, Canada}}{\textbf{Sep 2022 -- Apr 2024}}
      {Master of Applied Computer Science}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{GRIET, Hyderabad, India}}{\textbf{Aug 2015 -- May 2019}}
      {Bachelor of Technology in Computer Science and Engineering}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}