\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience designing and implementing \textbf{cloud-native} and \textbf{enterprise-level AI-driven systems}. Proficient in \textbf{Python}, \textbf{Java}, and \textbf{JavaScript} frameworks, with hands-on expertise in \textbf{Machine Learning}, \textbf{Deep Learning}, and \textbf{Natural Language Processing (NLP)} to build scalable, robust AI solutions. Experienced in delivering solutions leveraging \textbf{transformer models}, \textbf{prompt engineering}, and \textbf{RAG pipelines}. Strong background in developing scalable backend services and AI workflows, with effective collaboration in Agile teams within financial and enterprise industries.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, JavaScript, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, React, RESTful APIs, Microservices, Agentic Workflows \\
     \textbf{AI/ML}: Deep Learning (SGD, Backpropagation), Machine Learning (clustering, classification, regression, tree-based models), NLP (BERT, entity recognition, sentiment analysis), Generative AI, Transformer Models, RAG Pipelines, Prompt Engineering \\
     \textbf{Databases}: PostgreSQL, MongoDB, DynamoDB, Vector Databases, Redis \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3), Azure (OpenAI Services, AKS, Data Factory), GCP \\
     \textbf{DevOps and MLOps}: Docker, Kubernetes, Jenkins, GitHub Actions, Terraform, Observability and Monitoring Tools \\
     \textbf{Development Practices}: Agile/Scrum, TDD/BDD, CI/CD Pipelines, Code Reviews, System Design, Scalable Architectures
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Python}-based workflows and validation scripts processing large transactional datasets, integrating with cloud platforms and data services to support fraud detection initiatives with high reliability.}
        \resumeItem{Automated regression and UI testing by developing Java test suites with Cucumber and Selenium, improving feature stability and reducing manual testing effort by 40\%.}
        \resumeItem{Collaborated with cross-functional teams to build scalable, cloud-native data processing pipelines adhering to enterprise security and compliance standards.}
        \resumeItem{Optimized complex SQL queries and production workflows aligned with Agile/Scrum processes, facilitating high-quality, timely feature delivery.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Contributed to \textbf{Azure Cognitive Services} enhancements by testing and validating AI/ML features using SDKs, REST APIs, and Azure AI Studio, improving reliability and performance.}
        \resumeItem{Drove \textbf{OpenAI GPT model} training, evaluation, and optimization workflows on \textbf{Azure OpenAI}, improving inference latency and accuracy through fine-tuning and benchmark-driven parameter tuning.}
        \resumeItem{Implemented observability and monitoring solutions for AI models and pipelines utilizing MLOps best practices, ensuring system stability and scalability under production workloads.}
        \resumeItem{Partnered with product and engineering teams to evaluate and deploy \textbf{Generative AI} solutions and \textbf{RAG pipelines} for enterprise AI services, driving innovation in NLP-powered systems.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Accelerated onboarding by mastering \textbf{C\#}, \textbf{C++}, \textbf{XSLT}, and \textbf{Azure} technologies to deliver independent ownership of sprint tasks and bug fixes.}
        \resumeItem{Introduced code quality and refactoring improvements, contributing agile principles and increasing development velocity by 10-15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{React}-based frontend with seamless backend API integration, delivering responsive UI for automotive design platforms while collaborating with cross-disciplinary teams.}
        \resumeItem{Developed and tested embedded software features for haptic feedback systems in automotive applications using \textbf{C++} and \textbf{Qt}, ensuring compliance with safety and UX standards.}
        \resumeItem{Established CI/CD pipelines with \textbf{Jenkins}, automating build and deployment processes which improved deployment efficiency and reduced integration errors.}
        \resumeItem{Worked on multi-layer automotive infotainment HMI development with \textbf{Qt}, \textbf{Rhapsody}, and vehicle communication protocols, enhancing system responsiveness and reliability.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented high-performance analytical models and backend components leveraging \textbf{Python}, \textbf{Java}, \textbf{C++}, and \textbf{SQL}, improving processing speeds by 40\%.}
        \resumeItem{Developed \textbf{Python}-based tool to convert model data into compressed binary formats, significantly reducing storage and processing times.}
        \resumeItem{Provided root cause analysis and performance tuning for complex production issues ensuring stability of large-scale analytics platforms.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification, applying process improvement methodologies to optimize software development lifecycle.}
        \resumeItem{Mentored junior engineers and led Scrum ceremonies as \textbf{Scrum Master}, fostering agile team culture and delivering business-critical releases.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}