\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience designing and maintaining \textbf{enterprise trading and compliance systems}. Skilled in \textbf{C\#}, \textbf{SQL}, \textbf{PowerShell}, and modern web frameworks, with strong expertise in developing and deploying cloud-native solutions on \textbf{Azure} platforms. Experienced in collaborating with portfolio managers, traders, and back-office users to solve complex business problems, improve workflows, and enhance system reliability. Proven track record delivering robust solutions with a focus on automation, operational support, and continuous improvement in fast-paced financial environments.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: C\#, SQL, PowerShell, Java, Python, JavaScript (Angular/Typescript), Bash, C++ \\
     \textbf{Backend and Frameworks}: .NET Core, Spring Boot, Node.js, RESTful APIs, Microservices Architecture \\
     \textbf{Frontend}: Angular, React, JavaScript, HTML/CSS \\
     \textbf{Databases}: MSSQL, PostgreSQL, MySQL, Oracle, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: Azure (DevOps, AKS, Data Factory, App Services), AWS (EC2, Lambda, S3) \\
     \textbf{DevOps and Tools}: Azure DevOps, Docker, Kubernetes, Jenkins, Git, CI/CD Pipelines, Terraform \\
     \textbf{Testing and QA}: JUnit, Selenium, Cucumber, Postman, Automated Testing, BDD/TDD \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, Continuous Improvement, System Design, Scalability Optimization
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in \textbf{Azure Data Notebooks} to verify and validate incoming transactional data, improving \textbf{data quality} and system integrity for fraud detection workflows.}
        \resumeItem{Automated regression and functional testing using Java, Cucumber, Selenium and BDD methodologies, enhancing testing efficiency by 40\% and reliability of compliance features.}
        \resumeItem{Maintained and optimized complex SQL queries and ETL workflows supporting risk and compliance systems, collaborating closely with business stakeholders to align with trading requirements.}
        \resumeItem{Collaborated with cross-functional teams in an Agile environment to drive continuous improvement in operational support and enhancements, ensuring smooth system uptime and business continuity.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led quality assurance and testing improvements for \textbf{Azure Cognitive Services} by validating new features, APIs, and SDKs, significantly improving system stability and performance.}
        \resumeItem{Streamlined automation workflows using Azure DevOps, \textbf{C\#}, Jupyter, and Postman, reducing manual intervention and boosting overall product observability.}
        \resumeItem{Pioneered fine-tuning of large language models on \textbf{Azure OpenAI}, improving real-time processing efficiency by 25\% and reducing response latency for cognitive services.}
        \resumeItem{Engaged collaboratively with engineering and product teams to refine and deploy scalable cloud-based AI capabilities integrated with enterprise applications.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Acquired in-depth knowledge of \textbf{Azure} cloud services, \textbf{C\#}, and \textbf{XSLT} to deliver production fixes and enhancements on a complex health information codebase.}
        \resumeItem{Drove improvements in code quality and refactoring practices, accelerating delivery velocity and system reliability by approximately 15\% through Agile team collaboration.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented interactive frontend automotive applications using React and \textbf{Typescript}, integrating with backend APIs to enhance user experience and compliance workflows.}
        \resumeItem{Developed and tested \textbf{haptic feedback} components and automotive infotainment UI using \textbf{C++}, \textbf{Qt}, and \textbf{PowerShell} automation for build and deployment pipelines.}
        \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins} and \textbf{Bitbucket}, automating software builds and tests, accelerating releases and reducing integration errors.}
        \resumeItem{Collaborated with cross-disciplinary teams to align development efforts with client safety standards and project delivery milestones.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Built core analytical models and backend components using \textbf{Java}, \textbf{C\#}, \textbf{SQL}, and \textbf{Python}, improving processing performance by 40\% for critical financial data products.}
        \resumeItem{Developed automated tools to convert and optimize large datasets for damage assessments, accelerating computations and enabling real-time data processing.}
        \resumeItem{Diagnosed and resolved production issues such as memory leaks and bottlenecks, increasing system reliability and uptime for mission-critical applications.}
        \resumeItem{Applied \textbf{Lean Six Sigma} methodologies to enhance software development workflows and foster continuous improvements.}
        \resumeItem{Led a team of engineers as \textbf{Scrum Master}, collaborating with product owners and stakeholders to deliver scalable technology solutions aligned with business goals.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}