\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building scalable, cloud-native backend systems and APIs with a strong focus on \textbf{Python}, distributed systems, and \textbf{AWS services}, including Lambda, DynamoDB, and S3. Skilled in designing and maintaining \textbf{RESTful} and \textbf{GraphQL APIs}, implementing microservices, and deploying mission-critical features in enterprise environments. Proven ability to collaborate effectively in cross-functional remote teams and deliver scalable, reliable software solutions aligned with business goals.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Python (Flask, FastAPI), Spring Boot, Node.js, RESTful APIs, GraphQL, Microservices Architecture \\
     \textbf{Databases}: DynamoDB, PostgreSQL, MySQL, Oracle, MongoDB, Redis \\
     \textbf{Cloud Platforms}: AWS (Lambda, EC2, S3, ECS, DynamoDB, API Gateway, CloudFormation), Azure, GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Testing and QA}: Unit Testing, Integration Testing, Performance Testing, TDD/BDD, Postman, JUnit \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and SQL validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, improving data quality and system reliability.}
        \resumeItem{Automated regression and functional testing with Java-based Cucumber and Selenium suites, increasing feature stability and reliability.}
        \resumeItem{\textbf{Collaborated with cross-functional teams to design, build, and maintain scalable backend services supporting critical financial workflows, applying Agile/Scrum practices.}}
        \resumeItem{Optimized complex SQL queries, improving data retrieval and processing speeds critical for financial fraud monitoring systems.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led quality improvements for \textbf{Azure Cognitive Services} via rigorous testing of new features with \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Azure AI Studio}, contributing to scalability and reliability.}
        \resumeItem{Enhanced product observability and system performance by streamlining workflows using \textbf{Python}, \textbf{Jupyter}, and \textbf{Postman}, increasing reliability.}
        \resumeItem{Pioneered training, evaluation, and optimization of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, improving latency and throughput for AI workloads.}
        \resumeItem{\textbf{Collaborated on design discussions and sprint planning} with engineering and product teams to deliver scalable, cloud-native AI services.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Ramped up on \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, and \textbf{Azure} to independently own sprint user stories and production bug fixes.}
        \resumeItem{Introduced code-quality and refactoring improvements, increasing development velocity and maintainability by 10-15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of haptic feedback features for Cadillac vehicles, from concept through integration, ensuring alignment with UX and safety standards.}
        \resumeItem{Designed and implemented frontend interfaces using React, integrating backend APIs to deliver responsive user experiences.}
        \resumeItem{Contributed to infotainment UI and interaction workflows using \textbf{Qt} and \textbf{C++} to improve system responsiveness and reliability.}
        \resumeItem{Developed and maintained \textbf{CI/CD pipelines} using Jenkins and Bitbucket, automating builds, tests, and deployments, improving release efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Built scalable components using \textbf{Python}, Java, and SQL that improved performance of business-critical analytical models by 40\%.}
        \resumeItem{Developed a \textbf{Python}-based application to convert large model data into optimized binary formats, reducing file sizes by 90\% and accelerating processing times.}
        \resumeItem{Diagnosed and resolved complex performance bottlenecks, employing debugging, profiling, and root cause analysis techniques.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process improvements to increase development efficiency and reduce waste.}
        \resumeItem{Mentored junior engineers and led a team of three, serving as \textbf{Scrum Master} and facilitating Agile ceremonies and sprint planning.}
        \resumeItem{\textbf{Collaborated closely with Product Management and Research to design and deliver scalable backend solutions with a focus on reliability and performance.}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an \textbf{AWS Lambda}-based expense tracking solution integrating \textbf{DynamoDB}, \textbf{API Gateway}, and \textbf{S3} for serverless compute and storage.}
            \resumeItem{Enhanced data extraction by integrating Amazon Textract for intelligent receipt processing, reducing manual errors by 50\%.}
            \resumeItem{Automated user notifications via Python scripts in Lambda invoking SNS, boosting system responsiveness and user engagement.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona aftermath by developing restoration algorithms in Java, validated with JUnit to ensure high reliability.}
            \resumeItem{Applied advanced data structures and algorithms to optimize power restoration routing, reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}