\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software and Machine Learning Engineer} with 5+ years of experience building scalable, cloud-native backend services and \textbf{ML pipelines} for enterprise applications. Proficient in \textbf{Python}, \textbf{Java}, and \textbf{Scala}, with strong expertise in \textbf{building, deploying, and optimizing machine learning systems} on \textbf{AWS} and \textbf{Azure}. Skilled in \textbf{designing ML platforms} including feature stores, model registries, and real-time inference systems, with hands-on experience integrating ML models into user-facing applications. Demonstrated ability to deliver high-impact solutions supporting millions of users, with a focus on performance, scalability, and reliability. Proven collaborator and mentor experienced in Agile environments.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, Scala, C++, C\#, SQL, Bash \\
     \textbf{Machine Learning}: ML Pipeline Design, Feature Engineering, Model Training, Model Serving, Embedding-based Retrieval, Model Experimentation, A/B Testing \\
     \textbf{Frameworks \& Tools}: Apache Spark, Databricks, Airflow, AWS Sagemaker, OpenAI API, Anthropic, Terraform \\
     \textbf{Backend \& API}: RESTful APIs, gRPC, Microservices Architecture, Node.js, Spring Boot \\
     \textbf{Cloud Platforms}: AWS (ECS, EKS, Lambda, SQS, ElastiCache), Azure (Data Factory, AKS), GCP \\
     \textbf{Databases}: PostgreSQL, MongoDB, Redis, DynamoDB \\
     \textbf{DevOps}: Docker, Kubernetes, Jenkins, Git, CI/CD, Terraform, Monitoring with Datadog and CloudWatch \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, Performance Tuning
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and \textbf{SQL} validation scripts in Azure Data Notebooks to verify and ensure \textbf{data accuracy, integrity, and quality} from fraud detection pipelines, improving system reliability.}
        \resumeItem{Automated regression and functional testing by developing \textbf{Java}-based test suites using Cucumber and Selenium, reducing manual testing by 40\% and enhancing feature stability.}
        \resumeItem{Built and maintained \textbf{data pipelines} for large-scale transaction monitoring, collaborating closely with cross-functional teams following Agile methodologies to deliver reliable fraud detection workflows.}
        \resumeItem{Optimized complex SQL queries and participated in code reviews to improve \textbf{performance, scalability, and maintainability} of backend services supporting financial fraud detection.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements in \textbf{Azure Cognitive Services} by testing features using \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Azure AI Studio}, identifying and resolving critical defects to enhance stability and performance.}
        \resumeItem{Streamlined code testing and data processing workflows using \textbf{Jupyter}, \textbf{Postman}, \textbf{Java}, \textbf{Python}, and \textbf{Kusto}, improving product reliability and observability.}
        \resumeItem{Led training, evaluation, and optimization of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, improving key metrics by 25\% and reducing latency for \textbf{real-time AI workloads}.}
        \resumeItem{Collaborated across engineering and product teams to integrate \textbf{LLM capabilities} into scalable, production-ready \textbf{Azure AI} services, enhancing enterprise cognitive solutions.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly acquired expertise in \textbf{Azure} cloud services and \textbf{C\#}, contributing to backend development and resolving production issues in a complex software environment.}
        \resumeItem{Introduced code-quality improvements through mentorship and \textbf{refactoring}, accelerating development velocity and improving maintainability of core software components.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led requirement analysis and integration for haptic feedback systems in automotive applications, ensuring alignment with safety standards and client specifications.}
        \resumeItem{Developed an interactive \textbf{React} frontend application with seamless integration to backend APIs, improving user experience and visualizing complex automotive configurations.}
        \resumeItem{Designed and validated \textbf{prototype hardware haptics}, testing vibration patterns and timing for in-car usage scenarios, improving system reliability.}
        \resumeItem{Contributed to infotainment UI workflows using \textbf{Qt} and \textbf{C++} in a resource-constrained HMI environment, increasing responsiveness and fault tolerance.}
        \resumeItem{Automated automotive CI/CD pipelines using \textbf{Jenkins} and Bitbucket, reducing integration issues and speeding up deployment cycles.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed scalable analytical models and core components using \textbf{Java}, \textbf{Python}, \textbf{SQL}, and \textbf{algorithms}, achieving 40\% performance improvements across key products.}
        \resumeItem{Created a \textbf{Python}-based tool to compress large model datasets, reducing file size by 90\% and improving load and processing times for downstream computations.}
        \resumeItem{Conducted root-cause analysis and optimization of production applications, troubleshooting memory leaks and performance bottlenecks to enhance system reliability.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied continuous process improvements to accelerate development cycles and reduce waste.}
        \resumeItem{Mentored engineers, fostering adoption of \textbf{best practices} in coding, testing, and deployment; served as \textbf{Scrum Master} leading Agile delivery for multiple releases.}
        \resumeItem{Collaborated closely with Product and Research teams to define scalable, high-performance solutions that met evolving business requirements.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}