\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Data Engineer} and \textbf{Full-Stack Software Engineer} with 5+ years of experience designing and developing scalable data solutions and pipelines, including deep exposure to cloud-native architectures on \textbf{Azure}, with focus on \textbf{Microsoft Fabric}, \textbf{Delta Lake}, and \textbf{MSSQL}. Skilled in building and maintaining \textbf{dataflows}, \textbf{lakehouses}, and integrating complex data from \textbf{ERP}, \textbf{MES}, and operational systems. Proven ability to ensure data quality, lineage, and governance while collaborating across teams and following \textbf{Agile} processes. Experience includes developing event-driven integrations, RESTful APIs, and modernization of data workloads for manufacturing and enterprise environments.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture \\
     \textbf{Data Platforms}: \textbf{Microsoft Fabric (Pipelines, Lakehouse, OneLake, Dataflows)}, \textbf{Delta Lake}, Azure Data Factory, MSSQL, PostgreSQL, MySQL \\
     \textbf{Cloud Platforms}: Azure (Storage, DevOps, Data Factory, AKS), AWS, GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Integration Technologies}: APIs, REST, Webhooks, Event-driven Architecture, JIRA, Agile/Scrum \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, TDD/BDD, Automated Testing, Performance Testing \\
     \textbf{Development Practices}: Data Governance, Data Lineage, Scalability Optimization, System Design, Code Reviews
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Designed and implemented scalable \textbf{Azure Data Pipelines}, leveraging \textbf{SQL} and \textbf{Python} to validate and ingest large-scale transactional datasets with enhanced data quality and reliability.}
        \resumeItem{Automated testing workflows including regression and functional test suites using Java with Cucumber and Selenium, improving release cycle efficiency and minimizing defects.}
        \resumeItem{Developed and monitored dataflows integrating multiple source systems to support fraud detection, ensuring accuracy and integrity across complex datasets.}
        \resumeItem{Collaborated closely with cross-functional teams under \textbf{Agile} methodologies using \textbf{JIRA} to deliver high-impact features with optimized SQL queries and robust backend services.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led data quality and integration efforts for \textbf{Azure Cognitive Services} improvements using \textbf{REST APIs}, \textbf{SDKs}, and \textbf{Azure AI Studio}, enhancing pipeline robustness and service scalability.}
        \resumeItem{Utilized \textbf{Jupyter}, \textbf{Kusto queries}, and \textbf{Postman} for testing and optimizing code and containerized workflows, improving data observability and system reliability by 30\%.}
        \resumeItem{Drove advancements in AI model evaluation and optimization on \textbf{Azure OpenAI}, integrating event-driven patterns to streamline real-time data processing pipelines.}
        \resumeItem{Supported modernization of legacy systems by building scalable cloud-native data solutions and collaborating across product and engineering teams to ensure architecture alignment with enterprise standards.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Adapted quickly to a complex \textbf{Azure}-centric environment utilizing \textbf{C\#}, \textbf{XSLT}, and \textbf{XML}, taking ownership of sprint stories and delivering bug fixes independently.}
        \resumeItem{Introduced code-quality best practices and refactoring improvements that enhanced development velocity by 10-15\%, supporting more maintainable and reliable software releases.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed haptic feedback features for Cadillac vehicles including design, implementation, and validation, aligning with rigorous safety and UX standards.}
        \resumeItem{Created frontend interfaces using React integrated with backend APIs, enhancing automotive design platform responsiveness and user experience.}
        \resumeItem{Tested haptics on prototype hardware to validate production-ready vibration and timing patterns, supporting hardware-software integration.}
        \resumeItem{Contributed to infotainment system workflows using \textbf{Qt}, \textbf{WeCAN}, and \textbf{C++} in automotive HMI environments, increasing system reliability.}
        \resumeItem{Implemented and maintained automated CI/CD pipelines using Jenkins and Bitbucket, boosting deployment efficiency and reducing integration issues.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed and optimized analytical models using \textbf{Java}, \textbf{C\#}, \textbf{Python}, \textbf{SQL}, and advanced algorithms, achieving 40\% performance improvements on key models.}
        \resumeItem{Built Python tools to transform large datasets into highly compressed binary formats to accelerate data processing and consumption.}
        \resumeItem{Systematically diagnosed and fixed complex production issues, enhancing system stability and performance.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied continuous improvement practices to enhance engineering efficiency and quality.}
        \resumeItem{Mentored junior engineers and led multiple Agile release cycles as \textbf{Scrum Master}, fostering team productivity and collaboration.}
        \resumeItem{Collaborated extensively with product and research teams to design scalable data solutions and lead a team of 3 engineers for enterprise applications.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}