\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience in building end-to-end, cloud-native applications and developing \textbf{AI/ML} solutions. Proficient in \textbf{Python}, \textbf{Java}, \textbf{Spring Boot}, and cloud ML platforms including \textbf{AWS}, \textbf{Azure}, and \textbf{GCP}. Skilled at translating complex business problems into data-driven hypotheses, designing scalable data pipelines, and deploying production-ready AI models. Demonstrated ability to collaborate cross-functionally and deliver innovative solutions for enterprise clients including \textbf{TD Bank} and \textbf{Microsoft}, with a focus on \textbf{model optimization, data governance}, and autonomous agent frameworks.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{AI/ML and Frameworks}: Agentic AI, Generative AI (GANs, VAEs, Transformer models), LangChain, Hugging Face, OpenAI GPT, RAG, Context-aware Prompt Engineering \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, Bedrock, S3), Azure (DevOps, Data Factory, Azure AI Studio, AKS), GCP (Dataflow, AI Platform) \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines, MLOps Pipelines \\
     \textbf{Databases and Data Management}: PostgreSQL, MySQL, Oracle, MongoDB, Redis, DynamoDB, Vector Databases \\
     \textbf{Data Streaming and Processing}: Apache Kafka, Real-time Data Processing, Event-driven Architecture \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, TDD/BDD, Automated Testing, Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, Data Governance, Privacy, and Security \\
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and deployed Python and SQL data validation scripts on \textbf{Azure Data Notebooks} to ensure \textbf{data quality, accuracy}, and security for fraud detection pipelines, aligning with enterprise \textbf{data governance} standards.}
        \resumeItem{Automated regression and functional tests using \textbf{Java}, \textbf{Cucumber}, and \textbf{Selenium} with BDD method, reducing manual QA effort and increasing system robustness.}
        \resumeItem{Engineered scalable fraud monitoring workflows integrating large-scale transaction data and third-party financial analytics tools (such as OFSAA), enabling early \textbf{anomaly detection} and \textbf{real-time alerts} for suspicious activity.}
        \resumeItem{Collaborated in Agile teams to design optimized SQL queries, enhance pipelines, and support \textbf{model deployment} that complies with \textbf{privacy} and availability policies for financial services.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led R\&D efforts on training, evaluating, and optimizing \textbf{OpenAI GPT} and \textbf{Generative AI} models on \textbf{Azure OpenAI} platform, improving inference latency by 25\% for interactive applications using \textbf{context-aware prompt engineering} and \textbf{retrieval-augmented generation (RAG)} techniques.}
        \resumeItem{Enhanced \textbf{Azure Cognitive Services} with rigorous validation of new AI features, applying SDKs, REST APIs, and \textbf{Azure AI Studio}, improving stability and customer-facing reliability in production.}
        \resumeItem{Implemented MLOps pipelines for cloud-native deployment, enabling \textbf{model monitoring, version control}, and automated retraining on \textbf{Azure} and \textbf{GCP} platforms.}
        \resumeItem{Collaborated with product and engineering teams to validate enterprise-ready \textbf{AI models} and frameworks emphasizing \textbf{ethical guardrails}, bias mitigation, and sustainable AI use cases.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly acquired expertise in \textbf{XML/XSLT}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure} to independently own sprints, production bug fixes, and feature delivery within a complex enterprise system.}
        \resumeItem{Promoted clean code and refactoring standards through mentorship and training, accelerating delivery of key product milestones by 15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led the design and implementation of interactive haptic feedback features for Cadillac vehicles from concept through validation, collaborating closely with clients and cross-functional teams to align with safety and UX guidelines.}
        \resumeItem{Developed dynamic frontend applications using \textbf{React}, integrating backend APIs to visualize automotive configurations with high responsiveness and reliability.}
        \resumeItem{Built and tested embedded haptics modules leveraging \textbf{Qt} and \textbf{C++}, verifying real-world functionality on prototype hardware before deployment.}
        \resumeItem{Implemented CI/CD pipelines using \textbf{Jenkins} and \textbf{Bitbucket}, automating build and test processes, improving software delivery velocity and quality for infotainment systems.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Architected and implemented high-performance analytical models and core platform components using \textbf{Java}, \textbf{Python}, \textbf{C++}, and \textbf{SQL}, driving a 40\% overall improvement in model execution efficiency.}
        \resumeItem{Created a scalable \textbf{Python} application converting large modeling datasets into compact binary formats, reducing memory usage by 90\%, significantly enhancing data processing workflows.}
        \resumeItem{Diagnosed and resolved critical production issues including memory leaks and performance bottlenecks using advanced profiling and root cause analysis techniques.}
        \resumeItem{Attained \textbf{Lean Six Sigma} certification and led process improvements to optimize engineering workflows and reduce technical waste.}
        \resumeItem{Mentored new engineers and served as \textbf{Scrum Master} for cross-functional agile teams, driving collaboration and successful delivery of multiple software releases.}
        \resumeItem{Partnered with Product Management and Research to translate business requirements into scalable, data-driven solutions, leading a team of three in development and deployment efforts.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}