\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building end-to-end, cloud-native web applications and \textbf{microservices} architectures for enterprise and SaaS products. Skilled in \textbf{C\#/.NET Core}, Java, \textbf{React/TypeScript}, and cloud-native deployment on \textbf{Azure} and AWS with Kubernetes and Terraform. Experienced in designing and developing scalable backend services with REST APIs and \textbf{NoSQL} databases such as MongoDB and Redis. Proven ability in implementing \textbf{CI/CD pipelines} and infrastructure as code, while delivering quality software through comprehensive automated testing and agile development. Fluent in French and English with effective cross-cultural collaboration skills. 
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: C\#, Java, Python, SQL, TypeScript, JavaScript, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: ASP.NET Core, Spring Boot, Node.js, RESTful API, Microservices, Event-Driven Architecture (AMQP) \\
     \textbf{Frontend}: ReactJS, TypeScript, MaterialUI, ViteJS, Cypress, Tanstack \\
     \textbf{Databases}: MongoDB, ElasticSearch, Redis, PostgreSQL, MySQL, DynamoDB \\
     \textbf{Cloud Platforms}: Azure (DevOps, AKS, Data Factory), AWS (EC2, Lambda, S3), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Terraform, Argo CD, Azure DevOps, Jenkins, CI/CD Pipelines \\
     \textbf{Testing and QA}: Unit Testing, Functional Testing, Integration Testing, Cypress, JUnit, Cucumber, BDD/TDD \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Feature Flagging, A/B Testing, Canary Release (LaunchDarkly)
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in Azure Data Notebooks to verify incoming data from fraud detection microservices, significantly improving data quality and reliability in a \textbf{cloud-native} environment.}
        \resumeItem{Automated regression and functional testing by developing \textbf{Java}-based test suites using Cucumber, Selenium, and BDD practices, reducing manual testing effort by 40\% and enhancing feature reliability within Agile teams.}
        \resumeItem{Built and maintained fraud monitoring workflows leveraging large-scale transactional datasets and \textbf{NoSQL} data stores, enabling rapid detection, case creation, and tracking of suspicious financial transactions.}
        \resumeItem{Delivered multiple initiatives by designing and optimizing complex SQL queries, collaborating cross-functionally to support continuous integration and \textbf{CI/CD} deployment pipelines aligned with cloud infrastructure.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements for \textbf{Azure Cognitive Services} by rigorously testing features using \textbf{SDKs}, REST APIs, and Azure AI Studio, identifying and resolving critical defects to enhance performance and stability of microservices.}
        \resumeItem{Streamlined code testing, database analysis, and container workflows using \textbf{Jupyter}, Visual Studio, Java, Python, \textbf{C\#}, and Kusto queries, boosting product reliability and observability.}
        \resumeItem{Led training, evaluation, and optimization of \textbf{OpenAI GPT} models on Azure OpenAI, improving latency and throughput for real-time, scalable deployments with AI microservices.}
        \resumeItem{Collaborated with engineering and product teams to validate scalable, production-ready AI capabilities deployed on \textbf{cloud infrastructure}, promoting best practices for microservices development and integration.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly ramped up on \textbf{C\#}, \textbf{C++}, XML, and \textbf{Azure} technologies, gaining ownership of sprint user stories and contributing to backend services in a microservices architecture following Agile methodology.}
        \resumeItem{Introduced code-quality improvements and refactoring practices leveraging Pluralsight and mentorship programs, improving team delivery velocity for critical Medic1 software components.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of automotive haptic feedback features using \textbf{React} frontend integrated with backend microservices, collaborating closely with client teams to meet UX and safety requirements.}
        \resumeItem{Developed interactive frontend applications with ReactJS using modern component architecture, improving user experience and responsiveness aligning with client design standards.}
        \resumeItem{Designed and tested hardware-integrated haptic feedback functionality with real-time event-driven responses in prototype and production systems.}
        \resumeItem{Contributed to infotainment UI workflows using \textbf{Qt}, Rhapsody, and \textbf{C++}, improving responsiveness and reliability in embedded automotive software.}
        \resumeItem{Implemented CI/CD pipelines with Jenkins and Bitbucket for infotainment software, enabling smoother containerized deployments and reducing integration issues.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed next-gen analytical microservices and core components with \textbf{Java}, \textbf{C\#}, Python, and SQL, achieving 40\% performance improvement on key financial models.}
        \resumeItem{Built a Python application to efficiently convert large datasets into optimized binary formats, improving data loading times and supporting scalable damage assessment workflows.}
        \resumeItem{Troubleshot complex production issues including memory leaks and bottlenecks using profiling and root cause analysis in distributed microservices.}
        \resumeItem{Obtained \textbf{Lean Six Sigma} certification and applied process improvements to optimize Agile engineering workflows.}
        \resumeItem{Mentored new engineers through onboarding, pair programming, and code reviews, fostering strong engineering culture and collaboration.}
        \resumeItem{Collaborated with Product Management and Research to define scalable features, led a team of engineers, and served as \textbf{Scrum Master} ensuring timely delivery of releases.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {\textbf{Dalhousie University, Halifax, Canada}}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {\textbf{GRIET, Hyderabad, India}}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}