\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} and \textbf{Data Engineer} with 5+ years experience designing and optimizing \textbf{complex SQL queries}, \textbf{stored procedures}, and \textbf{ETL pipelines} using \textbf{MySQL} and \textbf{bash scripts} in Linux environments. Skilled in automating data validation and reporting solutions, with strong ability to analyze large datasets and ensure data integrity. Proven history of supporting business analytics and operational reporting for enterprise clients using relational databases and cloud services. Adept at cross-functional collaboration, process improvement, and delivering high-quality solutions in dynamic, fast-paced settings.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: SQL (MySQL, PostgreSQL), Python, Bash, Java, C++, C\#, PowerShell \\
     \textbf{Databases}: MySQL, PostgreSQL, Oracle, MSSQL, MongoDB, Redis \\
     \textbf{ETL Tools}: Bash scripting, Cron jobs, Linux/Unix shell scripting \\
     \textbf{Reporting \& Analytics}: SQL performance tuning, Data validation, MS Excel (Pivot Tables, VLOOKUP, Charts) \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3), Azure (Data Factory, DevOps) \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, CI/CD Pipelines \\
     \textbf{Frameworks}: Spring Boot, Node.js, RESTful APIs \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, JIRA \\
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and raw \textbf{MySQL SQL} validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, significantly improving data quality and system reliability.}
        \resumeItem{Automated functional and regression testing leveraging Java, Cucumber, and Selenium, reducing manual effort by 40\% and ensuring data consistency for reporting.}
        \resumeItem{Designed and optimized \textbf{complex SQL queries} and \textbf{stored procedures} for large-scale transactional datasets to support business reporting and operational monitoring.}
        \resumeItem{Collaborated within Agile teams to deliver high-impact initiatives focused on data integrity, query optimization, and reporting accuracy.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Data Engineer}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Developed and optimized ETL workflows using \textbf{bash scripts} and Linux shell scripting to automate data extraction, transformation, and loading tasks between transactional and reporting systems.}
        \resumeItem{Performed root cause analysis and remediation of data anomalies to maintain accuracy and integrity in enterprise reporting databases.}
        \resumeItem{Streamlined database query analysis and performance tuning using \textbf{SQL explain plans} to reduce slow query times and improve system responsiveness.}
        \resumeItem{Collaborated across engineering and product teams to design and implement data validation frameworks and ongoing monitoring solutions for complex datasets.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Development Engineer Co-op}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Enhanced backend services using \textbf{C\#} and \textbf{Azure} cloud technologies, taking ownership of production bug fixes and sprint user stories.}
        \resumeItem{Introduced improvements in code quality and deployment process contributing to smoother release cycles and higher team development velocity.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development and integration of automotive haptic feedback features including requirements analysis, implementation, and client engagement to align with safety and UX standards.}
        \resumeItem{Designed and developed React-based frontend applications integrating backend APIs to deliver responsive automotive infotainment experiences.}
        \resumeItem{Implemented CI/CD pipelines using Jenkins and Bitbucket, automating builds and tests to streamline deployment and reduce integration issues.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer II}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed analytical data models and core software components using \textbf{Java}, \textbf{Python}, and \textbf{SQL}, achieving significant performance improvements for business-critical applications.}
        \resumeItem{Built Python-based tools for efficient data format conversion, reducing large data file sizes and improving processing speed for downstream analytics.}
        \resumeItem{Diagnosed and resolved performance bottlenecks and memory leaks using profiling and root-cause analysis, enhancing application stability.}
        \resumeItem{Applied \textbf{Lean Six Sigma} methodologies to optimize engineering workflows, improving delivery efficiency and quality.}
        \resumeItem{Mentored new engineers and led Scrum teams, facilitating Agile practices and improving communication across departments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}