\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} and \textbf{Performance Engineer} with 5+ years of experience in building and optimizing end-to-end, cloud-native applications and backend services. Skilled in \textbf{Java/Spring Boot}, \textbf{Python}, \textbf{MySQL}, and \textbf{performance testing tools} such as \textbf{JMeter}. Strong background in analyzing performance bottlenecks, root cause analysis through profiling tools, and ensuring \textbf{scalability} and \textbf{high reliability} for distributed systems deployed on \textbf{AWS} and Linux environments. Proven success delivering high-impact projects at \textbf{TD Bank}, \textbf{Microsoft}, and other global organizations, with a focus on \textbf{performance engineering}, mentoring peers, and collaborating across teams to enhance product quality.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, SQL, Bash, Shell Scripting, C++, C\# \\
     \textbf{Performance Tools}: JMeter, LoadRunner (familiar), YourKit, Profiling and Benchmarking \\
     \textbf{Backend and Frameworks}: Spring Boot, Microservices, RESTful APIs, Node.js \\
     \textbf{Databases}: MySQL, PostgreSQL, Oracle, MongoDB, Redis, DynamoDB, Redshift (basic knowledge) \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure, Linux \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, CI/CD Pipelines \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Performance Optimization, JIRA \\
     \textbf{Other}: Distributed Computing Systems, Containerization, Monitoring and Automation Tools
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and automated \textbf{performance monitoring} and validation scripts in Python and SQL within Azure Data Notebooks to verify large-scale transactional data, improving data quality and system reliability.}
        \resumeItem{Automated regression and functional testing by creating \textbf{Java}-based test suites using Cucumber and Selenium following \textbf{BDD}, enhancing feature reliability and reducing manual effort by 40\%.}
        \resumeItem{Designed and optimized complex SQL queries for \textbf{performance benchmarking} of fraud monitoring workflows, enabling rapid detection and tracking of suspicious financial transactions.}
        \resumeItem{Collaborated cross-functionally following Agile/Scrum, ensuring timely delivery of high-quality releases with a focus on \textbf{scalability} and \textbf{system performance}.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove \textbf{performance testing and benchmarking} for \textbf{Azure Cognitive Services} by rigorously testing new features through SDKs, REST APIs, and Azure AI Studio, identifying and resolving critical defects.}
        \resumeItem{Streamlined testing and monitoring pipelines using Jupyter, Postman, and containerized workflows leveraging \textbf{Python}, \textbf{Java}, and \textbf{Kusto} queries to improve product reliability and observability by 30\%.}
        \resumeItem{Led training, evaluation, and systematic \textbf{performance tuning} of OpenAI GPT models on Azure OpenAI, achieving a 25\% improvement in latency and throughput for real-time workloads.}
        \resumeItem{Collaborated with product and engineering teams to ensure \textbf{production readiness} and scalability of next-generation cognitive and LLM-based services.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained proficiency in \textbf{Azure} cloud services and technologies including XSLT, XML, C\#, and C++ while supporting sprint user stories and production bug fixes independently.}
        \resumeItem{Introduced code quality and refactoring improvements via mentorship and Pluralsight courses, increasing development velocity by 10--15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development and integration of new haptic feedback features for Cadillac vehicles, including requirements analysis, implementation, and client alignment based on UX and safety guidelines.}
        \resumeItem{Developed React-based interactive frontend applications integrated with backend APIs to deliver responsive user experience and automotive configuration visualization.}
        \resumeItem{Designed and tested haptics functionality on prototype hardware, validating system performance in realistic driving scenarios.}
        \resumeItem{Contributed to automotive infotainment UI workflows using Qt, Rhapsody, WeCAN, and C++, focusing on responsiveness and reliability in performance-critical environments.}
        \resumeItem{Implemented CI/CD pipelines using Jenkins, SourceTree, and Bitbucket, optimizing build and test automation for software releases and reducing integration bottlenecks.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Implemented and optimized next-generation analytical models in Java, C\#, Python, and C++ resulting in 40\% performance improvements across business-critical systems.}
        \resumeItem{Built Python tools to convert large-scale model data into optimized binary formats reducing file sizes by 90\%, greatly improving load times and processing efficiency.}
        \resumeItem{Performed systematic \textbf{performance bottleneck analysis} and \textbf{root cause investigation} using profiling and debugging tools to resolve critical production issues, including memory leaks.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process improvement techniques to increase development workflow efficiency and reduce waste.}
        \resumeItem{Mentored new hires on best practices, pair programming, and peer reviews, elevating team skill levels and accelerating onboarding processes.}
        \resumeItem{Collaborated closely with Product Management and Research to define features and deliver scalable, high-performance solutions while serving as \textbf{Scrum Master} and leading a team of three engineers.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}