\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building scalable, real-time web applications and backend services. Proficient in strong \textbf{backend development} with \textbf{Node.js} and \textbf{TypeScript}, designing high-throughput messaging systems and handling large, real-time datasets. Skilled in building multiplayer/team-based product features with seamless data synchronization across devices. Experienced working with cloud platforms, distributed infrastructure, and \textbf{AI-powered} communication features. Proven success delivering robust, scalable systems with a customer-focused approach at enterprises including \textbf{TD Bank}, \textbf{Microsoft}, and startup environments.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: TypeScript, JavaScript, Java, Python, C++, C\#, SQL, Bash \\
     \textbf{Backend and Frameworks}: Node.js, Express.js, Spring Boot, RESTful APIs, Microservices, Event-driven Architecture \\
     \textbf{Frontend}: React, HTML/CSS, JavaScript \\
     \textbf{Databases}: MongoDB, PostgreSQL, Redis, DynamoDB, MySQL \\
     \textbf{Cloud Platforms}: AWS (Lambda, EC2, S3, DynamoDB), Azure, GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, Terraform, CI/CD Pipelines \\
     \textbf{Messaging \& Real-Time}: Apache Kafka, WebSocket, Real-time Data Processing, Distributed Systems \\
     \textbf{AI and ML Integration}: Azure Cognitive Services, OpenAI GPT, Azure OpenAI Studio \\
     \textbf{Development Practices}: Agile/Scrum, TDD, BDD, System Design, Scalability Optimization
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in Azure Data Notebooks to validate and improve the quality of large-scale transactional data, ensuring reliable inputs for fraud detection systems.}
        \resumeItem{Automated regression and functional testing via Java-based test suites following BDD using Cucumber and Selenium, enhancing feature reliability by 40\%.}
        \resumeItem{Engineered backend workflows to process high-throughput financial data streams, facilitating rapid fraud detection, case creation, and transaction monitoring across complex datasets.}
        \resumeItem{Collaborated within Agile teams to optimize SQL queries and backend services for performance and scalability supporting real-time data processing and monitoring.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led testing and quality improvements of \textbf{Azure Cognitive Services} by extensive use of \textbf{SDKs}, \textbf{REST APIs}, and Azure AI Studio, addressing defects to improve service stability and throughput for AI-powered communication systems.}
        \resumeItem{Optimized workflows using \textbf{Jupyter}, \textbf{Postman}, \textbf{Visual Studio}, and \textbf{Kusto} to analyze large real-time datasets, boosting product reliability and observability by 30\%.}
        \resumeItem{Pioneered training and benchmarking of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, improving latency and accuracy for real-time AI-powered messaging and conversational workloads.}
        \resumeItem{Coordinated with cross-functional teams to validate scalable AI and cognitive service features for enterprise communication applications.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Adapted rapidly to complex technology stacks including \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure} to independently own sprint deliverables and fixes.}
        \resumeItem{Introduced code quality improvements and refactoring aided by Pluralsight training and mentorship, increasing team productivity and delivery quality by 10–15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led full lifecycle development of haptic feedback features for Cadillac vehicles, collaborating closely with UX and safety teams to align product behavior with brand requirements.}
        \resumeItem{Built a highly interactive frontend for Cadillac’s design platform using React with modern component architecture, delivering responsive UI integrated with backend APIs.}
        \resumeItem{Developed and validated \textbf{haptics} on prototype hardware, ensuring vibration accuracy and timing aligned with real driving scenarios.}
        \resumeItem{Contributed to infotainment UI workflows using \textbf{Qt}, \textbf{Rhapsody}, \textbf{WeCAN}, and \textbf{C++}, enhancing system responsiveness and stability.}
        \resumeItem{Automated build and deployment pipelines with \textbf{Jenkins} and \textbf{Bitbucket}, reducing integration issues across teams.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed next-gen analytical and backend services using \textbf{Java}, \textbf{C\#}, \textbf{Python}, and \textbf{SQL}, improving processing throughput by 40\%.}
        \resumeItem{Built a Python tool to optimize large model data into compressed binary formats, reducing data load times and enhancing scalability of downstream computations.}
        \resumeItem{Resolved complex memory and performance issues with systematic debugging on production distributed systems, maintaining high reliability.}
        \resumeItem{Applied \textbf{Lean Six Sigma} process improvements, accelerating workflows and improving engineering efficiency.}
        \resumeItem{Mentored peers and led engineering teams as \textbf{Scrum Master}, driving Agile delivery of scalable backend solutions.}
        \resumeItem{Collaborated closely with Product teams to design scalable, high-throughput distributed systems handling large datasets and messaging workflows.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}