\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Software Engineer} with 5+ years of experience in \textbf{Python-based development}, automated testing, and backend services for financial and enterprise organizations. Skilled in designing scalable and secure software architectures, performing unit testing, and supporting complex applications in regulated environments. Experienced in working with \textbf{Linux systems}, networking fundamentals, and Agile methodologies. Proven ability to collaborate across teams and deliver high-quality, production-ready cybersecurity and business solutions.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Python Scripting, Spring Boot, Microservices, RESTful APIs \\
     \textbf{Operating Systems}: Linux, Windows \\
     \textbf{Networking}: TCP/IP, HTTP, Network Protocols, Security Concepts \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, Data Factory, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Testing and QA}: Unit Testing, TDD, BDD, JUnit, Cucumber, Selenium, Postman \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle \\
     \textbf{Cybersecurity}: Application Security, Automation, Secure Coding Practices
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Designed and implemented automated \textbf{Python}-based scripts and validation workflows in Azure Data Notebooks to support cybersecurity fraud detection pipelines, improving data integrity and operational efficiency.}
        \resumeItem{Performed extensive \textbf{unit testing} and regression automation using Java and BDD frameworks such as Cucumber and Selenium to enhance the reliability of security applications.}
        \resumeItem{Collaborated cross-functionally to design scalable application architectures aligned with cybersecurity requirements and business needs, ensuring secure, performant production-ready solutions.}
        \resumeItem{Provided technical support and troubleshooting for other application teams, resolving critical issues and maintaining enterprise-scale system stability.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Enhanced quality and reliability of \textbf{Azure Cognitive Services} by developing and executing automated tests and \textbf{Python, C\#} code alongside REST API integrations, contributing to secure AI service delivery.}
        \resumeItem{Used \textbf{Jupyter notebooks}, scripting, and containerized environments for testing, validation, and optimization of large-scale AI/ML services with a focus on automation and security.}
        \resumeItem{Collaborated on design and development of scalable AI-based solutions in an \textbf{Agile} environment, ensuring alignment with enterprise-grade security and performance standards.}
        \resumeItem{Supported cross-team efforts by troubleshooting and resolving technical issues, improving product stability and user experience for enterprise customers.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained hands-on experience with \textbf{Azure} cloud services, \textbf{C++}, \textbf{C\#}, and XML technologies within a regulated software environment, contributing to secure and maintainable code delivery.}
        \resumeItem{Applied software engineering best practices including unit testing and documentation to ensure software quality and supportability in production environments.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed and tested critical automotive HMI features using \textbf{C++}, \textbf{Qt}, and related frameworks in a safety-critical environment, emphasizing reliability and compliance.}
        \resumeItem{Implemented CI/CD pipelines with Jenkins to automate builds, tests, and deployments, improving release quality and reducing integration issues.}
        \resumeItem{Designed and validated haptic feedback for enhanced user experience, working collaboratively with cross-functional teams to meet stringent quality and safety standards.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Built performant \textbf{Python}-based applications and core modules for enterprise analytical platforms, improving processing speed by 40\% and optimizing resource use.}
        \resumeItem{Developed scalable data transformation tools to support large datasets, enabling faster and more accurate computations for risk analytics.}
        \resumeItem{Applied systematic debugging and root cause analysis to resolve complex production issues, ensuring high availability and reliability of critical services.}
        \resumeItem{Led Agile teams as Scrum Master and mentored engineers on coding best practices, unit testing, and scalable system design aligned with enterprise standards.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}