\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience specializing in \textbf{application performance engineering}, distributed systems, and cloud-native application optimization. Skilled in \textbf{Python}, \textbf{shell scripting}, and performance testing tools such as \textbf{JMeter} and proficient in \textbf{Dynatrace} for monitoring and diagnostics in microservices and cloud environments. Experienced in automating testing frameworks and enhancing system reliability across large-scale distributed architectures. Proven ability to deliver high-quality solutions by integrating \textbf{performance analysis} and \textbf{automation} with strong problem-solving and analytical aptitude.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Shell, Java, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Performance Testing Tools}: JMeter, LoadRunner, Selenium, Cucumber \\
     \textbf{Application Performance Monitoring}: \textbf{Dynatrace}, Azure Monitor, Log Analytics \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, Microservices Architecture, RESTful APIs \\
     \textbf{Cloud Platforms}: AWS, Azure, GCP, Kubernetes, Docker, CI/CD Pipelines \\
     \textbf{DevOps and Automation}: Jenkins, GitHub Actions, Azure DevOps, Terraform, Test Automation \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MongoDB, Redis, DynamoDB \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization \\
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and Shell validation and automation scripts in Azure Data Notebooks to verify and optimize incoming data pipelines, enhancing data quality and \textbf{system performance monitoring}.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites with \textbf{Cucumber} and Selenium using \textbf{BDD}, improving testing coverage and reducing manual effort by 40\%.}
        \resumeItem{Built and maintained fraud monitoring workflows leveraging large-scale transactional datasets, integrating \textbf{performance monitoring} tools to detect anomalies and improve alerting accuracy.}
        \resumeItem{Collaborated with cross-functional teams to optimize SQL queries and system workflows, driving performance improvements in distributed data processing systems following Agile practices.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led \textbf{performance testing} and quality assurance efforts for \textbf{Azure Cognitive Services}, utilizing SDKs, REST APIs, and Azure AI Studio to identify and resolve performance bottlenecks.}
        \resumeItem{Streamlined code testing and observability workflows using Jupyter, Postman, and Visual Studio with a focus on automation and \textbf{scripting} in \textbf{Python} and C\#, increasing reliability by 30\%.}
        \resumeItem{Optimized training and evaluation pipelines for \textbf{OpenAI GPT} models, employing systematic benchmarking to enhance runtime efficiency and reduce latencies in cloud environments.}
        \resumeItem{Collaborated with engineering teams to validate and scale \textbf{distributed microservices} in Azure AI, improving service responsiveness under load and cloud-native deployment practices.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly assimilated complex backend codebases using \textbf{C\#}, \textbf{C++}, and Azure cloud services, enabling efficient sprint delivery and bug fixes within a microservices architecture.}
        \resumeItem{Introduced automated testing and \textbf{performance validation} improvements through Pluralsight courses and mentoring, boosting overall development velocity and code quality by 10-15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of new haptic feedback features for Cadillac vehicles, including design, integration, and validation of system responsiveness under real-world conditions.}
        \resumeItem{Developed frontend React applications integrated with backend APIs and contributed to \textbf{microservices-based UI workflows}, ensuring high responsiveness and reliability in automotive infotainment systems.}
        \resumeItem{Conducted extensive \textbf{performance testing} of haptics functionality on prototype hardware to validate timing and vibration patterns before in-car deployment.}
        \resumeItem{Built and maintained CI/CD pipelines with Jenkins and Bitbucket, automating build, test, and deployment workflows for critical automotive software components.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and optimized analytical models and core components using Java, C\#, Python, and C++, achieving an average 40\% \textbf{performance improvement} across key business solutions.}
        \resumeItem{Developed a \textbf{Python}-based tool for converting large model data into compressed binary formats, reducing load times and processing overhead significantly.}
        \resumeItem{Diagnosed and resolved critical production memory leaks and performance issues using advanced debugging and profiling tools focused on scalability and reliability.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification to implement process improvement measures enhancing testing and development workflows.}
        \resumeItem{Led mentorship and onboarding efforts and served as \textbf{Scrum Master}, fostering Agile practices and continuous integration across engineering teams.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}