\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Machine Learning Engineer} and \textbf{Software Engineer} with 5+ years of experience in designing, building, and deploying scalable AI and software solutions. Skilled in developing and integrating \textbf{Large Language Models (LLMs)}, \textbf{Generative AI}, and cloud-native applications with expertise in \textbf{Python}, \textbf{Java}, \textbf{C\#}, and AI frameworks such as \textbf{PyTorch} and \textbf{TensorFlow}. Proven ability to collaborate across cross-functional teams, optimize performance, and deliver production-ready AI systems focusing on reliability, security, and cost-efficiency. Experience includes AI model evaluation, tuning, and integrating AI into enterprise customer-facing applications.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{AI/ML Frameworks}: PyTorch, TensorFlow, Hugging Face Transformers, OpenAI GPT APIs \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation), Azure (OpenAI, AI Studio, AKS), GCP \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, Azure DevOps, CI/CD Pipelines \\
     \textbf{Distributed Systems}: Scalable AI systems design, cloud-native deployment, performance optimization \\
     \textbf{Testing and QA}: Automated Testing, TDD/BDD, Performance Testing \\
     \textbf{Methodologies}: Agile/Scrum, Code Reviews, System Design, Security Best Practices
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in Azure Data Notebooks to verify and improve quality of incoming data from fraud detection pipelines, boosting system reliability in production environments.}
        \resumeItem{Automated regression and functional testing frameworks using Java, Cucumber, and Selenium with a focus on enhancing feature stability and reliability in complex enterprise systems.}
        \resumeItem{Built and maintained scalable fraud monitoring workflows leveraging large-scale datasets and integrated with third-party tools such as OFSAA to automate suspicious transaction detection and case management.}
        \resumeItem{Collaborated with cross-functional teams to optimize SQL queries, ensuring timely high-quality releases with strong adherence to Agile development and distributed system design principles.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led training, evaluation, and optimization of state-of-the-art \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, improving model performance by 25\% and significantly reducing latency in real-time AI workloads.}
        \resumeItem{Contributed extensively to \textbf{Azure Cognitive Services} AI enhancements by testing new SDK features and REST APIs, identifying critical defects to boost robustness and scalability of cloud-based AI platforms.}
        \resumeItem{Streamlined code testing and cloud infrastructure workflows using Jupyter, Postman, and Kusto queries, enhancing product observability and reliability across AI/ML services.}
        \resumeItem{Collaborated with multidisciplinary teams to integrate large-scale LLM-based solutions into enterprise products, focusing on evaluation, reasoning improvements, and AI production deployment challenges.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Quickly ramped up on complex codebases involving \textbf{C\#}, \textbf{C++}, and \textbf{Azure} cloud services, independently owning sprint user stories and contributing to reliable production fixes.}
        \resumeItem{Introduced code-quality and refactoring improvements through mentorship and focused learning, enhancing team velocity and reducing technical debt within the software development lifecycle.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led full software development lifecycle for new haptic feedback features in Cadillac vehicles, collaborating closely with client teams to align with UX, safety, and product requirements.}
        \resumeItem{Developed interactive frontend applications using React with robust backend integration, delivering seamless user experiences aligned with automotive design priorities.}
        \resumeItem{Contributed to UI and HMI workflows through development in Qt, Rhapsody, WeCAN, and C++, improving system reliability and responsiveness in embedded automotive environments.}
        \resumeItem{Implemented automated CI/CD pipelines leveraging Jenkins and Bitbucket, accelerating integration and deployment cycles of automotive infotainment software.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented core analytical models and components using Java, Python, and C++, achieving 40\% average performance improvement and robust scalable solutions in production.}
        \resumeItem{Developed Python applications to optimize binary data formats for large-scale model datasets, reducing file sizes and enhancing processing efficiency in cloud environments.}
        \resumeItem{Diagnosed and resolved critical production issues including memory leaks and bottlenecks through systematic debugging and performance profiling, enhancing system reliability.}
        \resumeItem{Applied \textbf{Lean Six Sigma} methodologies to streamline engineering processes and improve software delivery efficiency.}
        \resumeItem{Mentored junior engineers and led a team of three, serving as \textbf{Scrum Master}, driving Agile best practices and fostering collaboration.}
        \resumeItem{Worked closely with Product Management and Research teams to translate feature requirements into scalable, production-ready AI solutions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}