\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Accomplished \textbf{Frontend Engineer} with 5+ years of experience, specializing in building high-performance, accessible, and scalable web applications using \textbf{React} and \textbf{TypeScript}. Expertise in developing and maintaining \textbf{design systems}, reusable components, and optimizing frontend performance to enhance user experience. Proven success driving standards for accessibility, theming, and responsiveness, with strong collaboration skills and experience partnering with backend teams on API contracts and performance optimization. Experienced in enforcing best practices in frontend architecture and load-time reduction at scale.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: JavaScript, TypeScript, Java, Python, C++, C\#, SQL \\
     \textbf{Frontend}: React, Redux, HTML5, CSS3, SASS, Responsive Design, Accessibility (a11y), Design Systems, Theming \\
     \textbf{Backend and Frameworks}: Node.js, Express, Spring Boot, RESTful APIs, Microservices Architecture \\
     \textbf{Build Tooling}: Webpack, Babel, CI/CD Pipelines, Jenkins, Docker, Kubernetes \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS, Azure, GCP \\
     \textbf{DevOps and Tools}: Git, GitHub Actions, Azure DevOps, Terraform \\
     \textbf{Testing and QA}: Jest, React Testing Library, Selenium, Cucumber, TDD/BDD, Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, Documentation, JIRA
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented and maintained frontend components for fraud monitoring workflows with a focus on \textbf{performance optimization}, enhancing responsiveness and load times for large-scale datasets.}
        \resumeItem{Developed robust Python and SQL validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, significantly improving data quality and system reliability.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber, Selenium, and BDD practices, and contributed to writing clear \textbf{technical documentation} for test cases and feature behaviors.}
        \resumeItem{Collaborated with cross-functional teams in Agile environment to integrate backend APIs, ensuring \textbf{accessibility} and \textbf{responsive design} compliance across platforms.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements and performance enhancements for \textbf{Azure Cognitive Services} by rigorously testing frontend SDKs, REST APIs, and cloud AI features.}
        \resumeItem{Streamlined code testing, database analysis, and containerized workflows using Jupyter, Postman, Visual Studio, Java, Python, and C\#, boosting product reliability and observability.}
        \resumeItem{Led training and performance optimization of \textbf{OpenAI GPT} models on Azure OpenAI platform, contributing to reduced latency for real-time applications and better user experience.}
        \resumeItem{Partnered with engineering teams to validate APIs and performance benchmarks, promoting \textbf{best practices} in frontend-backend integration and \textbf{system scalability}.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained proficiency in \textbf{C\#}, \textbf{C++}, XSLT, and Azure environments while contributing to component development with emphasis on \textbf{code quality} and maintainability.}
        \resumeItem{Introduced \textbf{refactoring practices} and code quality improvements to increase development velocity and maintain frontend stability in complex projects.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed interactive frontend applications for Cadillac design platform using \textbf{React} with modular component architecture, ensuring \textbf{theming} consistency and \textbf{responsive UI} across devices.}
        \resumeItem{Collaborated with backend teams to integrate APIs supporting vehicle configuration workflows, focusing on rendering efficiency and performance optimizations.}
        \resumeItem{Led development of new haptic feedback features, aligning UX behavior with safety and brand guidelines through detailed client communication and testing.}
        \resumeItem{Implemented \textbf{CI/CD pipelines} with Jenkins, SourceTree, and Bitbucket automating builds and tests for infotainment components, improving deployment stability.}
        \resumeItem{Contributed to infotainment UI and interaction workflows using Qt, Rhapsody, WeCAN, and C++ in complex automotive HMI environments, enhancing responsiveness and system reliability.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed core analytical models and components using Java, C\#, Python, C++, and SQL, improving computation performance by 40\% and reducing load times significantly.}
        \resumeItem{Built Python applications converting large datasets into optimized binary formats, enhancing frontend data loading speeds and system responsiveness.}
        \resumeItem{Diagnosed and fixed complex production issues, including memory leaks and performance bottlenecks, improving system stability and rendering efficiency.}
        \resumeItem{Attained Lean Six Sigma certification and applied process improvements to engineering workflows, advocating for scalable and maintainable software practices.}
        \resumeItem{Mentored new engineers and led Agile Scrum processes, driving collaboration and documentation standards for design and implementation consistency.}
        \resumeItem{Collaborated closely with Product Management and research teams to optimize \textbf{system performance}, and served as Scrum Master for multiple successful releases.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using \textbf{React}, Bootstrap, and CSS, enhancing user engagement and satisfaction with responsive and accessible components.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}