\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} and \textbf{Data Engineer} with 5+ years of enterprise experience building backend services, \textbf{data-driven features}, and scalable APIs for cloud-native applications in Financial and SaaS domains. Proficient in \textbf{Python, Java,} and \textbf{C\#} for building robust services supporting \textbf{reporting, analytics, and data export}. Skilled in designing complex distributed systems with strong focus on \textbf{data modeling, transformation, and API integration} with BI tools like \textbf{Power BI} and \textbf{Looker}. Experienced working with cloud platforms including \textbf{AWS}, \textbf{Azure}, and \textbf{GCP}, leveraging streaming technologies such as \textbf{Kafka}, and following \textbf{Agile/Scrum} methodologies. Proven ability to mentor teams, optimize systems for scale and reliability, and drive innovation in data intelligence applications.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture, Data Engineering \\
     \textbf{Data \& Analytics}: Dimensional Data Modeling, Data Transformation, Data Visualization, ETL, Kafka, Pub/Sub, BigQuery \\
     \textbf{Databases}: MySQL, PostgreSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3), Azure (DevOps, Data Factory, AKS), GCP (BigQuery, Pub/Sub) \\
     \textbf{BI Integration}: REST APIs, JSON, CSV, Looker, Tableau, Power BI \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Testing}: JUnit, Cucumber, Postman, TDD/BDD \\
     \textbf{Methodologies}: Agile/Scrum, Code Reviews, System Design, Scalability, Mentorship
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{backend Python scripts} and \textbf{SQL} data validation workflows for fraud detection data pipelines in Azure, enhancing \textbf{data quality} and compliance with privacy standards.}
        \resumeItem{Automated regression and functional testing using Java with Cucumber and Selenium frameworks following \textbf{BDD} best practices, leading to a \textbf{40\% reduction} in manual testing efforts and boosting feature reliability.}
        \resumeItem{Collaborated in an \textbf{Agile team} to design and optimize \textbf{complex SQL queries} and backend components supporting fraud monitoring workflows with large transactional datasets.}
        \resumeItem{Contributed to system scalability by integrating and tuning \textbf{data export and reporting services}, supporting secure and performant delivery of insights.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Azure Cognitive Services} features by testing and validating using SDKs and \textbf{REST API} integration, ensuring high system stability and performance for AI workloads.}
        \resumeItem{Developed and optimized \textbf{data pipelines} and containerized workflows using Jupyter, Postman, and multiple programming languages (Java, Python, C\#), improving service observability and quality.}
        \resumeItem{Led training and performance tuning for \textbf{OpenAI GPT} models on Azure, improving responsiveness and reducing latency for real-time \textbf{AI-driven} applications.}
        \resumeItem{Partnered with \textbf{cross-functional teams} to build scalable cognitive AI services that integrate data-driven insights and intelligence features for enhanced user experience.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained proficiency in \textbf{Azure cloud} and \textbf{C\#} backend systems by managing code for complex \textbf{data transformation} workflows and production bug fixes.}
        \resumeItem{Introduced code quality standards and refactoring techniques, contributing to improved development velocity and reliability of product features aligned with sprint goals.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led design and integration of new haptic feedback features for automotive infotainment platforms, working closely with product and hardware teams to meet functional and safety specifications.}
        \resumeItem{Developed frontend applications with React, integrating backend \textbf{RESTful APIs} and enhancing interactive visualization of automotive configurations.}
        \resumeItem{Tested \textbf{hardware-haptic} interactions validating real-world responsiveness, ensuring reliability before production deployment.}
        \resumeItem{Built and optimized CI/CD pipelines using \textbf{Jenkins} and Bitbucket to automate deployment workflows, improving build efficiency and quality.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed next-generation analytical models and backend services using \textbf{Java}, \textbf{Python}, \textbf{SQL}, and \textbf{C\#}, achieving up to 40\% performance improvements in critical analytics systems.}
        \resumeItem{Built a \textbf{Python} application to convert large datasets into efficient binary formats, significantly reducing load times and facilitating scalable data processing workflows.}
        \resumeItem{Led root cause analysis and performance tuning initiatives to address memory leaks and bottlenecks, improving system scalability and fault tolerance.}
        \resumeItem{Mentored junior engineers and led \textbf{Scrum Master} duties to drive Agile delivery of data-driven features and backend services supporting reporting and insights.}
        \resumeItem{Collaborated closely with product and research teams to refine requirements and deliver features with strong emphasis on data quality, governance, and compliance.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}