\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years designing and delivering clean, testable, and well-documented backend and frontend solutions in cloud environments. Expertise includes \textbf{JavaScript}, \textbf{Node.js/Express}, and \textbf{MongoDB} alongside serverless computing on \textbf{AWS Lambda}. Proven ability to solve complex technical challenges in financial services and enterprise domains by writing scalable, maintainable code that meets high quality standards. Strong team player with advanced communication skills and a proactive approach to continuous learning and innovation.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: JavaScript, Java, Python, C++, C\#, SQL, Bash \\
     \textbf{Backend and Frameworks}: Node.js, Express, RESTful APIs, Microservices Architecture, Spring Boot \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS \\
     \textbf{Databases}: MongoDB, PostgreSQL, MySQL, Oracle, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: \textbf{AWS (Lambda, EC2, S3, CloudFormation, DynamoDB)}, Azure (DevOps, AKS), GCP \\
     \textbf{Serverless}: AWS Lambda, Azure Functions \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Testing and QA}: Jest, JUnit, Cucumber, Postman, TDD/BDD, Automated Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, improving data quality and system reliability.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber, Selenium, and BDD practices, reducing manual testing effort by 40\%.}
        \resumeItem{Built and maintained fraud monitoring workflows leveraging large-scale transactional datasets and third-party tools such as OFSAA, enabling rapid detection and tracking of suspicious financial transactions.}
        \resumeItem{\textbf{Collaborated with cross-functional teams to deliver clean, well-documented backend services adhering to Agile/Scrum methodologies, enhancing feature reliability and scalability.}}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements for \textbf{Azure Cognitive Services} by testing new features using SDKs, REST APIs, and Azure AI Studio, identifying and resolving critical defects.}
        \resumeItem{Streamlined code testing, database analysis, and container workflows using Jupyter, Postman, Visual Studio, Java, Python, C\#, and Kusto queries, boosting product reliability by 30\%.}
        \resumeItem{Pioneered \textbf{OpenAI GPT} model training and optimization on Azure, improving performance metrics by 25\% and reducing latency in real-time workloads.}
        \resumeItem{\textbf{Collaborated in scalable production-ready AI service development, aligning with best practices in cloud and serverless architectures in Azure environments.}}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Ramped up on XSLT, XML, C\#, C++, and Azure within the first month on a complex codebase, independently owning sprint stories and production bug fixes.}
        \resumeItem{Leveraged Pluralsight and mentorship to introduce code-quality and refactoring improvements, increasing development velocity by 10-15\%.}
        \resumeItem{\textbf{Applied problem-solving skills and proactive learning to contribute effectively in a remote, collaborative software development environment.}}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of new haptic feedback features for Cadillac vehicles including requirements analysis, implementation, and client communication to align UX and safety guidelines.}
        \resumeItem{Developed interactive frontend application for automotive design platform using React, integrating with RESTful backend APIs for responsive UX.}
        \resumeItem{Designed and tested haptics functionality on prototype hardware, validating vibration patterns in realistic scenarios.}
        \resumeItem{Contributed to infotainment UI workflows using Qt, Rhapsody, WeCAN, and C++ in a complex automotive HMI environment, improving system reliability.}
        \resumeItem{Implemented CI/CD pipelines using Jenkins, SourceTree, and Bitbucket, automating builds and tests to reduce deployment time and integration issues.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Implemented analytical models and core components using Java, C\#, Python, and SQL, delivering 40\% performance improvements across critical models.}
        \resumeItem{Built Python application to optimize large model data into binary formats, reducing file sizes and improving load times.}
        \resumeItem{Diagnosed and resolved complex production issues including memory leaks and bottlenecks via systematic debugging and root cause analysis.}
        \resumeItem{Earned Lean Six Sigma certification and applied process-improvement practices to streamline development workflows.}
        \resumeItem{Mentored new hires and led Agile Scrum ceremonies as Scrum Master, improving team productivity and collaboration.}
        \resumeItem{\textbf{Collaborated closely with Product Management and Research to deliver scalable, high-quality software solutions aligned with business goals.}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}