\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Software Engineer} and \textbf{Analytics Engineer} with 5+ years of experience developing scalable data solutions, advanced SQL transformations, and cloud-native applications. Adept at \textbf{data modeling}, building and optimizing \textbf{ETL/ELT pipelines}, and leveraging \textbf{Python}, \textbf{SQL}, and \textbf{dbt} frameworks for high-quality, reliable data products. Proven success collaborating cross-functionally with engineering, product, and analytics teams at leading organizations including \textbf{TD Bank}, \textbf{Microsoft}, and others. Passionate about driving business impact through data-driven insights and automation in cloud environments such as \textbf{AWS}, \textbf{Azure}, and \textbf{GCP}.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: SQL (Advanced), Python (Intermediate-Advanced), Java, C++, C\# \\
     \textbf{Data Engineering}: Data Modeling (Star, Snowflake schemas), ETL/ELT Pipelines, dbt, Airflow, Apache Kafka \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, DynamoDB), Azure (Data Factory, AKS), GCP \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Data Visualization}: Looker, Tableau, Superset, Python (Matplotlib, Plotly) \\
     \textbf{DevOps and Tools}: Git, GitHub Actions, CI/CD Pipelines, Docker, Kubernetes, Jenkins, Terraform \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, Clean Code, System Design, Scalability Optimization \\
     \textbf{Other}: Prompt Engineering and Optimization for LLMs (GPT)
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and \textbf{SQL} validation scripts in \textbf{Azure Data Notebooks} to verify incoming data from fraud detection and transactional pipelines, significantly improving \textbf{data quality}, reliability, and trustworthiness of downstream analytics.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber, Selenium, and BDD practices, reducing manual testing effort by 40\% and increasing feature reliability.}
        \resumeItem{Built and maintained fraud monitoring workflows handling large-scale financial datasets and enterprise tools such as OFSAA, enabling rapid detection, case management, and tracking of suspicious transactions.}
        \resumeItem{Collaborated in Agile/Scrum teams to design, optimize complex \textbf{SQL queries} and \textbf{data models}, contributing directly to timely delivery of high-impact, production-grade data solutions.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Improved quality and performance of \textbf{Azure Cognitive Services} features by extensive testing with \textbf{SDKs}, \textbf{REST APIs}, and cloud AI tools, ensuring high data fidelity and product stability.}
        \resumeItem{Streamlined workflows using \textbf{Jupyter}, \textbf{Postman}, \textbf{Visual Studio}, \textbf{Java}, \textbf{Python}, \textbf{C\#}, and \textbf{Kusto} for efficient data pipeline validation and monitoring.}
        \resumeItem{Led training, evaluation, and optimization of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, improving prompt engineering techniques and reducing latency for scalable, real-time workloads.}
        \resumeItem{Partnered with cross-functional teams to integrate \textbf{data science} and engineering insights, facilitating \textbf{scalable data products} and robust business-aligned data models powering AI services.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Acquired proficiency in \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure} cloud services to independently lead sprint deliverables and resolve production bugs efficiently.}
        \resumeItem{Introduced code-quality improvements and refactoring best practices enhancing development velocity by 10-15\% through mentorship and structured learning initiatives.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led full-cycle development of haptic feedback features for Cadillac vehicles, including data flow analysis, implementation, and collaborative alignment with UX and safety teams.}
        \resumeItem{Developed interactive React frontend integrated with backend APIs, improving user experience and enabling dynamic automotive configuration simulations.}
        \resumeItem{Validated haptics hardware performance through rigorous testing of vibration patterns and timing to ensure seamless production integration.}
        \resumeItem{Contributed to infotainment UI workflows using \textbf{Qt}, \textbf{Rhapsody}, \textbf{WeCAN}, and \textbf{C++}, enhancing reliability and responsiveness in complex automotive HMI systems.}
        \resumeItem{Established CI/CD pipelines with \textbf{Jenkins}, \textbf{SourceTree}, and \textbf{Bitbucket} for streamlined software delivery and automated integration testing across teams.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Implemented next-generation analytical data models and core components with \textbf{Java}, \textbf{C\#}, \textbf{Python}, \textbf{C++}, and \textbf{SQL}, achieving up to 40\% performance gains and enhanced data reliability.}
        \resumeItem{Built a \textbf{Python}-based tool to convert large model datasets into optimized binary formats, reducing storage by 90\% and significantly accelerating data processing.}
        \resumeItem{Diagnosed and resolved critical production issues including memory leaks and bottlenecks through systematic debugging and profiling, ensuring stable data operations.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification, applying process improvement techniques to increase team efficiency and reduce waste in software development.}
        \resumeItem{Mentored new engineers and facilitated knowledge transfer, strengthening team capabilities and accelerating onboarding processes.}
        \resumeItem{Collaborated closely with Product Management and Research teams, translating complex requirements into scalable, reliable data models and leading as \textbf{Scrum Master} in Agile environments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {\textbf{Dalhousie University, Halifax, Canada}}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {\textbf{GRIET, Hyderabad, India}}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}