\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience designing and developing scalable, cloud-native applications and backend services for large-scale enterprises. Skilled in \textbf{Java/Spring Boot}, \textbf{Python}, \textbf{C++}, and \textbf{React/JavaScript}, with expertise in distributed system architecture, RESTful APIs, and integrating relational and NoSQL databases including \textbf{PostgreSQL} and \textbf{MongoDB}. Experienced in collaborating closely with business stakeholders and engineering teams to deliver robust, secure, and high-performance solutions. Proficient with \textbf{Linux}, \textbf{Windows}, and \textbf{Mac OS} environments, automated testing, code reviews, and modern DevOps practices. Strong communicator and adaptive problem solver committed to delivering technology solutions aligned with business objectives.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, C++, C\#, Go (basic), SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices, Unit Testing, BDD \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS, Bootstrap \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Oracle, MSSQL, Redis \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3), Azure (DevOps, Data Factory, Azure OpenAI, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, CI/CD Pipelines, Datadog \\
     \textbf{Testing and QA}: JUnit, Cucumber, Selenium, Postman, Automated Testing, Performance Testing \\
     \textbf{Other}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, AI-assisted Coding Tools (GitHub Copilot, Cursor), Prompt Engineering
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Designed and developed backend services and data validation scripts using \textbf{Python} and \textbf{SQL} in Azure Data Notebooks, improving data quality and system reliability for fraud detection pipelines in a large-scale financial system.}
        \resumeItem{Automated functional and regression testing through \textbf{Java}-based test suites implementing \textbf{Cucumber}, \textbf{Selenium}, and BDD frameworks, increasing test coverage and reducing manual testing efforts by 40\%.}
        \resumeItem{Built and enhanced fraud monitoring workflows processing large transactional data sets, integrating various third-party tools and APIs to enable effective suspicious activity detection, case creation, and tracking.}
        \resumeItem{Collaborated closely with cross-functional product and engineering teams following \textbf{Agile} methodology, contributing to system design reviews, solution documentation, and timely delivery of high-quality software releases.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Data Engineer}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Developed and tested new features for \textbf{Azure Cognitive Services} leveraging \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Azure AI Studio} with focus on scalability and distributed system performance, ensuring alignment with business goals.}
        \resumeItem{Streamlined containerized batch workflows and cross-language code testing using \textbf{Jupyter}, \textbf{Postman}, \textbf{Visual Studio}, \textbf{Java}, \textbf{Python}, and \textbf{C\#}, improving observability and reliability by ~30\%.}
        \resumeItem{Pioneered training, benchmarking, and fine-tuning of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, achieving improved real-time inference performance while ensuring robust model validation and safety.}
        \resumeItem{Engaged with cross-functional teams for design validation and contributed to technical documentation and code reviews, driving development of production-ready AI services for enterprise use.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Development Engineer Co-op}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Quickly adapted to a complex technology stack involving \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure}, independently managing sprint backlog items and resolving production issues.}
        \resumeItem{Introduced code-quality improvements and refactoring practices aligned with best development standards, contributing to enhanced maintainability and faster delivery of \textbf{Medic1} application features.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development and integration of advanced haptic feedback features for Cadillac vehicles, utilizing \textbf{C++} and prototype hardware to ensure reliable and brand-compliant user experience.}
        \resumeItem{Developed responsive frontend using \textbf{React} and integrated backend APIs, aligning closely with design and engineering teams for enhanced product usability.}
        \resumeItem{Contributed to automotive infotainment UI workflows using \textbf{Qt}, \textbf{Rhapsody}, \textbf{WeCAN}, and C++ in a distributed software architecture environment, improving system robustness and responsiveness.}
        \resumeItem{Implemented CI/CD pipelines using \textbf{Jenkins} and \textbf{Bitbucket}, automating build and test processes for improved deployment reliability across engineering teams.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer II}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and developed high-performance analytical components and models using \textbf{Java}, \textbf{Python}, \textbf{C++}, and \textbf{SQL}, enhancing system scalability and reducing runtimes by 40\%.}
        \resumeItem{Created a \textbf{Python}-based binary conversion tool significantly optimizing large model data storage, decreasing file sizes and load times by over 80\%.}
        \resumeItem{Diagnosed and resolved critical production issues with memory leaks and performance using advanced debugging and profiling techniques.}
        \resumeItem{Applied \textbf{Lean Six Sigma} principles to improve engineering workflows, and acted as \textbf{Scrum Master}, leading a team of developers to deliver iterative releases successfully.}
        \resumeItem{Mentored junior engineers and collaborated with Product and Research teams to align technical solutions with evolving business objectives, ensuring detailed solution documentation and code review participation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}