\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building end-to-end, cloud-native web applications and backend services for financial services and enterprise organizations. Skilled in \textbf{Java/Spring Boot}, \textbf{Node.js/React}, \textbf{Python}, and \textbf{TypeScript}, with strong experience designing RESTful APIs, integrating relational and NoSQL databases, and robust deployment on \textbf{AWS} and \textbf{Azure} using containers and CI/CD pipelines. Proven ability to take end-to-end ownership of systems to ensure \textbf{reliability, scalability, and performance} in fast-paced, collaborative environments. Experienced mentor and proactive problem solver committed to delivering impactful, high-quality software.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, TypeScript, JavaScript, C++, C\#, SQL, Bash \\
     \textbf{Backend and Frameworks}: Node.js, Spring Boot, RESTful APIs, Microservices Architecture, Express.js \\
     \textbf{Frontend}: React, TypeScript, JavaScript, HTML/CSS \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, DynamoDB, API Gateway, SNS, ECS), Azure (DevOps, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Testing and QA}: Jest, JUnit, Cucumber, Selenium, Postman, Test-Driven Development (TDD/BDD) \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, significantly improving data quality and system \textbf{reliability and performance at scale}.}
        \resumeItem{Automated regression and functional testing with Java-based test suites using Cucumber, Selenium, and \textbf{BDD}, reducing manual testing effort by 40\% and ensuring high-quality feature releases.}
        \resumeItem{Built and maintained fraud monitoring workflows using large-scale transactional datasets and third-party tools such as OFSAA, enabling rapid detection and tracking of suspicious financial transactions.}
        \resumeItem{\textbf{Collaborated cross-functionally} with business and engineering teams following Agile methodologies to deliver reliable, \textbf{end-to-end features} aligned with customer needs.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements for \textbf{Azure Cognitive Services} through rigorous testing of SDKs, REST APIs, and Azure AI Studio, contributing to highly scalable and \textbf{resilient} AI services.}
        \resumeItem{Streamlined testing and observability of services using \textbf{Jupyter}, Postman, Java, Python, C\#, and Kusto queries, enhancing product stability by 30\%.}
        \resumeItem{Led \textbf{performance optimization} and tuning of OpenAI GPT models on Azure OpenAI, boosting key metrics by 25\% and supporting real-time deployment pipelines.}
        \resumeItem{Partnered with cross-functional teams to validate and deliver enterprise-ready \textbf{cloud-native AI} services emphasizing availability and scalability.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly ramped up on XSLT, XML, C\#, C++, and Azure cloud environment, enabling ownership of sprint user stories and production bug fixes with a focus on \textbf{code quality} and maintainability.}
        \resumeItem{Proactively introduced \textbf{code refactoring} and quality improvements through Pluralsight learning and mentorship, improving development velocity by 15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of new haptic feedback features for Cadillac vehicles, including requirements analysis, implementation, and collaboration with UX teams to align product behavior with client standards.}
        \resumeItem{Developed interactive frontend application using React with modern component architecture, integrating backend APIs and ensuring a responsive user experience.}
        \resumeItem{Designed and validated haptics functionality on prototype hardware in realistic driving scenarios before car integration, ensuring quality and safety.}
        \resumeItem{Contributed to infotainment UI workflows using Qt, Rhapsody, WeCAN, and C++, improving responsiveness and \textbf{system scalability} within automotive HMI software.}
        \resumeItem{Implemented CI/CD pipelines for automotive software using Jenkins, SourceTree, and Bitbucket, automating builds and reducing integration issues for complex infotainment components.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed high-performance analytical models and core components with Java, C\#, Python, C++, and SQL, improving business-critical model efficiency by 40\%.}
        \resumeItem{Built Python applications to convert large datasets into optimized binary formats, enhancing data processing speed and reducing load times by over 80\%.}
        \resumeItem{Diagnosed and resolved production memory leaks and performance bottlenecks, improving \textbf{system reliability} and uptime through in-depth root cause analysis.}
        \resumeItem{Earned Lean Six Sigma certification and applied process improvements to optimize engineering workflows and minimize waste.}
        \resumeItem{Mentored new engineers via inductions, pair programming, and reviews, accelerating onboarding and reinforcing \textbf{best practices} in a collaborative team environment.}
        \resumeItem{Partnered with Product and Research to refine feature requirements and deliver scalable solutions, while leading a team of three engineers as \textbf{Scrum Master} for multiple releases.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services, supporting \textbf{scalable and resilient} cloud infrastructure.}
            \resumeItem{Enhanced expense monitoring by integrating Amazon Textract for intelligent data extraction from receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated user notifications by developing Python Lambda scripts extracting critical info and triggering alerts via SNS, improving user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Contributed to a project simulating extensive power outages in Atlantic Canada after Hurricane Fiona, supporting efficient disaster response planning.}
            \resumeItem{Developed core functionality in Java and JUnit tests, ensuring reliability and accuracy in restoration route computations.}
            \resumeItem{Applied advanced data structures and algorithms to optimize power restoration routes, reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}