\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Software Engineer} with 5+ years of experience designing and implementing cloud-native, scalable backend services and infrastructure automation at enterprise scale. Skilled in \textbf{Python} software development, \textbf{Linux} environments, and \textbf{DevOps} practices with extensive experience in container orchestration (\textbf{Kubernetes}), \textbf{cloud platforms}, and automating infrastructure with code. Proven ability to work in high-pressure, mission-critical operational environments delivering reliable solutions leveraging open source technologies.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, C++, C\#, Bash, SQL, PowerShell \\
     \textbf{Infrastructure \& Cloud}: Linux, Kubernetes, OpenStack, Docker, Terraform, AWS, Azure, GCP \\
     \textbf{Networking \& Storage}: Linux Networking, Software Defined Storage, Cloud Networking Concepts \\
     \textbf{Backend \& Frameworks}: RESTful APIs, Spring Boot, Node.js, Microservices, DevSecOps \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, DynamoDB, Redis \\
     \textbf{DevOps \& Automation}: CI/CD Pipelines, Jenkins, Azure DevOps, GitHub Actions, Helm, Ansible, Containerization \\
     \textbf{Monitoring \& Testing}: Prometheus, Grafana, JUnit, Cucumber, Selenium, Automated Testing \\
     \textbf{Practices}: Agile, Scrum, Code Reviews, System Design, Scalability, Root Cause Analysis
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Python}-based automation and validation scripts to verify transactional data quality within Azure cloud infrastructure, enhancing system reliability and observability in line with DevSecOps principles.}
        \resumeItem{Automated regression and functional testing using Java and Cucumber BDD framework, contributing to continuous integration workflows that improved test coverage and release stability by 40\%.}
        \resumeItem{Built fraud monitoring workflows integrating large-scale data pipelines and third-party platforms, enabling rapid anomaly detection and case tracking for critical banking operations.}
        \resumeItem{Collaborated with cross-functional teams using Agile methodologies to design and optimize SQL queries and cloud infrastructure components supporting enterprise workloads.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led quality assurance and testing initiatives for \textbf{Azure Cognitive Services} components, leveraging \textbf{SDKs}, REST APIs, and cloud-native tools to identify and resolve defects enhancing service reliability.}
        \resumeItem{Improved observability and automated workflow processes through extensive use of Python, Jupyter notebooks, Postman, and containerized testing environments, increasing efficiency by over 30\%.}
        \resumeItem{Optimized training and deployment of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI} platform, reducing inference latency and improving operational metrics for AI-powered applications.}
        \resumeItem{Collaborated with engineering and product teams on scalable, cloud-native AI services deployment and upgrades, maintaining alignment with the latest open source infrastructure standards.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained hands-on experience with \textbf{Azure cloud} platform, and modern development technologies including \textbf{C\#}, \textbf{C++}, XSLT, and XML, contributing to sprint goals and code quality improvements.}
        \resumeItem{Improved code maintainability and team velocity by introducing automated testing and refactoring guided by Pluralsight training and team mentorship.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led feature development for haptic feedback systems in automotive infotainment, including requirements analysis, implementation, and hardware testing to meet client and safety standards.}
        \resumeItem{Developed interactive frontend applications using React integrated with backend APIs, improving user experience in automotive design tools.}
        \resumeItem{Designed automated CI/CD pipelines with Jenkins and Bitbucket to streamline build and test processes, reducing deployment errors and integration times.}
        \resumeItem{Contributed to embedded UI and interaction workflows using Qt, C++ and CAN protocols in real-time automotive environments, enhancing system responsiveness and stability.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Implemented next-generation analytical models and core components using \textbf{Python}, Java, C++, SQL, enhancing performance and scalability of enterprise risk assessment applications.}
        \resumeItem{Developed Python tools to optimize data serialization formats for large-scale models, reducing memory footprint and improving processing times by over 80\%.}
        \resumeItem{Performed root cause analysis and debugging for critical production issues, improving system stability and reducing downtime.}
        \resumeItem{Applied \textbf{Lean Six Sigma} methodologies to improve engineering processes, reducing waste and improving delivery timelines.}
        \resumeItem{Led mentoring and onboarding initiatives and served as Scrum Master, facilitating Agile practices for high-performing engineering teams.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}