\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Senior Software Engineer} with over 8 years of experience including 3+ years with \textbf{Python} in backend development, and strong proficiency in \textbf{SQL} for data management and analytics. Experienced in designing and implementing high-quality, scalable, maintainable code and leading technical teams in Agile environments. Adept at architecture design, code optimization, and mentoring junior developers. Skilled in working with cloud-native technologies including \textbf{Google Cloud Platform}, container orchestration with \textbf{Kubernetes}, and automation with \textbf{Docker} and \textbf{Airflow}. Proven ability to deliver results in fast-paced financial and risk management domains.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, C++, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Microservices, RESTful APIs, Python (Pandas, NumPy), Object-Oriented Design \\
     \textbf{Cloud Platforms}: Google Cloud Platform (BigQuery, DataFlow, DataProc, Pub/Sub, Cloud Functions), AWS, Azure \\
     \textbf{Containerization/Orchestration}: Docker, Kubernetes, Airflow \\
     \textbf{Databases}: PostgreSQL, MySQL, MSSQL, Oracle, MongoDB \\
     \textbf{DevOps and Tools}: Jenkins, Git, CI/CD, Terraform, JIRA \\
     \textbf{Testing and QA}: JUnit, Selenium, Cucumber, TDD/BDD, Automated Testing \\
     \textbf{Development Practices}: Agile, Scrum, Code Reviews, System Design, Scalability Optimization
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and optimized \textbf{Python} scripts and \textbf{SQL} queries for validation and ETL processes in Azure Data Notebooks to ensure data integrity for fraud detection pipelines, increasing system accuracy and reliability.}
        \resumeItem{Led architectural discussions and performed detailed code reviews enforcing best practices, improving code quality and maintainability across distributed services.}
        \resumeItem{Implemented and maintained large-scale fraud monitoring workflows integrating multiple datasets and external risk tools such as OFSAA, enabling faster detection and case management.}
        \resumeItem{Collaborated in Agile teams for sprint planning, task estimation, and delivery, assisting month-end and quarter-end reporting processes related to risk analytics.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove feature quality and reliability improvements for \textbf{Azure Cognitive Services} using \textbf{Python}, \textbf{SDKs}, and REST APIs, including hands-on testing, benchmarking, and issue resolution.}
        \resumeItem{Utilized \textbf{Python (Pandas, NumPy)}, \textbf{Java}, and \textbf{SQL} with various tools to automate workflows and container-based testing pipelines, increasing development efficiency.}
        \resumeItem{Partnered with engineering and product teams to validate and optimize scalable AI and LLM-based services deployed on cloud platforms with high availability requirements.}
        \resumeItem{Contributed to the design and implementation of cloud-native components using \textbf{Kubernetes}, \textbf{Docker}, and \textbf{Azure OpenAI} services.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained proficiency in \textbf{C++}, \textbf{C\#}, and \textbf{Azure} cloud environment rapidly, contributing to development and production bug fixes within agile sprints.}
        \resumeItem{Proactively enhanced code quality and refactoring practices, improving team delivery effectiveness through mentorship and adoption of clean code principles.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led end-to-end development of haptic feedback features for Cadillac vehicles, including requirements gathering, design, implementation, and client collaboration to improve user safety and experience.}
        \resumeItem{Designed interactive React frontend and integrated backend APIs, ensuring responsive and intuitive automotive design platform features.}
        \resumeItem{Developed and tested \textbf{C++} haptics code on prototype hardware, validating vibration patterns in realistic scenarios before production deployment.}
        \resumeItem{Implemented CI/CD workflows using \textbf{Jenkins}, \textbf{Bitbucket}, and \textbf{SourceTree} to automate builds, tests, and deployments, enhancing integration efficiency and reducing errors.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed and optimized core analytics components using \textbf{Python}, \textbf{Java}, \textbf{C++}, and \textbf{SQL}, delivering up to 40\% performance improvements in risk modeling applications.}
        \resumeItem{Built \textbf{Python}-based tools to efficiently convert large datasets into compact binary formats, significantly reducing processing time and memory footprint.}
        \resumeItem{Identified and resolved production memory leaks and bottlenecks using advanced debugging and profiling tools, improving system stability.}
        \resumeItem{Led a technical team of three engineers and served as \textbf{Scrum Master}, guiding Agile practices, sprint planning, and ensuring timely delivery of multiple releases.}
        \resumeItem{Mentored new hires through pair programming, code reviews, and onboarding sessions to strengthen engineering team capabilities.}
        \resumeItem{Applied \textbf{Lean Six Sigma} principles to optimize development workflows and enhance operational efficiency.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}