\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience in \textbf{building complex, high-performance trading systems} and backend services specializing in financial services. Skilled in \textbf{Java, Python, C++}, and well-versed in \textbf{FIX protocol}, real-time messaging, and integration with distributed systems. Proven ability to rapidly iterate in \textbf{Agile} environments partnering closely with traders and product teams. Experienced in developing scalable, low-latency systems with strong focus on reliability, \textbf{real-time data streaming}, and continuous innovation. Demonstrated ability to deliver critical production support and high-quality system enhancements on enterprise trading platforms.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Spring MVC, RESTful APIs, Microservices Architecture \\
     \textbf{Trading Technologies}: FIX Protocol, Real-time Messaging (TCP, HTTP, MQ), High-Availability Architectures \\
     \textbf{Databases}: Oracle, PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, Data Factory, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, CI/CD Pipelines, Linux/Windows Server Administration \\
     \textbf{Data Streaming}: Apache Kafka, Real-time Data Processing, Event-driven Architecture \\
     \textbf{Testing and QA}: JUnit, Cucumber, Selenium, TDD/BDD, Automated and Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Wipro Technologies (TD Bank)}}{\textbf{Oct 2024 -- Present}}
      {Software Engineer}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{real-time data validation scripts} using Python and SQL to ensure high data quality and integrity in \textbf{fraud detection pipelines} integrated with streaming data sources.}
        \resumeItem{Automated regression and functional testing by building Java-based test suites with \textbf{Cucumber}, \textbf{Selenium}, and \textbf{BDD}, improving code quality and accelerating deployment cycles by 40\%.}
        \resumeItem{Collaborated closely with cross-functional teams in an \textbf{Agile} environment to rapidly deliver tactical and strategic enhancements while supporting production systems with \textbf{real-time monitoring} and troubleshooting.}
        \resumeItem{Optimized complex SQL queries and developed scalable backend components, contributing to system performance improvements aligned with business requirements and trading workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{LTI Mindtree LTD (Microsoft)}}{\textbf{Dec 2023 -- Apr 2024}}
      {Senior Data Engineer}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led testing and quality assurance for \textbf{Azure Cognitive Services} features, utilizing SDKs and \textbf{REST APIs} to validate performance and stability in production-like environments.}
        \resumeItem{Developed automated scripts and containerized workflows in Java, Python, and C\# to support \textbf{real-time data processing} and integration, improving reliability by 30\%.}
        \resumeItem{Conducted extensive model training and optimization in \textbf{Azure OpenAI} platform, enhancing system responsiveness and throughput with focus on low latency and scalability.}
        \resumeItem{Collaborated in cross-functional teams including product managers and engineers to refine features for \textbf{high-performance, cloud-native AI services} aligned with business goals.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{ESO}}{\textbf{Jan 2024 -- Apr 2024}}
      {Software Development Engineer Co-op}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained experience with \textbf{C++} and \textbf{C\#} on complex codebases, enabling delivery of critical bug fixes and sprint stories in a \textbf{real-time integrated environment}.}
        \resumeItem{Introduced improvements in code quality and refactoring using mentorship and online resources, increasing development speed and reliability for production components.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{People Tech Group Private Ltd.}}{\textbf{Jan 2022 -- Aug 2022}}
      {Software Engineer}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed interactive frontend applications using React and integrated with backend APIs, supporting configuration tools and user interfaces in demanding automotive environments.}
        \resumeItem{Contributed to automotive infotainment systems by developing C++ modules integrated with complex HMI frameworks, ensuring high responsiveness and stability under constrained conditions.}
        \resumeItem{Implemented automated CI/CD pipelines using Jenkins and Bitbucket, streamlining builds and deployment with improved traceability and reduced integration issues.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Verisk Analytics}}{\textbf{Sep 2018 -- Jan 2022}}
      {Software Engineer II}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{high-performance core components} in Java, C++, and Python, achieving 40\% average performance gains in large-scale analytical models used in enterprise applications.}
        \resumeItem{Built a Python tool to optimize data serialization into binary formats, reducing model load times by over 80\% to support faster damage computations.}
        \resumeItem{Led troubleshooting and root cause analysis for critical memory and latency issues in production systems, improving system stability and fault tolerance.}
        \resumeItem{Certified in \textbf{Lean Six Sigma}, applying process optimizations to improve cross-team efficiency and reduce defect rates.}
        \resumeItem{Mentored engineers as Scrum Master, facilitating Agile ceremonies and fostering collaborative delivery of trading and analytics platform features.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}