\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} and \textbf{Crypto Platform Engineer} with 5+ years of experience building and supporting secure, enterprise-grade applications and cryptographic security products. Skilled in \textbf{Java}, \textbf{Bash}, and \textbf{PowerShell} scripting for automation and troubleshooting, with strong expertise in cryptography, key management, and cloud platforms including \textbf{AWS}, \textbf{Azure}, and \textbf{GCP}. Proven ability to support and lead secure platform implementations in financial and enterprise environments, with focus on performance, compliance, and risk mitigation. Experienced collaborating cross-functionally with IT support, security teams, and business partners to deliver stable and resilient systems.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, Bash, PowerShell, C++, C\#, SQL \\
     \textbf{Crypto Technologies}: Crypto Engineering, Key Management, HSM Integration, Security Platform Support \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3), Azure (DevOps, AKS, Data Factory), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, Bitbucket, JIRA, Confluence, CI/CD Pipelines \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MongoDB, Redis \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, Automated Testing, Regression Testing \\
     \textbf{Development Practices}: Agile/Scrum, Change Management, Incident Troubleshooting, Disaster Recovery Testing \\
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Wipro Technologies (TD Bank)}}{\textbf{Oct 2024 -- Present}}
      {Software Engineer}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Provide technology operations support for financial applications, including automation of data validation using \textbf{Python} and \textbf{SQL}, improving accuracy and system reliability.}
        \resumeItem{Automated regression and functional testing with Java-based test suites using \textbf{Cucumber} and BDD, enhancing test coverage and deployment quality.}
        \resumeItem{Collaborate cross-functionally with IT and business teams to support platform stability and incident resolution, aligning with security and compliance standards.}
        \resumeItem{\textbf{Support operational activities such as change request creation, software currency upgrades, and regression testing}, ensuring environment integrity in production and non-production stages.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{LTI Mindtree LTD (Microsoft)}}{\textbf{Dec 2023 -- Apr 2024}}
      {Senior Data Engineer}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led integration and testing of \textbf{Azure Cognitive Services}, identifying defects and improving product increase reliability and security robustness.}
        \resumeItem{Utilized \textbf{Java}, \textbf{Python}, and \textbf{Kusto} queries to streamline workflows, diagnostics, and containerized deployments, boosting observability by 30\%.}
        \resumeItem{Collaborated with security and product teams to validate cloud AI services, ensuring alignment with security best practices and enterprise standards.}
        \resumeItem{Implemented automation solutions to support application lifecycle, \textbf{including patching, deployment orchestration, and monitoring} in cloud environments.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{ESO}}{\textbf{Jan 2024 -- Apr 2024}}
      {Software Development Engineer Co-op}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{Azure}-based applications involving \textbf{C\#} and \textbf{C++}, gaining hands-on experience with cloud services and secure coding practices.}
        \resumeItem{Enhanced code quality and security posture by applying refactoring and best practices, supporting reliable feature delivery under Agile methodologies.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{People Tech Group Private Ltd.}}{\textbf{Jan 2022 -- Aug 2022}}
      {Software Engineer}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed and integrated automotive HMI software features including interactive frontend using \textbf{React} and backend services with focus on security and user experience.}
        \resumeItem{Designed testing strategies for embedded \textbf{haptics} functionality, validating under realistic conditions to ensure safety-compliant system behavior.}
        \resumeItem{Implemented and maintained \textbf{CI/CD} pipelines using \textbf{Jenkins}, \textbf{Bitbucket}, and \textbf{SourceTree}, automating builds, deployment, and tests for faster and reliable software delivery.}
        \resumeItem{Participated in security-focused reviews and regression testing to maintain integrity of automotive infotainment systems.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Verisk Analytics}}{\textbf{Sep 2018 -- Jan 2022}}
      {Software Engineer II}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed analytical models and core software components using \textbf{Java}, \textbf{C\#}, and \textbf{Python}, improving application performance and robustness by 40\%.}
        \resumeItem{Built Python utilities for data optimization, significantly reducing processing times and storage usage, improving system efficiency.}
        \resumeItem{Diagnosed and resolved complex production issues through root cause analysis and incident troubleshooting, minimizing downtime and ensuring stable releases.}
        \resumeItem{Led scrum teams, applied \textbf{Lean Six Sigma} process improvements, and partnered with product management to improve feature delivery and compliance with security policies.}
        \resumeItem{Supported application portfolio management and compliance remediation, reducing audit findings by addressing security and control gaps proactively.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}