\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience designing, developing, and launching highly available, distributed backend systems at scale. Skilled in \textbf{Python}, \textbf{Java/Spring Boot}, and \textbf{Node.js}, with strong expertise in \textbf{microservices architecture}, \textbf{RESTful API design}, and cloud platforms including \textbf{AWS} and \textbf{Azure}. Proven ability to lead engineering teams through ambiguity to deliver scalable solutions, with experience driving product lifecycle from ideation to release. Excels at collaborating across teams including product management, design, and data science to build reliable and performant systems supporting millions of users.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, Kotlin, C++, C\#, SQL, Bash \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices, Service-Oriented Architecture \\
     \textbf{Databases}: MySQL, PostgreSQL, Oracle, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms \& Orchestration}: AWS (EC2, Lambda, S3, DynamoDB, EKS), Azure (AKS, DevOps), Kubernetes \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Terraform, CI/CD Pipelines \\
     \textbf{Event-Driven Architecture}: Apache Kafka, Event Streaming, Real-time Data Processing \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, TDD/BDD, Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and \textbf{SQL} validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, substantially enhancing data integrity and system reliability.}
        \resumeItem{Automated regression and functional testing using Java-based test suites (Cucumber, Selenium, BDD), improving delivery confidence and reducing manual QA efforts by 40\%.}
        \resumeItem{\textbf{Collaborated cross-functionally} with product, design, and analytics teams in Agile Scrum ceremonies to define technical constraints and scope for features impacting financial fraud monitoring.}
        \resumeItem{Designed and optimized complex SQL queries and workflows for fraud monitoring over large transactional datasets, enhancing detection speed and accuracy.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove quality improvements for \textbf{Azure Cognitive Services} by testing new features via \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Azure AI Studio}, significantly increasing \textbf{service reliability} and performance.}
        \resumeItem{Streamlined workflows through automation in \textbf{Jupyter}, \textbf{Postman}, \textbf{Java}, \textbf{Python}, and \textbf{Kusto} queries, improving observability and system stability.}
        \resumeItem{Led training and performance optimization of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, reducing latency for real-time workloads and boosting model deployment efficiency by 25\%.}
        \resumeItem{Partnered with cross-functional teams to validate scalable, production-ready \textbf{AI services}, contributing to robust system design and extensibility.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained rapid proficiency in \textbf{C\#}, \textbf{C++}, \textbf{XSLT}, \textbf{XML}, and \textbf{Azure} on complex codebases, independently delivering sprint user stories and resolving production issues.}
        \resumeItem{Introduced code quality and refactoring improvements, increasing team efficiency and aligning with best practices for maintainable, scalable software development.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led design and implementation of haptic feedback features for Cadillac vehicles with focus on safety, UX alignment, and system scalability through collaboration with cross-disciplinary teams.}
        \resumeItem{Developed React-based frontend integrating with backend APIs to deliver responsive UI for automotive design configurations.}
        \resumeItem{Implemented CI/CD pipelines automating builds and tests using \textbf{Jenkins}, resulting in faster, reliable software releases across distributed teams.}
        \resumeItem{Contributed to infotainment UI and interaction workflows using \textbf{Qt}, \textbf{C++}, and automotive middleware, enhancing system responsiveness and reliability.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and developed scalable, high-performance analytical models and components using \textbf{Java}, \textbf{Python}, and \textbf{C++}, improving system throughput by 40\%.}
        \resumeItem{Built a \textbf{Python} application to convert model data into optimized binary formats, reducing data size from 2GB to 200MB, enabling faster processing in distributed systems.}
        \resumeItem{Diagnosed and resolved critical production issues using systematic debugging and performance profiling, improving system availability.}
        \resumeItem{Mentored new engineers and led a team of three as \textbf{Scrum Master}, fostering engineering best practices and supporting continuous delivery in Agile environments.}
        \resumeItem{Collaborated with Product and Research teams for feature scoping, and led the adoption of coding standards improving code review quality and maintainability.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}