\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building end-to-end, cloud-native web applications and backend services specializing in \textbf{Python} and \textbf{Microsoft SQL}. Experienced in designing and developing \textbf{web-based APIs} integrated with powerful SQL analytics engines and deploying solutions on \textbf{Azure}. Proven ability to optimize database structures and analytics layers to deliver accurate, robust data delivery for financial services platforms. Skilled at collaborating in Agile environments and focused on performance optimization, reliability, and scalable system integration.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Python Flask, Spring Boot, Node.js, RESTful APIs, Microservices Architecture \\
     \textbf{Databases}: Microsoft SQL Server, SSAS, PostgreSQL, MySQL, Oracle, MongoDB \\
     \textbf{Cloud Platforms}: Azure (Data Factory, AKS, DevOps, Microsoft Fabric), AWS, GCP \\
     \textbf{ETL and Analytics}: ETL pipeline development, star and snowflake schemas, BI and Semantic Layer practices \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Testing and QA}: Postman, JUnit, Cucumber, TDD/BDD, Automated and Performance Testing \\
     \textbf{Methodologies}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and \textbf{SQL} validation scripts in \textbf{Azure Data Notebooks} to validate and ensure accuracy of incoming fraud data streams, enhancing data integrity and reliability.}
        \resumeItem{Developed and maintained RESTful \textbf{web-based APIs} for real-time fraud detection workflows, ensuring seamless integration with backend SQL analytics engines and third-party systems.}
        \resumeItem{Automated regression and functional testing using Java, Cucumber, Selenium, and BDD practices to reduce manual efforts and increase release quality by 40\%.}
        \resumeItem{Optimized complex \textbf{SQL queries} and collaborated cross-functionally within Agile teams to deliver scalable, high-impact data solutions.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove improvements for \textbf{Azure Cognitive Services} by testing new capabilities using \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Azure AI Studio}, contributing to system reliability and scalability.}
        \resumeItem{Streamlined code testing and data validation workflows with \textbf{Jupyter}, \textbf{Postman}, \textbf{Python}, and \textbf{Kusto} queries, enhancing product quality by 30\%.}
        \resumeItem{Contributed to development of \textbf{AI} and \textbf{ML} models deployed on \textbf{Azure OpenAI} to enhance cognitive service offerings with improved latency and accuracy.}
        \resumeItem{Collaborated across engineering teams to validate integration and scalability of \textbf{Azure AI} services within cloud-native environments.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Quickly ramped up on \textbf{Azure} technologies, \textbf{C\#}, \textbf{C++}, \textbf{XSLT}, and \textbf{XML}, contributing to development and maintenance of complex backend services.}
        \resumeItem{Introduced code-quality and refactoring improvements, increasing development velocity by 10-15\% through effective knowledge sharing and mentorship.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of haptic feedback features for Cadillac vehicles from design through integration, collaborating closely with cross-disciplinary teams to align with safety and UX requirements.}
        \resumeItem{Developed interactive frontend applications using React, integrating backend APIs for seamless data delivery and improving system responsiveness.}
        \resumeItem{Designed and validated haptics functionality and timing on prototype hardware to ensure performance in real driving conditions.}
        \resumeItem{Contributed to infotainment UI workflows using \textbf{Qt}, \textbf{WeCAN}, and \textbf{C++}, enhancing responsiveness and system reliability.}
        \resumeItem{Implemented CI/CD pipelines with Jenkins, SourceTree, and Bitbucket, automating builds and deployments to improve integration efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed core analytical components and models using \textbf{Java}, \textbf{Python}, \textbf{C\#}, \textbf{C++}, and \textbf{SQL}, achieving an average 40\% performance boost across multiple critical financial models.}
        \resumeItem{Built a scalable \textbf{Python}-based tool to convert large-scale model data into optimized binary formats, reducing load times and improving downstream data processing efficiency.}
        \resumeItem{Diagnosed and resolved production issues including memory leaks and performance bottlenecks to maintain system integrity and uptime.}
        \resumeItem{Applied \textbf{Lean Six Sigma} methodologies to improve engineering workflows and reduce waste in development cycles.}
        \resumeItem{Mentored team members and led a team of three engineers, serving as \textbf{Scrum Master} to drive Agile best practices and timely delivery.}
        \resumeItem{Collaborated with Product Management and Research to refine data requirements and design scalable, accurate analytics solutions for financial services.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}