\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience delivering end-to-end software solutions and collaborating in Agile environments. Skilled in \textbf{Python}, \textbf{web development (HTML, CSS, JavaScript)}, and \textbf{version control with Git}. Experienced in stakeholder management, translating business requirements into technical specifications, and process improvement. Proven ability to support technical change requests and develop \textbf{PowerBI} dashboards and \textbf{Power Automate} workflows. Strong written and verbal communication skills with a focus on aligning stakeholders and delivering scalable, maintainable software products.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, JavaScript, HTML, CSS, SQL, Bash \\
     \textbf{Frameworks}: Spring Boot, Node.js, React, RESTful APIs \\
     \textbf{Tools \& Platforms}: Git, Jira, Confluence, SharePoint, PowerBI, Power Automate, Azure, AWS \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis \\
     \textbf{Development Practices}: Agile, Scrum, PDLC, Code Reviews, CI/CD \\
     \textbf{Other}: Data Visualization, Stakeholder Management, Change Coordination, Automation Solutions
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Coordinate with stakeholders to manage and support \textbf{technical change requests}, acting as primary contact for change-related communications and ensuring alignment on scope and delivery.}
        \resumeItem{Implemented robust \textbf{Python} and SQL validation scripts in Azure Data Notebooks to verify incoming data streams, enhancing data integrity in fraud detection pipelines.}
        \resumeItem{Tracked deliverables and progress utilizing \textbf{Jira} and \textbf{Confluence}, performing follow-ups to maintain clarity on timelines and change windows.}
        \resumeItem{Developed and maintained \textbf{PowerBI} dashboards and automation workflows using \textbf{Power Automate}, increasing team's efficiency by streamlining reporting processes.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Data Engineer}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Participated actively in requirements gathering sessions, translating business needs into technical specifications, driving improvements in Azure Cognitive Services features.}
        \resumeItem{Utilized \textbf{Python}, \textbf{Azure AI Studio}, and RESTful APIs to test and enhance cloud AI services, contributing to a 30\% increase in product reliability.}
        \resumeItem{Collaborated using \textbf{Git} version control and containerized workflows for code testing and deployment, fostering efficient team collaboration in an Agile environment.}
        \resumeItem{Helped define and document new processes to improve operational efficiency, using \textbf{SharePoint} and \textbf{Confluence} to centralize knowledge sharing.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Development Engineer Co-op}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained expertise in \textbf{C\#}, \textbf{Azure}, and XML technologies, independently owning sprint deliverables and resolving production issues.}
        \resumeItem{Used self-driven learning and mentorship to improve team development processes, contributing to faster feature delivery and increased code quality while following Agile methodologies.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led frontend development using \textbf{React}, HTML, CSS, and JavaScript to build responsive client interfaces, collaborating closely with cross-disciplinary teams.}
        \resumeItem{Communicated technical progress and changes effectively with clients, ensuring requirements were clear and expectations managed throughout development cycles.}
        \resumeItem{Designed and tested haptics integration and interactive components, enhancing user experience in automotive platforms using \textbf{Qt} and \textbf{C++}.}
        \resumeItem{Improved CI/CD pipelines using \textbf{Jenkins} and \textbf{Git} based version control, reducing deployment times and minimizing integration issues.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer II}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed scalable analytical models and backend services using \textbf{Python}, \textbf{Java}, and \textbf{C++} contributing to system performance improvements of up to 40\%.}
        \resumeItem{Built Python scripts for data transformations and automations, aligning with Agile practices and improving data workflows efficiency.}
        \resumeItem{Led stakeholder interactions to refine feature requirements, ensuring alignment between business and technical teams.}
        \resumeItem{Contributed as \textbf{Scrum Master} driving Agile ceremonies and facilitating smooth product delivery cycles.}
        \resumeItem{Certifed in \textbf{Lean Six Sigma}, applied process improvement techniques to optimize team workflows and increase productivity.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}