\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience delivering end-to-end, cloud-native applications and \textbf{DevOps-driven} backend services for enterprise clients. Skilled in \textbf{Java/Spring Boot}, \textbf{Python}, and scripting with strong expertise in \textbf{performance engineering}, \textbf{garbage collection analysis}, and \textbf{server/host capacity analysis}. Proficient in designing and testing \textbf{RESTful APIs}, with a solid understanding of Agile methodologies, \textbf{three-tier web architecture}, and distributed client-server models. Experienced in leading complex automated test planning, execution, and coordinating releases in multi-environment, high-availability setups. Strong collaborator with proven success in mentoring and optimizing software quality in large-scale environments.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, Bash, PowerShell, C++, C\#, SQL \\
     \textbf{Backend and Frameworks}: Spring Boot, RESTful API Design, Microservices, Three-tier Architecture, Client-Server Model \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, Azure DevOps, Terraform, CI/CD Pipelines, Virtualized Environments \\
     \textbf{Performance Engineering}: Garbage Collection Analysis, Server/Host Capacity Analysis, Automated Test Frameworks, Load and Stress Testing \\
     \textbf{Testing and QA}: Cucumber, Selenium, JUnit, Automated Testing, BDD/TDD, Test Planning, Defect Tracking, Risk Analysis \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3), Azure (DevOps, AKS, Data Factory), GCP \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, Test Documentation, Audit Compliance, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Led test planning, preparation, and execution for fraud detection data pipelines, implementing comprehensive validation scripts in Python and SQL that enhanced data integrity and system stability.}
        \resumeItem{Automated regression and functional test cases using Java, Cucumber, and Selenium with BDD practices, increasing test coverage and reducing manual testing effort by 40\%.}
        \resumeItem{Monitored and analyzed system performance including Garbage Collection and server capacity metrics to optimize resource utilization and prevent production impact.}
        \resumeItem{Collaborated closely with business stakeholders, infrastructure, and CIO groups, coordinating integration, acceptance, performance, and deployment testing across multiple environments in Agile sprints.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Conducted rigorous automated and manual testing of Azure Cognitive Services features using SDKs, RESTful APIs, and Azure AI Studio to ensure product performance and operability.}
        \resumeItem{Analyzed performance bottlenecks and applied risk analysis for new AI capabilities, improving test coverage and coordinating with offshore teams on integration and release activities.}
        \resumeItem{Developed and maintained virtualized test environments and components using containerization and cloud orchestration tools to simulate production conditions and validate code deployments.}
        \resumeItem{Documented and led review sessions for test plans, defect logs, and quality metrics, ensuring audit readiness and adherence to project gating criteria.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly adapted to complex tech stack including XSLT, XML, C\#, and C++ within Azure environment, owning user stories and fixing production issues aligned with Agile processes.}
        \resumeItem{Implemented code-quality improvements and refactoring to support maintainability and automated testing, strengthening system reliability and development velocity.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development and testing of haptic feedback systems for Cadillac, including integrated testing on prototype hardware and validating performance and timing metrics to ensure safety compliance.}
        \resumeItem{Designed React-based frontend solutions interfacing with RESTful backend APIs, and contributed to infotainment UI and interaction workflows using Qt and C++, ensuring responsive client-server communication.}
        \resumeItem{Implemented and managed CI/CD pipelines using Jenkins and Bitbucket for automated build and testing, reducing deployment errors and improving release frequency.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented optimized analytical models using Java, C\#, Python, and SQL with focus on scalability, resulting in an average 40\% performance enhancement.}
        \resumeItem{Performed deep root-cause analysis, debugging complex memory leaks and bottlenecks, along with monitoring Garbage Collection and server capacity parameters to ensure smooth production operations.}
        \resumeItem{Authored and executed detailed test plans, coordinated defect tracking and resolution with cross-functional teams, and led Scrum ceremonies as Scrum Master to maintain project flow.}
        \resumeItem{Mentored junior team members and coordinated knowledge sharing on testing best practices, automated test case development, and Agile methodologies.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}