\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} and \textbf{Data Engineer} with 5+ years of experience building end-to-end data-intensive and cloud-native backend services for financial services and enterprise organizations. Skilled in \textbf{Java}, \textbf{Python}, \textbf{SQL}, and frameworks like \textbf{Spring Boot} and \textbf{Apache Spark} with hands-on expertise designing and maintaining \textbf{data pipelines}, working with \textbf{big data formats (Parquet, JSON, XML)}, and automating CI/CD deployments on \textbf{AWS}, \textbf{Azure}, and \textbf{GCP}. Proven ability to deliver scalable data integration and analytics solutions following Agile methodologies in complex, regulated environments including \textbf{TD Bank} and \textbf{Microsoft}.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, Scala, SQL, Bash, PowerShell \\
     \textbf{Big Data \& ETL Tools}: Apache Spark, Apache Beam, Talend, Azure Data Factory, Spring Batch \\
     \textbf{Data Formats}: Parquet, JSON, XML, ORC, Iceberg \\
     \textbf{Data Architecture}: Medallion, Lakehouse, Data Warehouse paradigms \\
     \textbf{Databases}: Oracle, MSSQL, PostgreSQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS, Azure, GCP (Google Cloud Build, Terraform) \\
     \textbf{DevOps \& Orchestration}: Jenkins, Airflow, Git, Bitbucket, CI/CD Pipelines, Terraform \\
     \textbf{Containers \& Automation}: Docker, Kubernetes, Terraform, Automated profiling and deployment \\
     \textbf{Development Practices}: Agile (Scrum, Kanban), Code Reviews, Root Cause Analysis, JIRA \\
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained scalable \textbf{data pipelines} and validation scripts in \textbf{Python} and \textbf{SQL} within Azure Data Notebooks, improving \textbf{data quality} for fraud detection and AML processes.}
        \resumeItem{Automated regression and functional testing with \textbf{Java}-based suites using \textbf{Cucumber}, Selenium, and \textbf{BDD} practices, improving reliability by 40\%.}
        \resumeItem{Built and managed workflows for large-scale transactional datasets leveraging third-party tools to enable rapid \textbf{case creation and monitoring} of suspicious activities.}
        \resumeItem{Collaborated with cross-functional teams in an \textbf{Agile/Scrum} environment, optimizing SQL queries and deploying robust backend services for fraud analytics.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led quality and performance testing for \textbf{Azure Cognitive Services} using \textbf{REST APIs}, \textbf{SDKs}, and \textbf{Azure AI Studio}, enhancing service reliability.}
        \resumeItem{Streamlined complex workflows combining \textbf{Jupyter}, \textbf{Python}, \textbf{Java}, \textbf{Kusto} queries, delivering 30\% improvement in data processing and observability.}
        \resumeItem{Trained and optimized \textbf{OpenAI GPT} models on \textbf{Azure OpenAI} platform, achieving a 25\% boost in AI performance for real-time workloads.}
        \resumeItem{Collaborated in cross-functional teams to validate and scale next-generation \textbf{Azure AI} features for enterprise data and analytics scenarios.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Rapidly upskilled in \textbf{XSLT}, \textbf{XML}, \textbf{C\#}, \textbf{C++}, and \textbf{Azure} to independently deliver sprint stories and address production issues.}
        \resumeItem{Implemented code quality improvements increasing development velocity by 10-15\%, leveraging \textbf{Pluralsight} trainings and mentorship.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led end-to-end development of haptic feedback features for Cadillac vehicles, including requirements analysis, design, implementation, and client coordination.}
        \resumeItem{Developed interactive frontend UI in React with backend API integration, providing responsive user experience for automotive design platform.}
        \resumeItem{Tested and validated \textbf{haptic} feedback hardware functionality in realistic scenarios, ensuring compliance with safety and quality standards.}
        \resumeItem{Contributed to infotainment UI components using \textbf{Qt}, \textbf{Rhapsody}, and \textbf{C++}, improving system responsiveness and stability.}
        \resumeItem{Automated CI/CD pipelines using \textbf{Jenkins}, \textbf{SourceTree}, and \textbf{Bitbucket}, reducing build and deployment times for automotive software releases.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented core analytical models and services using \textbf{Java}, \textbf{Python}, \textbf{C\#}, \textbf{SQL}, delivering up to 40\% performance improvements for business-critical applications.}
        \resumeItem{Developed a \textbf{Python}-based application to convert large datasets into optimized binary formats, reducing file sizes from 2GB to 200MB and improving processing efficiency.}
        \resumeItem{Diagnosed and resolved critical production issues via root cause analysis, memory leak identification, and performance tuning.}
        \resumeItem{Certified in \textbf{Lean Six Sigma} and applied process improvements to optimize development workflows and reduce engineering waste.}
        \resumeItem{Mentored new hires with systematic onboarding, pair programming, and regular code reviews, enhancing team productivity and code quality.}
        \resumeItem{Led a team of three engineers and served as \textbf{Scrum Master}, collaborating with Product and Research teams to deliver scalable and high-performance solutions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}