\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Detail-oriented \textbf{Software Engineer} with 5+ years of experience in building and evaluating complex software systems using \textbf{Python}, \textbf{Java}, \textbf{C\#}, and \textbf{JavaScript}. Skilled in \textbf{data structures}, \textbf{algorithms}, and debugging to solve challenging coding problems. Experienced in training and evaluating AI models, assessing quality and performance, and improving system reliability. Strong collaborator with proven ability to explain and communicate technical solutions effectively. Based in Canada and fluent in English.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, JavaScript, Java, C\#, C++, SQL, HTML, Bash \\
     \textbf{AI/ML Tools}: OpenAI GPT, Azure AI Studio, REST APIs, SDKs \\
     \textbf{Data Structures \& Algorithms}: Proficient in problem solving and coding challenges \\
     \textbf{Backend and Frameworks}: Node.js, Spring Boot, RESTful APIs, Microservices \\
     \textbf{DevOps and Tools}: Git, Jenkins, Docker, Kubernetes, Azure DevOps \\
     \textbf{Testing}: Automated testing frameworks, Debugging, Test-Driven Development \\
     \textbf{Cloud Platforms}: Azure, AWS, Azure Cognitive Services \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python} and \textbf{SQL} validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, enhancing data quality and system reliability.}
        \resumeItem{Automated regression and functional testing by developing \textbf{Java}-based test suites using Cucumber and Selenium, increasing test coverage and reducing manual testing effort by 40\%.}
        \resumeItem{Built and maintained fraud monitoring workflows leveraging large datasets to detect suspicious financial transactions and improve monitoring accuracy.}
        \resumeItem{\textbf{Performed detailed code reviews and debugging to solve complex problems}, ensuring robustness and maintainability of fraud detection applications.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove improvements in \textbf{Azure Cognitive Services} by rigorously testing AI features using \textbf{SDKs}, \textbf{REST APIs}, and \textbf{Azure AI Studio}, enhancing quality and performance.}
        \resumeItem{Streamlined cross-language code testing and debugging workflows using \textbf{Python}, \textbf{Java}, \textbf{C\#}, and \textbf{Kusto} queries, improving product stability by 30\%.}
        \resumeItem{Led training, evaluation, and optimization of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, achieving a significant performance improvement in AI chatbot outputs.}
        \resumeItem{Collaborated with engineering teams to evaluate AI model correctness and performance, contributing to scalable and production-ready AI services.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Quickly ramped up on \textbf{C\#}, \textbf{C++}, \textbf{XSLT}, and \textbf{Azure}, contributing to sprint user stories and solving production bugs independently.}
        \resumeItem{Introduced code-quality improvements through refactoring and mentoring, increasing development efficiency by 10-15\%.}
        \resumeItem{Contributed to debugging workflows to troubleshoot and resolve functional issues efficiently.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led end-to-end development of haptic feedback features for Cadillac vehicles, analyzing requirements and ensuring alignment with safety standards.}
        \resumeItem{Developed interactive React frontend applications integrating backend APIs, improving user experience and functionality.}
        \resumeItem{Tested \textbf{haptics} on prototype hardware to validate performance under real driving conditions.}
        \resumeItem{Contributed to infotainment UI workflows using \textbf{Qt} and \textbf{C++} in an automotive HMI environment, improving system stability.}
        \resumeItem{Implemented CI/CD pipelines with Jenkins and Bitbucket, automating build and test processes to reduce integration issues.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and optimized core analytical models using \textbf{Java}, \textbf{Python}, \textbf{C\#}, and \textbf{C++}, improving performance by 40\%.}
        \resumeItem{Developed Python tools for data processing that reduced file sizes and improved system efficiency significantly.}
        \resumeItem{Performed detailed debugging and root-cause analysis to resolve critical production issues effectively.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process improvements to enhance development workflows.}
        \resumeItem{Mentored junior engineers and served as \textbf{Scrum Master}, facilitating agile ceremonies and cross-team collaboration.}
        \resumeItem{Collaborated with Product and Research teams to refine technical requirements and deliver scalable software solutions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}