\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building end-to-end, cloud-native web applications and backend services with strong expertise in \textbf{Node.js}, \textbf{React.js}, and \textbf{JavaScript}. Skilled in designing scalable \textbf{RESTful APIs}, integrating \textbf{NoSQL databases} like \textbf{MongoDB} and \textbf{Redis}, and deploying containerized applications using \textbf{Kubernetes} and \textbf{Cloud Foundry}. Proven ability to develop secure authentication solutions leveraging \textbf{oAuth2} and \textbf{JWT}, and implement best practices in code quality, security scanning, and CI/CD pipelines. Experienced in mentoring teams and leading technical discussions to drive high-quality, enterprise-grade digital banking applications.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: JavaScript (ES6+), TypeScript, Java, Python, C++, C\# \\
     \textbf{Backend and Frameworks}: Node.js, Express, Spring Boot, RESTful APIs, Microservices Architecture \\
     \textbf{Frontend}: React.js, HTML5, CSS3, Jest, Protractor \\
     \textbf{Databases}: MongoDB, Redis, PostgreSQL, MySQL, Oracle \\
     \textbf{Cloud Platforms}: AWS, Azure (AKS, DevOps), GCP, Cloud Foundry \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, GitHub Actions, Azure DevOps, CI/CD Pipelines \\
     \textbf{Security}: oAuth2, JWT, SSO, Security Scanning and Best Practices \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, Test-Driven Development (TDD), JIRA
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Designed and implemented key backend components using \textbf{Node.js}, \textbf{Express}, and \textbf{RESTful APIs} to support digital banking use cases focusing on authentication and fraud detection workflows.}
        \resumeItem{Applied \textbf{security best practices} including authentication flows using \textbf{oAuth2} and \textbf{JWT} tokens to secure APIs, and conducted \textbf{security scanning} to identify and remediate vulnerabilities.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber, Selenium, and BDD practices, reducing manual testing effort by 40\% and increasing feature reliability.}
        \resumeItem{Collaborated with cross-functional Agile teams including architects and product owners to drive technical discussions and ensure adherence to coding standards and scalability requirements.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Led development and integration efforts for \textbf{Azure Cognitive Services} features, improving system security and performance by testing using \textbf{REST APIs}, SDKs, and \textbf{Azure AI Studio}.}
        \resumeItem{Enhanced product observability and reliability by managing containerized workflows and testing using \textbf{Jupyter}, \textbf{Postman}, and multiple programming languages, collaborating with distributed teams.}
        \resumeItem{Pioneered the training and optimization of machine learning models on \textbf{Azure OpenAI} platform, improving model performance and reducing latency for real-time applications by 25\%.}
        \resumeItem{Worked closely with product and engineering teams to validate and productionize scalable AI services, utilizing cloud-native CI/CD and container orchestration tools.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Ramped up quickly on \textbf{Azure} cloud services and C\# backend, independently handling user story implementation and production bug fixes in an Agile environment.}
        \resumeItem{Contributed to improved software quality by implementing code refactoring and quality standards, enabling smoother feature delivery during sprints.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led the development of frontend features for automotive design platforms using \textbf{React.js}, building responsive UI components consuming backend \textbf{RESTful APIs} to enable seamless user experiences.}
        \resumeItem{Implemented secure authentication flows and session management for client applications, collaborating closely with UI/UX and backend teams.}
        \resumeItem{Designed and tested \textbf{haptic feedback} functions on prototype automotive hardware, ensuring reliable integration with client systems.}
        \resumeItem{Contributed to infotainment system workflows using \textbf{Qt}, \textbf{Rhapsody}, and \textbf{C++} in a safety-critical automotive context.}
        \resumeItem{Built and maintained \textbf{CI/CD} pipelines using \textbf{Jenkins} and Git repositories to automate software testing and deployment, improving release frequency and quality.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed scalable backend components and analytical models using \textbf{Java}, \textbf{Python}, and \textbf{C\#}, optimizing performance by 40\% for enterprise-grade applications.}
        \resumeItem{Automated data processing workflows and optimized file handling using Python, significantly reducing data load time and improving processing efficiency.}
        \resumeItem{Diagnosed and fixed production memory leaks and performance bottlenecks through advanced debugging and profiling techniques.}
        \resumeItem{Earned \textbf{Lean Six Sigma} certification and applied process improvements to increase engineering efficiency and reduce waste.}
        \resumeItem{Mentored junior engineers and led a scrum team of three, facilitating Agile ceremonies and promoting best coding practices across the department.}
        \resumeItem{Collaborated with product managers and research teams to deliver secure, scalable, and robust software aligned with business requirements.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}