\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building end-to-end, cloud-native web applications and backend services with a strong focus on \textbf{Python}, \textbf{RESTful APIs}, and \textbf{AWS} services. Experienced in designing modular and maintainable code, implementing unit tests, and working with microservices and serverless architectures. Proficient in improving system observability and troubleshooting in distributed systems. Proven track record delivering high-impact projects and mentoring peers on backend best practices in distributed, event-driven architectures.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: RESTful APIs, Spring Boot, Microservices Architecture, Serverless (AWS Lambda) \\
     \textbf{Cloud Platforms}: AWS (Lambda, API Gateway, DynamoDB, EventBridge, S3, CloudFormation, CodePipeline), Azure, GCP \\
     \textbf{Databases}: DynamoDB, MongoDB, PostgreSQL, MySQL, Redis \\
     \textbf{DevOps and Tools}: Jenkins, Git, Terraform, AWS CDK, CI/CD Pipelines, Docker, Kubernetes \\
     \textbf{Observability}: OpenTelemetry, Prometheus, Grafana, Honeycomb \\
     \textbf{Testing and QA}: Unit Testing, Integration Testing, Contract Testing, TDD, BDD, Postman, JUnit \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Event-Driven Architecture, CI/CD, JIRA
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust \textbf{Python}-based data validation scripts within Azure Data Notebooks for fraud detection pipelines, improving data integrity and downstream system reliability.}
        \resumeItem{Developed and optimized RESTful APIs and validation workflows, integrating with cloud services and streamlining ingestion using \textbf{test-driven development} practices to enhance feature stability.}
        \resumeItem{Collaborated closely with cross-functional Agile teams, including UI and QA, to ensure features satisfy \textbf{Definition of Done} with comprehensive \textbf{unit} and \textbf{integration tests}, improving deployment safety.}
        \resumeItem{Contributed to improving system observability and incident troubleshooting processes by monitoring logs and metrics, aligning with DevOps and SRE teams for smoother incident response.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{Azure Cognitive Services} quality by testing \textbf{REST APIs}, SDKs, and cloud AI tools using unit and integration tests, ensuring robust deployment of cognitive features.}
        \resumeItem{Automated workflows using \textbf{Python}, \textbf{Jupyter}, and \textbf{containerization} techniques to improve reliability and observability by 30\%, incorporating event-driven and serverless best practices.}
        \resumeItem{Led experimentation and tuning of \textbf{OpenAI GPT} models on \textbf{Azure OpenAI}, improving model performance and reducing real-time latency through effective benchmarking and optimization.}
        \resumeItem{Collaborated with engineering and product teams to architect scalable cloud solutions, focusing on \textbf{microservices architecture}, observability, and contract testing methodologies.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained expertise in \textbf{Azure} services, XML/XSLT transformations, and C\# within a complex domain, responsible for independent delivery of sprint tasks and production fixes.}
        \resumeItem{Introduced refactoring and code-quality best practices, driving unit testing and automated QA involvement, thereby improving maintainability and delivery predictability.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led design and implementation of new features in automotive HMI systems, interfacing frontend React applications with backend services via \textbf{REST APIs} in embedded environments.}
        \resumeItem{Developed frontend with React and backend integration, incorporating clean and modular code principles aligned with client UX and safety requirements.}
        \resumeItem{Built and maintained \textbf{CI/CD pipelines} using \textbf{Jenkins} and Bitbucket, automating builds and tests to reduce integration issues and improve deployment cadence.}
        \resumeItem{Conducted unit and integration testing for automotive software components, facilitating early defect detection with continuous integration workflows.}
        \resumeItem{Collaborated on microservices-based automotive software architecture, contributing to modular, event-driven design patterns for better system scalability and maintainability.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and developed scalable backend services in \textbf{Python} and \textbf{Java}, implementing modular, maintainable code supporting large-scale analytical models and APIs.}
        \resumeItem{Created \textbf{unit} and \textbf{integration tests} improving code quality and reliability, and contributed to contract testing to validate API interactions.}
        \resumeItem{Built a Python-based tool to convert large data files into optimized binary formats, improving load and processing efficiency by 90\%.}
        \resumeItem{Implemented monitoring and diagnostics tools integrating with observability platforms to detect and resolve real-time production issues efficiently.}
        \resumeItem{Mentored junior engineers and led Agile Scrum teams, promoting peer code reviews ensuring adherence to coding standards and best practices for distributed software systems.}
        \resumeItem{Collaborated with product and research teams to design cloud-ready microservices and APIs in compliance with modern architecture styles and scalable SaaS principles in multi-tenant environments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}