\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience building scalable, cloud-native web applications and backend microservices for financial services and enterprise platforms. Skilled in \textbf{Java/Spring Boot}, \textbf{Node.js/React}, \textbf{Python}, and proficient in designing and decomposing large monolithic applications into \textbf{microservices architecture}. Experienced with container orchestration using \textbf{Docker} and \textbf{Kubernetes}, and deploying secure infrastructure on \textbf{AWS} and \textbf{Azure}. Proven ability to collaborate with cross-functional teams to deliver high-quality, secure, and performant services, with a strong focus on financial systems and backend scalability.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, Go (basic), C++, C\#, SQL, Bash, PowerShell \\
     \textbf{Backend and Frameworks}: Spring Boot, Spring MVC, Node.js, Rails, RESTful APIs, Microservices Architecture, Service-Oriented Architecture \\
     \textbf{Frontend}: React, JavaScript, HTML/CSS \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MSSQL, MongoDB, Redis, DynamoDB, Redshift \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, CloudFormation, DynamoDB), Azure (DevOps, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, Terraform, CI/CD Pipelines \\
     \textbf{Data Streaming}: Apache Kafka, Real-time Data Processing, Event-driven Architecture \\
     \textbf{Testing and QA}: JUnit, Cucumber, Postman, TDD/BDD, Automated Testing, Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, System Design, Scalability Optimization, JIRA, Maven, Gradle \\
     \textbf{Blockchain and Crypto}: Familiarity with blockchain concepts, Ethereum addresses, dApps, onchain activity; basic understanding of Bitcoin and Ethereum ecosystems.
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, significantly improving data quality and backend system reliability in a financial context.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber, Selenium, and BDD practices, reducing manual testing effort by 40\% and increasing feature reliability.}
        \resumeItem{Developed and optimized backend workflows to monitor suspicious financial transactions, enhancing real-time case creation and tracking, aligning with compliance and security requirements.}
        \resumeItem{Collaborated in Agile teams to design scalable microservices and RESTful APIs supporting fraud detection and monitoring, contributing to performance and system maintainability improvements.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Data Engineer}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove major quality improvements for \textbf{Azure Cognitive Services} by rigorously testing new features using SDKs, REST APIs, and Azure AI Studio, enhancing performance and stability for real-time applications.}
        \resumeItem{Streamlined testing, database analysis, and container-based workflows leveraging Jupyter, Postman, Java, Python, C\#, and Kusto queries, improving product reliability and scalability by 30\%.}
        \resumeItem{Trained, evaluated, and optimized \textbf{OpenAI GPT} models on Azure OpenAI, reducing latency for real-time workloads by 25\%, demonstrating capacity for handling complex, distributed workloads.}
        \resumeItem{Collaborated with cross-functional engineering teams to validate and scale next-generation AI services, applying principles applicable to building high-reliability backend systems.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Development Engineer Co-op}{\textbf{Jan 2024 -- Apr 2024}}
      {ESO}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Ramped up quickly on XSLT, XML, C\#, C++, and Azure cloud environments to independently deliver sprint user stories and production bug fixes in a fast-paced development setting.}
        \resumeItem{Introduced code-quality and refactoring improvements through Pluralsight training and mentorship, increasing development velocity by 10–15\% and enhancing backend reliability.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{\textbf{Jan 2022 -- Aug 2022}}
      {People Tech Group Private Ltd.}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of haptic feedback features for Cadillac vehicles from concept through integration, working with cross-functional teams to align UX behavior with product safety and functional requirements.}
        \resumeItem{Developed frontend applications using React and integrated backend APIs, ensuring smooth and responsive user experience in a complex automotive HMI environment.}
        \resumeItem{Implemented CI/CD pipelines using Jenkins, SourceTree, and Bitbucket, automating builds and tests for increased reliability and faster software delivery cycles.}
        \resumeItem{Contributed to infotainment UI development using Qt, Rhapsody, WeCAN, and C++, focusing on maintainability and responsiveness within safety-critical systems.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer II}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented scalable analytical models and backend components using Java, C\#, Python, C++, and SQL, resulting in a 40\% performance improvement in business-critical services.}
        \resumeItem{Built a Python-based tool to optimize large model data into compressed binary formats, reducing file sizes by over 90\% and cutting load and processing times, improving system scalability.}
        \resumeItem{Diagnosed and resolved complex production issues, including memory leaks and performance bottlenecks, using advanced debugging and profiling techniques to enhance system stability.}
        \resumeItem{Applied Lean Six Sigma principles to streamline engineering workflows, reducing waste and improving development efficiency within a Scrum environment.}
        \resumeItem{Mentored new engineers and led a cross-functional team as Scrum Master, fostering high standards in code reviews, agile best practices, and system design discussions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, increasing user accessibility.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring by integrating Amazon Textract for intelligent data extraction from receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications using Python Lambda scripts that extract critical information and trigger alerts via SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, facilitating efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to optimize power restoration routes, reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}