\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience designing, building, and maintaining scalable, secure, and \textbf{highly available cloud infrastructures} and backend services. Expertise in \textbf{AWS services} such as EC2, Lambda, S3, and DynamoDB, and strong skills in \textbf{Python}, \textbf{Java}, and \textbf{Node.js}. Proven ability to automate and optimize \textbf{CI/CD pipelines}, develop monitoring and diagnostic tools, and enhance infrastructure security and operational simplicity. Demonstrated leadership in cross-functional teams at \textbf{TD Bank}, \textbf{Microsoft}, and other global firms, with a passion for reliability, automation, and cloud-native solutions.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, Java, Golang, C++, C\#, SQL, Bash, PowerShell, Typescript, Node.js \\
     \textbf{Cloud Platforms}: \textbf{AWS} (ECS, EKS, RDS, S3, ElasticCache, ELB, ECR, CloudFormation, CDK, Lambda, DynamoDB), Azure (AKS, DevOps), GCP \\
     \textbf{Infrastructure \& DevOps}: Kubernetes, Docker, Jenkins, GitHub Actions, Terraform, CI/CD Pipelines, Monitoring and Alerting Tools \\
     \textbf{Frameworks and Backend}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
     \textbf{Testing and QA}: Automated Testing, TDD, BDD, JUnit, Cucumber, Postman \\
     \textbf{Collaboration}: Agile/Scrum, Code Reviews, Technical Writing, JIRA, System Design, Scalability and Reliability Optimization
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented automated Python and SQL validation scripts in Azure Data Notebooks to verify fraud detection data pipelines, improving data integrity and overall system \textbf{reliability}.}
        \resumeItem{Developed and maintained \textbf{CI/CD pipelines} for regression and functional tests using Java, Cucumber, and Selenium, enhancing deployment automation and reducing manual testing by 40\%.}
        \resumeItem{\textbf{Designed and maintained monitoring and diagnostic workflows} leveraging large-scale transactional datasets and third-party tools, enabling proactive fraud detection and faster incident response.}
        \resumeItem{Collaborated with cross-functional teams to optimize system performance and scalability following Agile methodologies, ensuring timely quality releases in a dynamic environment.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Data Engineer}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Improved \textbf{Azure Cognitive Services} quality by testing and debugging SDKs, REST APIs, and AI capabilities, enhancing service reliability and performance.}
        \resumeItem{Optimized containerized workflows using \textbf{Jupyter}, Postman, and various programming languages including Python and C\#, increasing system observability and reliability by 30\%.}
        \resumeItem{Led training, evaluation, and latency optimization of \textbf{OpenAI GPT} models deployed on \textbf{Azure OpenAI}, improving real-time production efficiency by 25\%.}
        \resumeItem{Partnered with product and engineering teams to validate and enhance scalable cloud AI systems, ensuring robust production readiness and operational simplicity.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Development Engineer Co-op}{\textbf{Jan 2024 -- Apr 2024}}
      {ESO}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained proficiency in \textbf{Azure} environment and programming languages including C\#, C++, and XSLT, delivering production bug fixes and sprint features independently.}
        \resumeItem{Introduced code quality and refactoring best practices through mentorship and training, improving team velocity and maintainability by up to 15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{\textbf{Jan 2022 -- Aug 2022}}
      {People Tech Group Private Ltd.}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed and integrated haptic feedback features for Cadillac vehicles, coordinating closely with clients to ensure compliance with safety and UX specifications.}
        \resumeItem{Designed reactive frontend application with React, enhancing user interaction and system responsiveness in automotive design platform.}
        \resumeItem{Contributed to UI and interaction workflow improvements using \textbf{Qt}, \textbf{Rhapsody}, \textbf{WeCAN}, and \textbf{C++}, increasing production system responsiveness and reliability.}
        \resumeItem{Implemented automated builds and testing with \textbf{Jenkins}, \textbf{SourceTree}, and \textbf{Bitbucket}, reducing deployment failures by 30\% and improving integration across teams.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer II}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed and optimized analytical models and core services using Java, Python, C\#, and SQL, achieving 40\% better performance over legacy systems.}
        \resumeItem{Created a \textbf{Python} tool to convert large datasets to optimized binary formats, reducing storage usage by 90\% and improving processing speed.}
        \resumeItem{Resolved critical production issues involving memory leaks and performance bottlenecks using detailed root cause analysis and profiling tools.}
        \resumeItem{Led process-improvement initiatives applying \textbf{Lean Six Sigma} principles, enhancing engineering workflows and reducing waste.}
        \resumeItem{Mentored peers and onboarded new engineers, strengthening team capability and maintaining high engineering standards.}
        \resumeItem{Collaborated with Product Management and Research to deliver scalable and reliable solutions, serving as \textbf{Scrum Master} for multiple projects.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}