\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Software Engineer} with 5+ years of experience in the design, development, and testing of complex software applications, including embedded systems and backend services. Skilled in \textbf{C++}, \textbf{Python}, and \textbf{Linux} environments, with strong expertise in software testing, debugging, and automation. Experienced collaborating with cross-functional agile teams to deliver high-quality, reliable, and scalable software solutions. Proven ability to work effectively in multicultural teams and quickly adapt to emerging technologies and tools.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: C++, Python, Java, C\#, SQL, Bash \\
     \textbf{Embedded Systems}: Embedded Software Development and Testing, Real-time Systems \\
     \textbf{Operating Systems}: Linux (Proficient in development and integration) \\
     \textbf{Networking}: Understanding of Networking Concepts and Protocols \\
     \textbf{Tools \& Frameworks}: Cucumber, Selenium, JUnit, Jenkins, Git, Docker \\
     \textbf{Cloud Platforms}: Azure, AWS (Basic familiarity) \\
     \textbf{Development Practices}: Agile/Scrum, Test Automation, Debugging, Bug Tracking, CI/CD Pipelines \\
     \textbf{Documentation}: Clear, organized software and testing documentation
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented automated testing and validation scripts using \textbf{Python} and \textbf{SQL} to improve data quality in financial pipelines, ensuring measurable increase in system reliability.}
        \resumeItem{Automated regression and functional testing with \textbf{Java}-based test frameworks using \textbf{Cucumber} and \textbf{Selenium}, reducing manual testing effort by 40\% and improving feature stability.}
        \resumeItem{Collaborated with cross-functional teams to troubleshoot, prioritize, and resolve software defects, contributing to enhanced product quality and delivery schedules.}
        \resumeItem{Contributed to integration and validation of software components deployed on \textbf{Linux} infrastructure, aligning with Agile/Scrum practices for continuous improvement.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Conducted comprehensive testing and quality assurance of cloud-based AI services using \textbf{SDKs}, \textbf{REST APIs}, and automated test tools, driving defect identification and resolution.}
        \resumeItem{Developed and maintained testing scripts and tool integrations with \textbf{Python} and \textbf{C\#}, improving test coverage and scalability of Azure Cognitive Services components.}
        \resumeItem{Supported troubleshooting and defect resolution by analyzing telemetry and logs, enhancing software performance and stability in production environments.}
        \resumeItem{Collaborated with product managers and engineers across teams to understand requirements and deliver validated, production-ready solutions.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Accelerated learning curve on embedded and backend software development with \textbf{C++}, \textbf{C\#}, and \textbf{XSLT}, owning production bug fixes and sprint user stories independently.}
        \resumeItem{Introduced coding and testing best practices, focusing on software maintainability, refactoring, and automated testing to enhance delivery quality.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed embedded software features for automotive haptic feedback systems using \textbf{C++} and \textbf{Qt}, ensuring consistent performance aligned with design and safety requirements.}
        \resumeItem{Participated in software testing, integration, and validation on prototype hardware, verifying functionality and responsiveness in real-world scenarios.}
        \resumeItem{Collaborated closely with multi-disciplinary teams to resolve defects and optimize infotainment UI stability using \textbf{Rhapsody}, \textbf{WeCAN}, and \textbf{C++}.}
        \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins} and \textbf{Bitbucket} to automate builds and tests, reducing integration errors across distributed teams.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented core analytical and embedded software components using \textbf{C++}, \textbf{Python}, and \textbf{Java}, improving processing efficiency by 40\%.}
        \resumeItem{Built automated test tools in \textbf{Python} to handle large datasets and streamline validation processes, enhancing reliability of downstream damage computations.}
        \resumeItem{Diagnosed and resolved critical memory and performance issues using systematic debugging and profiling techniques, improving software robustness.}
        \resumeItem{Led scrum ceremonies as \textbf{Scrum Master}, collaborating with cross-functional teams to optimize delivery pipelines and maintain high-quality releases.}
        \resumeItem{Mentored junior engineers and promoted best practices in code quality, automated testing, and documentation for embedded and backend software.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}