\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Software Engineer} with 5+ years of experience in designing, developing, and maintaining performant and scalable desktop and backend applications. Skilled in \textbf{C\#/.NET}, \textbf{WPF} (MVVM), REST and SOAP API integrations, and developing solutions with focus on performance, usability, and reliability. Strong experience with relational databases including \textbf{SQL Server} and \textbf{PostgreSQL}, and caching technologies such as \textbf{Redis}. Proven ability in refactoring legacy Windows Forms components and contributing to architectural decisions to support modular monolith and microservices evolution. Committed to delivering high-quality code with thorough unit and integration tests, mentoring peers, and collaborating effectively with cross-functional teams.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: C\#, Java, Python, SQL, Bash, PowerShell, C++ \\
     \textbf{Frameworks/Technologies}: .NET (async programming, LINQ, generics), WPF (MVVM, data binding), Windows Forms, REST & SOAP APIs, Syncfusion UI components \\
     \textbf{Databases}: PostgreSQL, SQL Server, Redis, MongoDB \\
     \textbf{Cloud \& DevOps}: Azure DevOps, GitHub Actions, Docker, Kubernetes, CI/CD pipelines \\
     \textbf{Tools \& Practices}: Visual Studio, JIRA, Unit, Integration \& UI Testing, Code Reviews, Agile/Scrum, Performance Profiling, Secure Coding \\
     \textbf{Other}: Experience with ESRI GIS platform APIs, AI-assisted development tooling (Copilot)
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Implemented robust Python and SQL validation scripts in Azure Data Notebooks to verify incoming data from fraud detection pipelines, significantly improving data quality and overall system reliability.}
        \resumeItem{Automated regression and functional testing by developing Java-based test suites using Cucumber, Selenium, and BDD practices, reducing manual effort by 40\% and increasing feature reliability.}
        \resumeItem{Built and maintained complex backend workflows integrating with multiple APIs, focusing on performance and scalability, aligned with best practices in asynchronous programming.}
        \resumeItem{Delivered multiple high-impact initiatives by designing and optimizing complex SQL queries, following Agile/Scrum methodologies to ensure timely, high-quality releases.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Drove major quality improvements for Azure Cognitive Services by rigorously testing new features using SDKs, \textbf{REST APIs}, and Azure AI Studio, identifying and resolving defects to enhance performance and stability.}
        \resumeItem{Streamlined testing and container-based workflows using Visual Studio, Java, Python, \textbf{C\#}, and Kusto, improving product reliability and observability by 30\%.}
        \resumeItem{Pioneered training, evaluation, and optimization of OpenAI GPT models on Azure OpenAI, improving performance and reducing latency through systematic benchmarking.}
        \resumeItem{Collaborated with engineering and product teams to validate scalable, production-ready AI capabilities using modern cloud technologies.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Ramped up on \textbf{C\#}, \textbf{C++}, \textbf{XSLT}, \textbf{XML}, and Azure within a complex codebase enabling independent ownership of sprint user stories and production bug fixes.}
        \resumeItem{Leveraged mentorship and training resources to introduce code-quality and refactoring improvements focused on maintainability and performance, increasing development velocity by 10-15\%.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led development of new haptic feedback features for Cadillac vehicles, including requirements analysis, implementation, and client communication to align UX behavior with safety and brand guidelines.}
        \resumeItem{Developed interactive frontend using React and backend API integrations to deliver responsive user experiences aligned with UI/UX best practices.}
        \resumeItem{Contributed to infotainment UI workflows using \textbf{Qt}, \textbf{C++}, and related technologies, improving responsiveness and reliability.}
        \resumeItem{Implemented CI/CD pipelines for automotive software using Jenkins and Bitbucket, automating builds, tests, and deployment to reduce integration issues.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Implemented next-generation analytical models using \textbf{C\#}, Java, Python, C++, and SQL, delivering 40\% performance improvement across business-critical components.}
        \resumeItem{Built a Python tool to convert large data into optimized binary formats, reducing file size and improving load times.}
        \resumeItem{Diagnosed and resolved complex production issues, including memory leaks and performance bottlenecks, using profiling and root-cause analysis.}
        \resumeItem{Applied Lean Six Sigma principles and mentored new engineers, while leading a team and serving as Scrum Master for multiple releases.}
        \resumeItem{Collaborated with Product Management to refine feature requirements and deliver scalable, high-performance software solutions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Master of Applied Computer Science}}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {\textbf{Bachelor of Technology in Computer Science and Engineering}}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}