\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer and Data Engineer} with 5+ years of experience designing and developing cloud-native applications, with a strong focus on \textbf{data engineering}, \textbf{Python}, \textbf{SQL}, and \textbf{Azure} platform services including \textbf{Azure Data Factory}, \textbf{Azure Databricks}, and \textbf{Azure DevOps}. Skilled in data ingestion, transformation (ETL), and processing of large-scale datasets using Spark, big data technologies, and distributed computing frameworks. Experienced in Agile/DevOps practices, test automation, and collaborating cross-functionally to deliver robust software solutions. Proven ability to support and enhance \textbf{intelligent analytics} and \textbf{AI} lifecycle solutions.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Python, SQL, Java, C\#, C++, Bash, PowerShell \\
     \textbf{Data Engineering}: Azure Databricks, Azure Data Factory, Spark, ETL Pipelines, Data Lake, Data Modeling (Medallion Architecture), Big Data Processing \\
     \textbf{Cloud Platforms}: Azure (Data Factory, Databricks, DevOps, ML Ops), AWS, GCP \\
     \textbf{DevOps \& Tools}: Azure DevOps, Git, JIRA, Confluence, VS Code, CI/CD Pipelines \\
     \textbf{Machine Learning \& AI}: MLOps concepts, AI lifecycle, Python libraries for data science, model training and evaluation \\
     \textbf{Frameworks \& Backend}: Spring Boot, Node.js, RESTful APIs \\
     \textbf{Databases}: SQL Server, PostgreSQL, Oracle, MongoDB, Redis \\
     \textbf{Development Practices}: Agile, Scrum, Test Automation, Code Reviews, Performance Tuning
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained \textbf{ETL pipelines} using \textbf{Azure Data Factory} and \textbf{Azure Databricks} to process large-scale transactional data, ensuring data quality and reliability for fraud detection workflows.}
        \resumeItem{Created automated data validation tests with \textbf{Python} and \textbf{SQL} in Azure notebooks, enhancing accuracy and enabling early detection of data anomalies.}
        \resumeItem{Collaborated in Agile teams, using \textbf{Azure DevOps} for source control and CI/CD with branching strategies, improving deployment efficiency and environment consistency.}
        \resumeItem{Assisted users and stakeholders by providing technical support and documentation for data pipelines and application components.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Senior Data Engineer}}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Contributed to the development and testing of intelligent analytics features in \textbf{Azure Cognitive Services} using \textbf{Python}, \textbf{REST APIs}, and SDKs, ensuring high service reliability.}
        \resumeItem{Implemented Spark and \textbf{distributed processing} concepts using \textbf{Databricks} notebooks to enhance data ingestion and processing capabilities within cloud ecosystems.}
        \resumeItem{Executed model evaluation and performance tuning tasks for \textbf{OpenAI GPT} integrations, aligned with \textbf{MLOps} best practices on \textbf{Azure OpenAI} platform.}
        \resumeItem{Participated in the Agile delivery process utilizing \textbf{JIRA} and \textbf{Confluence} for efficient communication and sprint management with DevOps teams.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\textbf{Software Development Engineer Co-op}}{\textbf{Jan 2024 -- Apr 2024}}
      {\textbf{ESO}}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Gained proficiency in \textbf{Azure} development environments and tools including \textbf{VS Code} and built mini-projects using \textbf{Python} and \textbf{C\#}, supporting application enhancements and bug fixes.}
        \resumeItem{Introduced improvements to code quality and refactoring through technical mentoring, accelerating development velocity and reducing technical debt.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer}}{\textbf{Jan 2022 -- Aug 2022}}
      {\textbf{People Tech Group Private Ltd.}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Engineered and tested embedded software components in C++ for automotive HMI systems, applying best practices relevant to safety-critical and real-time data processing.}
        \resumeItem{Developed RESTful APIs and frontend features for automotive design applications using React, enhancing real-time user interactions with data-driven feedback.}
        \resumeItem{Designed and executed testing for haptic feedback mechanisms, carrying out data acquisition and event-driven control to simulate real driving conditions.}
        \resumeItem{Implemented CI/CD pipelines with \textbf{Jenkins} and automated build/test processes across distributed teams to accelerate code integration and quality assurance.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Software Engineer II}}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed core \textbf{data processing} and analytical modules primarily in \textbf{Python}, \textbf{Java}, and \textbf{SQL} to improve model efficiency by 40\%, supporting critical insurance risk analysis.}
        \resumeItem{Built a Python tool to convert voluminous data into optimized binary formats, optimizing storage and accelerating ingestion pipelines.}
        \resumeItem{Led root cause analysis and troubleshooting of production performance issues using profiling and debugging methodologies to improve system stability.}
        \resumeItem{Acted as Scrum Master and mentored team members in Agile DevOps practices, ensuring smooth sprint cycles and continuous delivery improvements.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}