\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Experienced \textbf{Full-Stack Software Engineer} with 5+ years of designing and delivering scalable, customer-facing applications and backend services. Proficient in \textbf{Java}, \textbf{Python}, \textbf{Node.js/React}, and cloud platforms including \textbf{AWS} and \textbf{Azure}. Skilled in building and maintaining production systems with strong programming fundamentals, RESTful APIs, and microservices architectures. Proven ability to collaborate across product, design, firmware, and infrastructure teams to solve real-world problems with focus on user experience, operational reliability, and continuous improvement.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: Java, Python, TypeScript, JavaScript, C++, C\#, SQL, Bash \\
     \textbf{Backend and Frameworks}: Spring Boot, Node.js, RESTful APIs, Microservices Architecture, GraphQL \\
     \textbf{Frontend}: React, React Native, HTML/CSS \\
     \textbf{Databases}: PostgreSQL, MySQL, Oracle, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS (EC2, Lambda, S3, DynamoDB, CloudFormation), Azure (DevOps, AKS), GCP \\
     \textbf{DevOps and Tools}: Docker, Kubernetes, Jenkins, Git, GitHub Actions, Azure DevOps, CI/CD Pipelines \\
     \textbf{Data Streaming}: Apache Kafka, Event-driven Architecture \\
     \textbf{Testing and QA}: JUnit, Cucumber, Selenium, Postman, TDD/BDD, Performance Testing \\
     \textbf{Development Practices}: Agile/Scrum, System Design, Scalability, Code Reviews, JIRA, Maven, Gradle
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{Wipro Technologies (TD Bank)}}{\textbf{Oct 2024 -- Present}}
      {Software Engineer}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained data validation and fraud monitoring workflows with \textbf{Python}, \textbf{SQL}, and cloud-native solutions on \textbf{Azure}, improving data reliability and end-user trust.}
        \resumeItem{Automated functional and regression testing by implementing \textbf{Java}-based testing frameworks using \textbf{Cucumber} and \textbf{Selenium}, enhancing feature stability and release cadence.}
        \resumeItem{Collaborated with cross-functional teams using Agile practices to design scalable features and optimize key transactional workflows, aligning with customer success and operational efficiency.}
        \resumeItem{Engaged directly with product managers to translate user needs into technical solutions, ensuring high-quality delivery of customer-facing features.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{LTI Mindtree LTD (Microsoft)}}{\textbf{Dec 2023 -- Apr 2024}}
      {Senior Data Engineer}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Contributed to the quality and scalability of \textbf{Azure Cognitive Services} by validating features and APIs using SDKs, \textbf{RESTful} services, and cloud tools, enhancing product reliability.}
        \resumeItem{Improved monitoring and observability by integrating containerized workflows with tools such as \textbf{Jupyter}, \textbf{Postman}, and \textbf{Kusto}, enabling proactive operational support.}
        \resumeItem{Optimized large-scale machine learning models leveraging \textbf{Azure OpenAI}, resulting in better latency and performance for real-time enterprise applications.}
        \resumeItem{Worked closely with engineering and product teams to architect and ship cloud-based AI features that provide direct value to customers.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{ESO}}{\textbf{Jan 2024 -- Apr 2024}}
      {Software Development Engineer Co-op}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Built full-stack solutions with \textbf{C\#}, \textbf{C++}, and \textbf{Azure} services by quickly ramping up on complex codebases and independently owning sprint deliverables.}
        \resumeItem{Introduced and advocated code quality improvements and refactoring standards that increased team velocity and maintainability in production applications.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{People Tech Group Private Ltd.}}{\textbf{Jan 2022 -- Aug 2022}}
      {Software Engineer}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed and implemented \textbf{React}-based frontends and backend APIs for automotive infotainment platforms, enhancing user experience and system interactivity.}
        \resumeItem{Developed haptic feedback modules for automotive safety features, performing integration and validation on prototype hardware in realistic scenarios.}
        \resumeItem{Contributed to automotive HMI workflows using \textbf{Qt}, \textbf{C++}, and \textbf{Rhapsody}, improving system reliability and responsiveness.}
        \resumeItem{Built and maintained CI/CD pipelines with \textbf{Jenkins} and \textbf{Bitbucket} to automate build, test, and deployment processes for embedded software.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Verisk Analytics}}{\textbf{Sep 2018 -- Jan 2022}}
      {Software Engineer II}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Engineered scalable analytical models and core services in \textbf{Java}, \textbf{Python}, and \textbf{C\#}, achieving significant performance gains for enterprise risk assessment applications.}
        \resumeItem{Built efficient data processing tools to convert large model datasets into optimized formats, reducing load times and enabling faster computations.}
        \resumeItem{Diagnosed and resolved critical production issues such as memory leaks and bottlenecks through systematic debugging and performance profiling.}
        \resumeItem{Mentored engineers and led Agile Scrum teams, facilitating high-quality delivery of customer-focused features aligned with product goals.}
        \resumeItem{Collaborated closely with product and research teams to define requirements and develop solutions that improve customer outcomes and operational scalability.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{Sep 2022 -- Apr 2024}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{Aug 2015 -- May 2019}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using React, Bootstrap, and CSS, enhancing user engagement and satisfaction.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous Jest testing and Test-Driven Development (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to SOLID principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using Java, coupled with JUnit test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}