\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\bullet$}
\renewcommand\labelitemii{$\bullet$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%--------------- Header (centered) --------------- 
\begin{center}
  {\Large \textbf{Sai Sindhu Bhimavarapu}} \\
  Toronto, Canada \\
  +1-902-977-0490 \enspace | \enspace sindhu10988@gmail.com \enspace | \enspace \href{https://www.linkedin.com/in/sindhu1098/}{linkedin.com/in/sindhu1098} \enspace | \enspace \href{https://github.com/si-ndhu}{github.com/si-ndhu}
\end{center}

%--PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Results-driven \textbf{Full-Stack Software Engineer} with 5+ years of experience delivering enterprise-grade, cloud-native web applications with strong expertise in \textbf{React}, \textbf{Angular}, and \textbf{TypeScript}. Skilled in developing scalable, accessible, and high-performance user interfaces using UI frameworks such as \textbf{Material UI} and \textbf{Bootstrap}. Experienced in building and integrating RESTful APIs, following \textbf{Test-Driven Development} (TDD), and collaborating in agile teams for financial services and technology companies, including \textbf{TD Bank} and \textbf{Microsoft}. Passionate about improving user experience, UI architecture, and cross-functional teamwork to deliver consistent and reliable software solutions.
    }}
  \end{itemize}
\vspace{-16pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: JavaScript, TypeScript, Java, Python, C++, C\# \\
     \textbf{Frontend Frameworks}: React (v16+), Angular (v10+), Material UI, Bootstrap, Ant Design, HTML5, CSS3 \\
     \textbf{Backend and APIs}: Node.js, Spring Boot, RESTful APIs, Microservices \\
     \textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis, DynamoDB \\
     \textbf{Cloud Platforms}: AWS, Azure, GCP, Azure Kubernetes Service (AKS), AWS S3, Lambda \\
     \textbf{DevOps and Tools}: Git, Jenkins, Azure DevOps, GitHub Actions, Terraform, CI/CD Pipelines \\
     \textbf{Testing}: Jest, Cucumber, Selenium, TDD/BDD \\
     \textbf{Messaging and Streaming}: Apache Kafka \\
     \textbf{Development Practices}: Agile/Scrum, Code Reviews, Sprint Planning, JIRA
    }}
 \end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{\textbf{Oct 2024 -- Present}}
      {\textbf{Wipro Technologies (TD Bank)}}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Developed and maintained front-end components using \textbf{React} and \textbf{TypeScript}, leveraging UI frameworks like \textbf{Material UI} and \textbf{Bootstrap} to ensure a consistent, accessible, and responsive user interface across financial applications.}
        \resumeItem{Collaborated with designers and backend teams to implement seamless user experiences by integrating front-end applications with \textbf{RESTful APIs} and cloud services within an \textbf{Azure} environment.}
        \resumeItem{Automated regression and functional testing with Java-based test suites using \textbf{Cucumber} and \textbf{Selenium}, emphasizing \textbf{Test-Driven Development} (TDD) to improve feature stability and reduce bugs.}
        \resumeItem{Contributed to agile ceremonies including sprint planning and estimation, actively participating in code reviews and knowledge sharing to enhance code quality and team efficiency.}
        \resumeItem{Utilized \textbf{Git} for version control and collaborated within cross-functional teams following \textbf{Agile/Scrum} methodologies to deliver timely, high-quality software releases.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Data Engineer}{\textbf{Dec 2023 -- Apr 2024}}
      {\textbf{LTI Mindtree LTD (Microsoft)}}{Calgary, Canada}
      \resumeItemListStart
        \resumeItem{Tested and validated new Azure Cognitive Services features using \textbf{REST APIs}, SDKs, and front-end elements, enhancing stability and usability of AI-powered applications.}
        \resumeItem{Streamlined workflows involving containerized development using \textbf{Docker} and \textbf{Kubernetes}, improving deployment efficiency and scalability of cloud services on \textbf{Azure}.}
        \resumeItem{Partnered with engineering teams to integrate front-end components with backend APIs, focusing on performance and accessibility in enterprise AI solutions.}
        \resumeItem{Contributed to system design discussions and code reviews, applying best practices in UI architecture and front-end testing to achieve robust software delivery.}
      \resumeItemListEnd
    
    \resumeSubheading
      {Software Development Engineer Co-op}{\textbf{Jan 2024 -- Apr 2024}}
      {ESO}{Halifax, Canada}
      \resumeItemListStart
        \resumeItem{Supported front-end development efforts by ramping up on \textbf{C\#} and \textbf{Azure} platforms to maintain and improve user-facing features following best practices.}
        \resumeItem{Applied knowledge of UI design principles learned from course work and mentorship to assist in improving user interface components and accessibility compliance.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{\textbf{Jan 2022 -- Aug 2022}}
      {People Tech Group Private Ltd.}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Led front-end development for automotive applications using \textbf{React} and component-based UI frameworks, integrating backend APIs for sophisticated user interactions.}
        \resumeItem{Designed accessible and responsive UI elements, collaborating closely with cross-functional teams to align haptic feedback features with client and user experience standards.}
        \resumeItem{Implemented and maintained CI/CD pipelines with \textbf{Jenkins} and \textbf{Bitbucket}, optimizing continuous integration of web components and enhancing release quality.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer II}{\textbf{Sep 2018 -- Jan 2022}}
      {\textbf{Verisk Analytics}}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Developed and optimized Java and Python applications supporting data-intensive analytics, implementing REST services and improving system performance by up to 40\%.}
        \resumeItem{Built automated test suites using \textbf{JUnit} and \textbf{Cucumber}, applying \textbf{Test-Driven Development} (TDD) principles to ensure high code quality and reliability.}
        \resumeItem{Led code reviews and mentored team members on software best practices, including frontend-backend integration and agile workflow improvements.}
        \resumeItem{Collaborated with product and research teams to translate requirements into scalable software components, serving as \textbf{Scrum Master} to drive successful agile delivery cycles.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Applied Computer Science}{\textbf{Sep 2022 -- Apr 2024}}
      {Dalhousie University, Halifax, Canada}{GPA: 4.0/4.3}
    \resumeSubheading
      {Bachelor of Technology in Computer Science and Engineering}{\textbf{Aug 2015 -- May 2019}}
      {GRIET, Hyderabad, India}{GPA: 9.9/10}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Cart Pool} -- \emph{React, Node.js, Express, Jest, JWT}}{Full-Stack Web Application}
          \resumeItemListStart
            \resumeItem{Led the development of a full-stack web application enabling peer-to-peer delivery of daily essentials at the lowest delivery costs, resulting in increased accessibility for users.}
            \resumeItem{Designed an intuitive frontend interface using \textbf{React}, \textbf{Bootstrap}, and CSS, focusing on accessibility and responsiveness to enhance user engagement.}
            \resumeItem{Built a robust and scalable backend with Node.js and Express, ensuring seamless integration and performance.}
            \resumeItem{Achieved 100\% test coverage through rigorous \textbf{Jest} testing and \textbf{Test-Driven Development} (TDD), significantly reducing potential bugs.}
            \resumeItem{Implemented secure JWT-based authentication and adhered to \textbf{SOLID} principles and clean code practices, improving maintainability and scalability by 40\%.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{Expense Tracker} -- \emph{AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, CloudFormation}}{Cloud-Based Solution}
          \resumeItemListStart
            \resumeItem{Developed an expense tracking solution using AWS EC2, Lambda, S3, DynamoDB, API Gateway, SNS, and CloudFormation services.}
            \resumeItem{Enhanced expense monitoring processes by integrating Amazon Textract for intelligent data extraction from uploaded receipts, reducing manual input errors by 50\%.}
            \resumeItem{Automated notifications for users by developing Python scripts in Lambda, extracting critical information and triggering alerts through SNS, boosting user efficiency and satisfaction.}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\textbf{PowerGrid Restoration} -- \emph{Java, JUnit, Data Structures, Algorithms}}{Disaster Response Simulation}
          \resumeItemListStart
            \resumeItem{Addressed Hurricane Fiona's aftermath by contributing to a project simulating extensive power outages in Atlantic Canada, enabling more efficient disaster response planning.}
            \resumeItem{Developed core functionality using \textbf{Java}, coupled with \textbf{JUnit} test cases for validation, ensuring high accuracy and reliability in restoration algorithms.}
            \resumeItem{Applied advanced data structures and algorithms to analyze postal code data, optimizing power restoration routes and reducing recovery times by 35\%.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd
\vspace{-15pt}

\end{document}